### 2022-03-24 Article.tex
Initial commit

%\documentclass[preprint,12pt,times]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
 \documentclass[final,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%% or use the graphicx package for more complicated commands
%% \usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
\usepackage{lineno}

\biboptions{sort&compress}

\usepackage{amsmath}
\usepackage{textcomp} %Permet d'introduire un mu droit à l'aide de \textmu en dehors de l'environnement math
\usepackage{color}

\usepackage[leftbars]{changebar} %Pour insérer une barre de mise à  jour (à  gauche car [leftbars]) au moyen de \begin{changebar} %Ne fonctionne pas pour passer du DVI au pdf -> utiliser DV -> PS -> pdf

\usepackage{multirow}
%\usepackage{rotating} %Pour effectuer la rotation d'un tableau à  l'aide de "\begin{sidewaystable} et \end{}" et supprimer "\begin{table} et \end{}"
\usepackage{pdflscape}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usepackage{pgfplots}

\journal{CIRP Journal of Manufacturing Science and Technology}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frontmatter}

\title{Predictive 3D modelling of free oblique cutting of Ti6Al4V titanium alloy and experimental validation for a wide range of conditions}

\author[1]{F. Ducobu\corref{cor1}}
\ead{Francois.Ducobu@umons.ac.be}
\cortext[cor1]{Corresponding author. Tel.: +32 65 45 68}

\author[2]{O. Pantal\'{e}}
\author[1]{E. Rivi\`{e}re-Lorph\`{e}vre}
\author[3]{B. Lauwers}

\address[1]{Machine Design and Production Engineering Lab, Research Institute for Science and Material Engineering, UMONS, Belgium}
\address[2]{Laboratoire G\'{e}nie de Production, INP/ENIT, Universit\'{e} de Toulouse, Tarbes, France}
\address[3]{Department of Mechanical Engineering, KU Leuven \& Flanders Make@KU Leuven-MaPS, Belgium}

%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

Modelling of the cutting process needs to move from a 2D to a 3D configuration to get closer to industrial applications. The study introduces a predictive 3D finite element model of free orthogonal and oblique cutting with an ANN-based material constitutive model and experimental validation in strictly the same conditions (cutting and geometrical). Predictive performance of the model is high for the forces in the 3 directions and the chip thickness ratio on all 36 cutting conditions (including 2 inclination angles). Accuracy of the main cutting force is excellent: the mean difference with the experiments is 3%.

\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

Oblique cutting \sep Finite element method (FEM) \sep Predictive model \sep Artificial Neural Network (ANN)

\end{keyword}
%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{frontmatter}
%%%%%%%%%%%%%%%%%%%%%%%%%%

%%
%% Start line numbering here if you want
%%
\linenumbers

%% main text
%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{Intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%

Selection of the tools and the cutting conditions in machining, but also comprehension of the influence of the process parameters on the quality of a component and its optimisation, are still difficult to achieve because of the high level of complexity and linked nonlinear involved phenomena. In the frame of digital manufacturing and Industry 4.0, modelling of the cutting process supports them, while remaining a challenging task. As highlighted by Arrazola et al. \cite{arrazola_recent_2013}, most finite element (FE) models are developed in 2D (orthogonal cutting configuration usually) although industrial applications require a 3D modelling.
The experimental configuration to validate a model must be as close as possible to the simulation. Few configurations in strictly orthogonal cutting conditions are found. Broaching \cite{abouridouane_friction_2021} or milling \cite{sela_measurement_2021, ducobu_experimental_2015} machines are mostly used; dedicated machines such as in \cite{afrasiabi_numerical-experimental_2021} allow for high cutting speed. Free oblique cutting with a straight cutting edge has not been studied yet: all the efforts have been focussing on orthogonal cutting (mostly for 2D validation).
Lagrangian and Eulerian formulations are the most used for FE modelling of the cutting process. The Coupled Eulerian-Lagrangian (CEL) formulation has recently been successfully applied to the modelling of cutting (2D orthogonal configuration): it provides accurate results with a realistic chip shape and no mesh distortion \cite{ducobu_application_2016}. First applications in 3D are found in recent works \cite{xu_simulation_2021, ducobu_finite_2017, ambrosio_new_2022, vovk_finite_2020, hardt_three_2021}. They mostly cover (free) orthogonal cutting, while free oblique cutting still needs to be investigated.
The behaviour of the machined material is one of the key aspects of a FE model \cite{arrazola_recent_2013, melkote_advances_2017}. Research is very intense in this field, which leads to a growing number of material constitutive models ranging from empirical to physical models \cite{melkote_advances_2017}. The empirical Johnson-Cook (JC) model \cite{johnson_constitutive_1983} is still the most used so far. One issue of material behaviour modelling for cutting simulation is the identification of the model parameters, moreover as the experimental equipment does not allow to reach the high levels of strains, strain rates and temperature of machining \cite{melkote_advances_2017}. Inverse identification is an alternative, but the uniqueness of the solution is not always guaranteed \cite{arrazola_recent_2013}. It uses optimisation or Artificial Intelligence based methods \cite{melkote_advances_2017}, such as in \cite{hardt_investigations_2021}, and requires defining the analytical expression of the constitutive model.
This paper fills the literature gap on oblique cutting by investigating free orthogonal and oblique 3D cutting configurations from both the experimental and the numerical points of view. An Artificial Neural Network (ANN), introduced in \cite{pantale_efficient_2022}, is implemented in a FE cutting model for the first time instead of the analytical JC law. A broad range of cutting speeds (6), uncut chip thicknesses (3) and inclination angles (2) resulting in 36 different conditions are considered to demonstrate the predictive ability of the FE model for fundamental variables. No assumptions are made about the geometry of the machined workpiece in the model (i.e. its width is the same as in the experiments), while keeping computation time relevant for industrial applications. The developments apply to the titanium alloy Ti6Al4V.

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental setup}
\label{ExpSet}
%%%%%%%%%%%%%%%%%%%%%%%%%%

A 3-axis GF Mikron VCE 600 Pro milling machine is used to carry out dry free orthogonal and oblique cutting tests on Ti6Al4V (grade 5 annealed at 750°C for 1 h followed by air cooling) with the same kinematics as a shaper. As shown in Figure 1, the tungsten carbide tool (modified LCGN160602-0600-FG, CP500 from SECO) is fixed on a dedicated holder (modified CFHN-06 from SECO) and the sample to be cut is clamped in the spindle (no rotation is allowed during the test). The top of the sample includes 3 ribs of 1 mm in width (width of the tool is 6 mm) and 10 mm in length. The test consists of removing the upper layer (its height is the uncut chip thickness, h) of one rib at the prescribed cutting speed, $v_c$. The cutting speed is provided by the feed rate, $v_f$, of the machine (max. value of 40 m/min). The tool cutting edge inclination, $\lambda_s$, results from the orientation of the tool and the sample. Forces are measured with a 3-component Kistler 9257B dynamometer and are amplified by a Kistler 5070A charge amplifier. Acquisition is performed at 3 kHz with a Kistler 5697A2 data acquisition system and the DynoWare software. Table 1 shows the cutting conditions, each is repeated 3 times.

\begin{figure}[h]
\centering
\includegraphics{Figures/ExpSetup}
\caption{Experimental setup}
\label{ExpSetup}
\end{figure}

\begin{figure}[h]
\centering
\caption{Tables 1 -- Cutting conditions of the study}
\includegraphics[width = 8cm]{Figures/Tab1}
\label{Tab1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Finite element model}
\label{FEM}
%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Modelling choices}

The CEL formulation is adopted to model the dry free orthogonal and oblique cutting tests with Abaqus/Explicit 2020. The 3D model is composed of a fixed Lagrangian tool and a Eulerian workpiece (Figure 2). Chip formation occurs by plastic flow across the Eulerian domain with no mesh distortion. No damage properties are necessary since continuous chips are formed, removing modelling assumptions.

\begin{figure}[h]
\centering
\includegraphics{Figures/BC}
\caption{Boundary conditions and schematic initial geometry of the model}
\label{BC}
\end{figure}

As shown in Figure 3, the full width of the workpiece (1 mm) is modelled. To allow chip formation and side flow, the Eulerian domain is wider (it includes the volume in which material can move). The volume above the initial workpiece is also meshed with Eulerian elements for the same reasons. As in the experiments and to fulfil the hypothesis of free orthogonal and oblique cutting, the tool is wider than the workpiece. The models are the same for both inclination angles: they differ by the rotation of the tool of 6° about Y axis as in the experiments (Figure 3).

\begin{figure}[h]
\centering
\includegraphics{Figures/FEConfig}
\caption{Configuration of the FE model for $\lambda_s$ = 6°}
\label{FEConfig}
\end{figure}

According to a previous mesh sensitivity study in orthogonal cutting with CEL \cite{ducobu_finite_2017}, elements edge size is 5 µm in the plane parallel to the cutting speed. In the direction perpendicular to this plane, it is 5 µm in areas close to the lateral boundaries of the Eulerian domain and 50 µm in the middle of the workpiece. To reduce computation time, the size of the model depends on the value of the uncut chip thickness. This results in a Eulerian domain (EC3D8RT elements) composed of 216,550 to 273,350 nodes and a Langrangian domain (C3D8T elements) of 4,650 nodes.
The tungsten carbide tool with TiN coating is assumed to be linear elastic. The Ti6Al4V workpiece is assumed to be thermo-elasto-viscoplastic (isotropic) and inelastic heat fraction is 0.9. Following the experimental results of Rech et al. \cite{rech_characterisation_2013}, Coulomb’s friction is assumed to occur at the tool-workpiece interface and both friction and heat partition coefficients depend on the cutting speed; limiting shear stress is included. All the friction energy is converted into heat. Room temperature of 293 K is imposed on the upper and right surfaces of the tool and on the left and bottom surfaces of the workpiece (Figure 2). Radiation and convection are assumed to occur on the rake and clearance faces of the tool. Initial temperature of the tool and the workpiece is set to room temperature (293 K).

\subsection{Material constitutive model of Ti6Al4V}

The material constitutive model of Ti6Al4V used for all numerical simulations is a thermo-elasto-viscoplastic law using a flow criterion based on an ANN implemented in the Abaqus/Explicit code via a VUHARD Fortran routine as proposed by Pantalé et al. in \cite{pantale_efficient_2022}. Several neural network architectures are tested, for the metal cutting simulations, having 2 hidden layers with a variable number of neurons for the first hidden layer ($\zeta$ = 9 to 17) and 7 neurons for the second hidden layer, 3 inputs (plastic strain, $\varepsilon^p$, plastic strain rate, ${\dot{\varepsilon}}^p$, and temperature, T) and one output (the yield stress, $\sigma^y$). The global architecture of this kind of ANN is given in Figure 4.

\begin{figure}[h]
\centering
\includegraphics{Figures/ANN}
\caption{Architecture of the ANN 3-9-7-1-sig used for the flow law}
\label{ANN}
\end{figure}

A Sigmoid activation function is used for all neurons in the two hidden layers. Because of the large number of parameters (from 122 to 210 for 9 and 17 neurons for the first hidden layer, respectively); the 5 sets of ANN parameters are provided in \cite{pantale_coefficients_2022}.

\subsection{Sensitivity study of the results to mass scaling}

FE modelling of the cutting process is very expensive in CPU computation time because of the coupling on many nonlinear phenomena and the large amount of tiny finite elements. Mass scaling (MS) is introduced in the model to reduce the CPU computation time while checking that it does not influence the results (forces and energies) via a mass scaling sensitivity study.
MS factors, ${MS}_f$, ranging from 1E6 (theoretical scaling of CPU time of 1000) to 1 (no scaling) have been used for one cutting condition ($\lambda_s$ = 0°, $v_c$ = 30 m/min and h = 60 µm). Table 2 gives the results normalised ($\hat{x}$) by these of the model without MS (x). As expected, actual speed-up does not increase linearly with the ${MS}_f$, but it is still significant. ${MS}_f$ of 1E6 leads to unstable computation and ${MS}_f$ of 1E5 results in erratic forces evolutions. These results are confirmed by high values of the kinetic ($KE$) on internal ($IE$) energies ratio (it should not exceed a few \%). A ${MS}_f$ value of 1E3 is selected as it provides a good balance between computation time reduction and impact on forces (considered in the analysis), while keeping $\frac{KE}{IE}$ below 1\%. To provide an order of magnitude of CPU computation time, between 10 h and 50 h are needed on 4 cores of an Intel i7-5700 HQ at 3.48 GHz.

\begin{figure}[h]
\centering
\caption{Tables 2 -- MS sensitivity study (selected ${MS}_f$ in bold)}
\includegraphics[width = 8cm]{Figures/Tab2}
\label{Tab2}
\end{figure}

\subsection{Sensitivity study of the results to the number of neurons}

The number of neurons on the hidden layers may influence the results. A sensitivity study on the number of neurons for the first hidden layer is carried out to select the ANN providing the best balance between CPU computation time and quality of the results. The study shows no influence on the forces when compared to the built-in Johnson-Cook model, only computation time is influenced (Table 3). A first hidden layer with 9 neurons is therefore selected.

\begin{figure}[h]
\centering
\caption{Tables 3 -- Sensitivity to the number of neurons of the first layer, $\zeta$ (selection in bold)}
\includegraphics[width = 8cm]{Figures/Tab3}
\label{Tab3}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental and numerical results}
\label{Results}
%%%%%%%%%%%%%%%%%%%%%%%%%%

Experimental and numerical forces are filtered with a second-order low-pass Bessel filter at 750 Hz before computing the mean value of the signal at steady state. Mean and standard deviation ($2\sigma$) are computed from the 3 experimental values and are shown in Figures 5 to 7. Mean numerical values are plotted inside the experimental bars in Figures 5 to 7.

\begin{figure}[h]
\centering
\includegraphics{Figures/Fc}
\caption{Comparison of experimental (E) and numerical (N) cutting forces}
\label{Fc}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics{Figures/Ff}
\caption{Comparison of experimental (E) and numerical (N) feed forces}
\label{Ff}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics{Figures/Fp}
\caption{Comparison of experimental (E) and numerical (N) passive forces}
\label{Fp}
\end{figure}

The increase of the cutting force with the uncut chip thickness is clearly observed in Figure 5 for both experimental and numerical results at the 2 inclination angles, as well as the decrease of the force with the increase in the cutting speed. This shows temperature softening domination on strain rate hardening for Ti6Al4V and that it is accurately modelled. The increase of the inclination angle from 0° to 6° reduces the cutting force; this is well captured by the model. For cutting speeds of 20-40 m/min, $F_c$ is almost constant for 40 µm and 60 µm, while it slightly decreases for 80 µm; this small stabilisation is less marked for the model.
Increase in the deviation around the mean value with the cutting speed is noted for values above 10 m/min. All numerical values are within a confidence interval of 95\% of the experiments (35 out of 36 conditions are within a confidence interval of 68\%) and the mean difference with the experiments is 3\%, which is remarkable, moreover given the wide range of cutting conditions considered. This highlights the predictive qualities of the FE model for both inclination angles.
Figure 6 shows the results for the feed force, where the two clearest trends are its decrease with inclination angle and its increase with the uncut chip thickness for both experimental and numerical results. For 80 µm, $F_f$ globally decreases with $v_c$ in the experiments. For 40 and 60 µm, the force decreases at lower $v_c$ and then increases for 0°, while a decrease is observed at all $v_c$ for 6°. For the numerical values, the global trend is the same for the 3 uncut chip thicknesses and both inclination angles: a decrease for the lowest $v_c$ values and then an increase. The numerical values are mostly not within the 95\% confidence interval (it has no clear evolution with the cutting conditions). Coupled with the differences in trends, it shows that $F_f$ is less well modelled (mean difference is 35\%) as usual in FE modelling of the cutting process. Improving the friction model should enhance the results.
Passive force is non-zero for the inclination angle of 6° (Figure 7). As the cutting force, it increases with the uncut chip thickness and it decreases with the cutting speed. Comparison with the experiments is globally the same as for $F_c$, except for a larger difference in the magnitude of $F_p$ (mean difference is 26\%, but it is small in absolute – less than 5 N). The numerical values are mostly not in the 95\% experimental confidence interval.
Regarding the chips morphology, all of them are continuous. For both the simulation and the experiments, the chip thickness ratio, $\lambda_h$, decreases with the cutting speed because of reduction of friction and it is almost independent of the uncut chip thickness. The mean difference between experimental and numerical $\lambda_h$ is 13\% across the whole range of cutting conditions.

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%

In this paper, an experimental study has been carried out in free orthogonal and oblique cutting for Ti6Al4V. It is a reference to assess the performances of the 3D FE model introducing an ANN-based constitutive model and developed in the same conditions. An unpreviously seen wide range of cutting conditions, 36, is considered, including 2 inclination angles.
Accurate evaluation of fundamental variables in 3D with the absence of tuning of both numerical parameters and model features when cutting conditions and inclination angle are significantly modified is a strong novelty of this work. Only changing the inclination angle to move from free orthogonal to oblique cutting while maintaining the quality of the results has no equivalent in the current literature, moreover as no study on free oblique cutting is available. Predictive abilities of the model make it adequate for development of tools with a straight cutting edge, for example.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% The Appendices part is started with the command \appendix;
%%% appendix sections are then done as normal sections
%%% \appendix
%
%%% \section{}
%%% \label{}
%
%%% References
%%%
%%% Following citation commands can be used in the body text:
%%% Usage of \cite is as follows:
%%%   \cite{key}          ==>>  [#]
%%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
%%%   \citet{key}         ==>>  Author [#]
%
%%% References with bibTeX database:
%
\bibliographystyle{model1-num-names}
\bibliography{Biblio}
%
%%% Authors are advised to submit their bibtex database files. They are
%%% requested to list a bibtex style file in the manuscript if they do
%%% not want to use model1-num-names.bst.
%
%%% References without bibTeX database:
%
%% \begin{thebibliography}{00}
%

%%% \bibitem must have the following form:
%%%   \bibitem{key}...
%%%
%
%% \bibitem{}
%
%% \end{thebibliography}
%

\end{document}

### 2022-04-17 Article.tex
Changing the ANN figure for a PDF
Introduction of tables (instead of figures) and the new forces figures in the tex file
Text linked to the forces figures still to be updated

@@
 Acquisition is performed at 3 kHz with a Kistler 5697A2 data acquisition system and the DynoWare software.
-Table 1 shows the cutting conditions, each is repeated 3 times.
+Table \ref{tab:CutCond} shows the cutting conditions, each is repeated 3 times.
 
@@
 
-\begin{figure}[h]
-\centering
-\caption{Tables 1 -- Cutting conditions of the study}
-\includegraphics[width = 8cm]{Figures/Tab1}
-\label{Tab1}
-\end{figure}
+%
+\begin{table}[!h]
+\begin{center}
+\caption{\label{tab:CutCond} Cutting conditions of the study}
+\begin{tabular}{ll}
+\hline\noalign{\smallskip}
+Parameter  & Values\\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Cutting speed, $v_c$ (m/min) & 5, 7.5, 10, 20, 30, 40\\
+Uncut chip thickness, $h$ (\textmu{}m) & 40, 60, 80\\
+Cutting edge inclination, $\lambda_s$ & 0, 6\\
+Width of the workpiece (mm) & 1\\
+Length of the workpiece (mm) & 10\\
+Width of the cutting edge (mm) & 6 (1.1 in the model)\\
+Cutting edge radius, $r_\beta$ (\textmu{}m) & 20\\
+Rake angle, $\gamma_0$ (\textdegree{}) & 15\\
+Clearance angle, $\alpha_0$ (\textdegree{}) & 2\\
+\noalign{\smallskip}\hline
+\end{tabular}
+\end{center}
+\end{table}
+%
 
@@
 \centering
-\includegraphics{Figures/ANN}
+\includegraphics[width=0.8\columnwidth]{Figures/ANN}
 \caption{Architecture of the ANN 3-9-7-1-sig used for the flow law}
@@
 MS factors, ${MS}_f$, ranging from 1E6 (theoretical scaling of CPU time of 1000) to 1 (no scaling) have been used for one cutting condition ($\lambda_s$ = 0°, $v_c$ = 30 m/min and h = 60 µm).
-Table 2 gives the results normalised ($\hat{x}$) by these of the model without MS (x).
+Table \ref{tab:MS} gives the results normalised ($\hat{x}$) by these of the model without MS (x).
 As expected, actual speed-up does not increase linearly with the ${MS}_f$, but it is still significant.
@@
 
-\begin{figure}[h]
-\centering
-\caption{Tables 2 -- MS sensitivity study (selected ${MS}_f$ in bold)}
-\includegraphics[width = 8cm]{Figures/Tab2}
-\label{Tab2}
-\end{figure}
+%
+\begin{table}[!h]
+\begin{center}
+\caption{\label{tab:MS} MS sensitivity study (selected $MS_f$ in bold)}
+\begin{tabular}{lllll}
+\hline\noalign{\smallskip}
+$MS_f$  & Speed-up & $\hat{F_c}$ & $\hat{F_f}$ & $\frac{KE}{IE}$ (\%)\\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+1 & 1 & 1 & 1 & 2.3E-4\\
+1E2 & 9 & 1.006 & 0.982 & 2.2E-2\\
+\textbf{1E3} & \textbf{21} & \textbf{1.008} & \textbf{0.940} & \textbf{2.2E-1}\\
+1E4 & 61 & 1.012 & 0.921 & 2.4\\
+1E5 & 173 & Erratic & Erratic & 22\\
+1E6 & 207 & Unstable & Unstable & 58\\
+\noalign{\smallskip}\hline
+\end{tabular}
+\end{center}
+\end{table}
+%
 
@@
 A sensitivity study on the number of neurons for the first hidden layer is carried out to select the ANN providing the best balance between CPU computation time and quality of the results.
-The study shows no influence on the forces when compared to the built-in Johnson-Cook model, only computation time is influenced (Table 3).
+The study shows no influence on the forces when compared to the built-in Johnson-Cook model, only computation time is influenced (Table \ref{tab:NbNeurons}).
 A first hidden layer with 9 neurons is therefore selected.
 
-\begin{figure}[h]
-\centering
-\caption{Tables 3 -- Sensitivity to the number of neurons of the first layer, $\zeta$ (selection in bold)}
-\includegraphics[width = 8cm]{Figures/Tab3}
-\label{Tab3}
-\end{figure}
+%
+\begin{table}[!h]
+\begin{center}
+\caption{\label{tab:NbNeurons} Sensitivity to the number of neurons of the first layer, $\zeta$
+(selection in bold)}
+\begin{tabular}{llll}
+\hline\noalign{\smallskip}
+$\zeta$  & Time increase (\%) & $\hat{F_c}$ & $\hat{F_f}$\\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Built-in & 0 & 1.000 & 1.000\\
+\textbf{9} & \textbf{6} & \textbf{1.000} & \textbf{0.999}\\
+11 & 6 & 1.001 & 1.000\\
+13 & 7 & 1.000 & 0.998\\
+15 & 8 & 1.001 & 1.001\\
+17 & 10 & 1.000 & 1.000\\
+\noalign{\smallskip}\hline
+\end{tabular}
+\end{center}
+\end{table}
+%
 
@@
 \centering
-\includegraphics{Figures/Fc}
-\caption{Comparison of experimental (E) and numerical (N) cutting forces}
-\label{Fc}
+\includegraphics{Figures/Fx_0}
+\caption{Comparison of experimental (E) and numerical (N) cutting forces at 0°}
+\label{Fx_0}
 \end{figure}
@@
 \centering
-\includegraphics{Figures/Ff}
-\caption{Comparison of experimental (E) and numerical (N) feed forces}
-\label{Ff}
+\includegraphics{Figures/Fx_6}
+\caption{Comparison of experimental (E) and numerical (N) cutting forces at 6°}
+\label{Fx_6}
 \end{figure}
@@
 \centering
-\includegraphics{Figures/Fp}
-\caption{Comparison of experimental (E) and numerical (N) passive forces}
-\label{Fp}
+\includegraphics{Figures/Fy_0}
+\caption{Comparison of experimental (E) and numerical (N) feed forces at 0°}
+\label{Fy_0}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\includegraphics{Figures/Fy_6}
+\caption{Comparison of experimental (E) and numerical (N) feed forces at 6°}
+\label{Fy_6}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\includegraphics{Figures/Fz_6}
+\caption{Comparison of experimental (E) and numerical (N) passive forces at 6°}
+\label{Fz_6}
 \end{figure}

### 2022-04-23 Article.tex
Set width of the figures in tex file
New figure + introduction in tex file
Introduction of a figure showing temporal evolutions of the forces. It is included in the tex file, but the corresponding text still needs to be written.
Update Article.tex
Revision of section 3, to be continued

@@
 Predictive performance of the model is high for the forces in the 3 directions and the chip thickness ratio on all 36 cutting conditions (including 2 inclination angles).
-Accuracy of the main cutting force is excellent: the mean difference with the experiments is 3%.
+Accuracy of the main cutting force is excellent: the mean difference with the experiments is 3\%.
 
@@
 \cite{arrazola_recent_2013}, most finite element (FE) models are developed in 2D (orthogonal cutting configuration usually) although industrial applications require a 3D modelling.
+
 The experimental configuration to validate a model must be as close as possible to the simulation.
@@
 Free oblique cutting with a straight cutting edge has not been studied yet: all the efforts have been focussing on orthogonal cutting (mostly for 2D validation).
+
 Lagrangian and Eulerian formulations are the most used for FE modelling of the cutting process.
@@
 They mostly cover (free) orthogonal cutting, while free oblique cutting still needs to be investigated.
+
 The behaviour of the machined material is one of the key aspects of a FE model \cite{arrazola_recent_2013, melkote_advances_2017}.
@@
 It uses optimisation or Artificial Intelligence based methods \cite{melkote_advances_2017}, such as in \cite{hardt_investigations_2021}, and requires defining the analytical expression of the constitutive model.
+
 This paper fills the literature gap on oblique cutting by investigating free orthogonal and oblique 3D cutting configurations from both the experimental and the numerical points of view.
@@
 A 3-axis GF Mikron VCE 600 Pro milling machine is used to carry out dry free orthogonal and oblique cutting tests on Ti6Al4V (grade 5 annealed at 750°C for 1 h followed by air cooling) with the same kinematics as a shaper.
-As shown in Figure 1, the tungsten carbide tool (modified LCGN160602-0600-FG, CP500 from SECO) is fixed on a dedicated holder (modified CFHN-06 from SECO) and the sample to be cut is clamped in the spindle (no rotation is allowed during the test).
+As shown in Figure \ref{ExpSetup}, the tungsten carbide tool (modified LCGN160602-0600-FG, CP500 from SECO) is fixed on a dedicated holder (modified CFHN-06 from SECO) and the sample to be cut is clamped in the spindle (no rotation is allowed during the test).
 The top of the sample includes 3 ribs of 1 mm in width (width of the tool is 6 mm) and 10 mm in length.
-The test consists of removing the upper layer (its height is the uncut chip thickness, h) of one rib at the prescribed cutting speed, $v_c$.
+The test consists of removing the upper layer (its height is the uncut chip thickness, $h$) of one rib at the prescribed cutting speed, $v_c$.
 The cutting speed is provided by the feed rate, $v_f$, of the machine (max.
@@
 \centering
-\includegraphics{Figures/ExpSetup}
+\includegraphics[width=\columnwidth]{Figures/ExpSetup}
 \caption{Experimental setup}
@@
 The CEL formulation is adopted to model the dry free orthogonal and oblique cutting tests with Abaqus/Explicit 2020.
-The 3D model is composed of a fixed Lagrangian tool and a Eulerian workpiece (Figure 2).
+The 3D model is composed of a fixed Lagrangian tool and a Eulerian workpiece (Figure \ref{BC}).
 Chip formation occurs by plastic flow across the Eulerian domain with no mesh distortion.
-No damage properties are necessary since continuous chips are formed, removing modelling assumptions.
+The Eulerian formulation enables to form chips without damage properties, removing modelling assumptions.
+These two characteristics contribute to cutting models providing accurate results and realistic chips \cite{ducobu_application_2016}.
 
@@
 \centering
-\includegraphics{Figures/BC}
+\includegraphics[width=\columnwidth]{Figures/BC}
 \caption{Boundary conditions and schematic initial geometry of the model}
@@
 
-As shown in Figure 3, the full width of the workpiece (1 mm) is modelled.
+As shown in Figure \ref{FEConfig}, the full width of the workpiece (1 mm) is modelled.
 To allow chip formation and side flow, the Eulerian domain is wider (it includes the volume in which material can move).
 The volume above the initial workpiece is also meshed with Eulerian elements for the same reasons.
-As in the experiments and to fulfil the hypothesis of free orthogonal and oblique cutting, the tool is wider than the workpiece.
-The models are the same for both inclination angles: they differ by the rotation of the tool of 6° about Y axis as in the experiments (Figure 3).
+As in the experiments and to fulfil the hypothesis of free orthogonal and oblique cutting, the tool is wider than the workpiece (it is of 1.1 mm in the model and of 6 mm in the experiments).
+It is very important to stress that the models are the same for both inclination angles: they only differ by the rotation of the tool of 6° about Y axis as in the experiments (Figure \ref{FEConfig}).
+This, coupled to the absence of assumptions when developing the models, contributes to make the models predictive.
 
@@
 \centering
-\includegraphics{Figures/FEConfig}
+\includegraphics[width=\columnwidth]{Figures/FEConfig}
 \caption{Configuration of the FE model for $\lambda_s$ = 6°}
@@
 To reduce computation time, the size of the model depends on the value of the uncut chip thickness.
-This results in a Eulerian domain (EC3D8RT elements) composed of 216,550 to 273,350 nodes and a Langrangian domain (C3D8T elements) of 4,650 nodes.
+This results in a Eulerian domain (EC3D8RT linear 3D Eulerian elements with 8 nodes, coupled mechanical-thermal behaviour and reduced integration) composed of 216,550 to 273,350 nodes and a Langrangian domain (C3D8T linear 3D Lagrangian elements with 8 nodes, coupled mechanical-thermal behaviour and reduced integration) of 4,650 nodes.
+
+The Ti6Al4V workpiece is assumed to be thermo-elasto-viscoplastic (isotropic) and inelastic heat fraction is 0.9.
 The tungsten carbide tool with TiN coating is assumed to be linear elastic.
-The Ti6Al4V workpiece is assumed to be thermo-elasto-viscoplastic (isotropic) and inelastic heat fraction is 0.9.
+Material properties are provided in Table \ref{tab:prop}.
+
+%
+\begin{table}[!h]
+\begin{center}
+\caption{\label{tab:prop} Materials properties \cite{Seo2004, Granta, Milosevic}}
+\begin{tabular}{lll}
+\hline\noalign{\smallskip}
+Young's modulus, $E$ (GPa) & Ti6Al4V & 113.8$^*$\\
+ & WC & 650\\
+Poisson's ratio, $\nu$ & Ti6Al4V & 0.34\\
+ & WC & 0.2\\
+Density, $\rho$ (kg/m$^3$) & Ti6Al4V & 4,430\\
+ & WC & 14,850\\
+Conductivity, $k$ (W/mK) & Ti6Al4V & 6.3$^*$\\
+ & WC & 100\\
+Expansion, $\alpha$ (K$^{-1}$) & Ti6Al4V & 8.6 e$^{-6*}$\\
+ & WC & 5 e$^{-6}$\\
+Specific heat, $c_{p}$ (J/KgK) & Ti6Al4V & 531$^*$\\
+ & WC & 202\\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+JC constitutive model & $A$ (MPa) & 997.9\\
+ & $B$ (MPa) & 653.1\\
+ & $C$ & 0.0198\\
+ & $m$ & 0.7\\
+ & $n$ & 0.45\\
+ & $\dot{\varepsilon}_{0}$ (s$^{-1}$) & 1\\
+ & $T_{\text{room}}$ (K) & 293\\
+ & $T_{\text{melt}}$ (K) & 1873\\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+\end{tabular}
+\end{center}
+\vspace{-0.4cm}$^*$: Dependence to the temperature, value provided at 293 K
+\end{table}
+%
+
 Following the experimental results of Rech et al.
-\cite{rech_characterisation_2013}, Coulomb’s friction is assumed to occur at the tool-workpiece interface and both friction and heat partition coefficients depend on the cutting speed; limiting shear stress is included.
+\cite{rech_characterisation_2013}, Coulomb's friction is assumed to occur at the tool-workpiece interface and both friction and heat partition coefficients depend on the cutting speed.
+Limiting shear stress is included + equa.
 All the friction energy is converted into heat.
+Table XX shows the friction parameters adopted in this study.
+
+%
+Table friction
+%
+
 Room temperature of 293 K is imposed on the upper and right surfaces of the tool and on the left and bottom surfaces of the workpiece (Figure 2).
@@
 \centering
-\includegraphics{Figures/Fx_0}
+\includegraphics[width=\columnwidth]{Figures/ExpNum_Forces_v10_40µ_6}
+\caption{Temporal evolutions of experimental (E) and numerical (N) forces at 6°, 10 m/min and 40 \textmu{}m: dispersion around mean experimental values and linear extrapolation of numerical values in dashed}
+\label{ExpNum_Forces_v10_40µ_6}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=\columnwidth]{Figures/Fx_0}
 \caption{Comparison of experimental (E) and numerical (N) cutting forces at 0°}
@@
 \centering
-\includegraphics{Figures/Fx_6}
+\includegraphics[width=\columnwidth]{Figures/Fx_6}
 \caption{Comparison of experimental (E) and numerical (N) cutting forces at 6°}
@@
 \centering
-\includegraphics{Figures/Fy_0}
+\includegraphics[width=\columnwidth]{Figures/Fy_0}
 \caption{Comparison of experimental (E) and numerical (N) feed forces at 0°}
@@
 \centering
-\includegraphics{Figures/Fy_6}
+\includegraphics[width=\columnwidth]{Figures/Fy_6}
 \caption{Comparison of experimental (E) and numerical (N) feed forces at 6°}
@@
 \centering
-\includegraphics{Figures/Fz_6}
+\includegraphics[width=\columnwidth]{Figures/Fz_6}
 \caption{Comparison of experimental (E) and numerical (N) passive forces at 6°}

### 2022-05-11 Article.tex
Update ANN

@@
 \usepackage{pgfplots}
+
+%\newcommand{\e}[1]{\exp\left({#1}\right)}
+\newcommand{\e}[1]{\mbox{\ensuremath{\mathrm{e}^{#1}}}}
+\DeclareMathOperator{\sigmoid}{sig}
 
@@
 
-The material constitutive model of Ti6Al4V used for all numerical simulations is a thermo-elasto-viscoplastic law using a flow criterion based on an ANN implemented in the Abaqus/Explicit code via a VUHARD Fortran routine as proposed by Pantalé et al.
+The constitutive model of the Ti6Al4V material used in all the numerical simulations proposed in section \ref{sec:ExpNumResults} is a thermo-elasto-viscoplastic law using a flow criterion based on an artificial neural network (ANN) identified for the selected material and implemented in the Abaqus/Explicit code via a Fortran routine VUHARD as proposed by Pantalé et al.
 in \cite{pantale_efficient_2022}.
-Several neural network architectures are tested, for the metal cutting simulations, having 2 hidden layers with a variable number of neurons for the first hidden layer ($\zeta$ = 9 to 17) and 7 neurons for the second hidden layer, 3 inputs (plastic strain, $\varepsilon^p$, plastic strain rate, ${\dot{\varepsilon}}^p$, and temperature, T) and one output (the yield stress, $\sigma^y$).
-The global architecture of this kind of ANN is given in Figure 4.
+The principle of this approach consists in replacing the analytical formulation of the flow law, based on a Johnson-Cook or Zerilli-Armstrong type model, and allowing the calculation of the flow stress $\sigma^y$ as a function of the plastic strain $\varepsilon^p$, of the plastic strain rate, ${\dot{\varepsilon}}^p$, and of the temperature $T$, by a multi-layer ANN serving as universal approximator.
+Thus, we can directly identify the parameters of the neural network from the experimental data without having to postulate a behavioural model, which simplifies the procedure and allows more flexibility in the definition of the model.
+The proposed approach also allows, as shown in Pantalé et al.
+\cite{pantale_efficient_2022}, to compute the derivatives of the flow stress $\sigma^y$ with respect to the three input variables of the model, a necessary step to implement this model as a flow law in the form of a VUHARD subroutine in the Abaqus/Explicit FEM code.
+
+In order to verify the influence of the complexity of the neural network on the numerical results of the simulation and the computing time, several architectures of ANN are tested thereafter.
+The chosen global architecture has 2 hidden layers with a variable number of neurons for the first hidden layer ($\zeta$ = 9 to 17) and 7 neurons for the second hidden layer, 3 inputs (plastic strain, $\varepsilon^p$, plastic strain rate, ${\dot{\varepsilon}}^p$, and temperature, T) and one output (the yield stress, $\sigma^y$).
+The global architecture of this kind of ANN is given in Figure \ref{ANN}.
 
@@
 
-A Sigmoid activation function is used for all neurons in the two hidden layers.
-Because of the large number of parameters (from 122 to 210 for 9 and 17 neurons for the first hidden layer, respectively); the 5 sets of ANN parameters are provided in \cite{pantale_coefficients_2022}.
+A Sigmoid activation function defined by equation (\ref{eq:sigmoid}) is used for all neurons in the two hidden layers, but none is used for the output neuron.
+\begin{equation}
+\sigmoid(x)=\frac{1}{1 + \e{-x}}\label{eq:sigmoid}
+\end{equation}
+Because of the large number of identified parameters for the whole ANN model (from 122 to 210 for 9 and 17 neurons for the first hidden layer, respectively); the 5 sets of ANN parameters used in this publication are provided in \cite{pantale_coefficients_2022}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Experimental and numerical results}
+\section{Experimental and numerical results\label{sec:ExpNumResults}}
 \label{Results}

### 2022-05-12 Article.tex
Add Appendix A and details about ANN

@@
 \usepackage{pgfplots}
+\usepackage{accents}
 
@@
 \DeclareMathOperator{\sigmoid}{sig}
+\newcommand{\lay}[1]{^{(#1)}}
+\newcommand{\dotp}{\boldsymbol{\cdot}}
+\newcommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
+\newcommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
 
@@
 In order to verify the influence of the complexity of the neural network on the numerical results of the simulation and the computing time, several architectures of ANN are tested thereafter.
-The chosen global architecture has 2 hidden layers with a variable number of neurons for the first hidden layer ($\zeta$ = 9 to 17) and 7 neurons for the second hidden layer, 3 inputs (plastic strain, $\varepsilon^p$, plastic strain rate, ${\dot{\varepsilon}}^p$, and temperature, T) and one output (the yield stress, $\sigma^y$).
-The global architecture of this kind of ANN is given in Figure \ref{ANN}.
+The chosen global architecture has 2 hidden layers with a variable number of neurons for the first hidden layer ($\zeta$ = 9 to 17) and 7 neurons for the second hidden layer, 3 inputs (plastic strain, $\varepsilon^p$, plastic strain rate, ${\dot{\varepsilon}}^p$, and temperature, $T$) and one output (the yield stress, $\sigma^y$).
+The global architecture of this kind of ANN is given in Figure \ref{ANN} for 9 neurons in the first hidden layer.
+Conforming to Pantalé et al.
+\cite{pantale_efficient_2022}, this ANN is referred after the terminology ANN 3-9-7-1-sig, because it has 3 inputs, 9 neurons in the first hidden layer, 7 neurons in the second hidden layer, 1 output and a sigmoid activation function.
 
@@
 
-A Sigmoid activation function defined by equation (\ref{eq:sigmoid}) is used for all neurons in the two hidden layers, but none is used for the output neuron.
+The main advantage of this approach (the use of an ANN), after the training phase, is that the output $\sigma^y$ of the network is related to the inputs $\varepsilon^p$, ${\dot{\varepsilon}}^p$, and $T$ through equations (\ref{eq:ANN-preprocess}) to (\ref{eq:ANN-vonMises}).
+The first step is to scale the input data to the interval $[0,1]$ using the following equation:
+
+\begin{equation}
+\overrightarrow{x} =
+\begin{cases}
+x_1 = \frac{\varepsilon^p - [\varepsilon^p]_{min}}{[\varepsilon^p]_{max} - [\varepsilon^p]_{min}}\\
+x_2 = \frac{\ln(\mdot{\varepsilon}^p)-[\ln(\mdot{\varepsilon}^p)]_{min}}{[\ln(\mdot{\varepsilon}^p)]_{max}-[\ln(\mdot{\varepsilon}^p)]_{min}}\label{eq:ANN-preprocess}\\
+x_3 = \frac{T-[T]_{min}}{[T]_{max}-[T]_{min}}
+\end{cases}
+\end{equation}
+
+The output of the neurons in the first hidden layer are given by the following equation:
+
+\begin{equation}
+\overrightarrow{y_1} = \sigmoid\left(\w_1 \dotp \overrightarrow{x}+ \overrightarrow{b_1}\right)\label{eq:ANN-y1}
+\end{equation}
+where, a $\sigmoid()$ is the sigmoid activation function defined by equation (\ref{eq:sigmoid}).
 \begin{equation}
@@
 \end{equation}
-Because of the large number of identified parameters for the whole ANN model (from 122 to 210 for 9 and 17 neurons for the first hidden layer, respectively); the 5 sets of ANN parameters used in this publication are provided in \cite{pantale_coefficients_2022}.
+
+Then, the output of the neurons in the second hidden layer are given by equation (\ref{eq:ANN-y2}).
+\begin{equation}
+\overrightarrow{y_2} = \sigmoid\left(\w_2 \dotp \overrightarrow{y_1}+ \overrightarrow{b_2}\right)\label{eq:ANN-y2}
+\end{equation}
+
+So, that, the output of the ANN is therefore given by equation (\ref{eq:ANN-vonMises}).
+\begin{equation}
+\sigma =  \left([\sigma]_{max}-[\sigma]_{min}\right) \left(\overrightarrow{w}^T \dotp \overrightarrow{y_2} + b\right) + [\sigma]_{min} \label{eq:ANN-vonMises}
+\end{equation}
+
+In equations (\ref{eq:ANN-preprocess}) to (\ref{eq:ANN-vonMises}), quantities $\w_1$, $\w_2$, $\overrightarrow{w}$, $\overrightarrow{b_1}$, $\overrightarrow{b_2}$ and $b$ are given by the training procedure of the ANN.
+Corresponding values for an ANN containing 9 neurons in the first hidden layer are reported in \ref{sec:appendix-1}.
+Quantities $[\ ]_{min}$ and $[\ ]_{max}$  are the boundaries of the range of the corresponding field during the training phase, values are also given in \ref{sec:appendix-1}.
+
+Because of the large number of identified parameters for all the ANN models (from 114 to 202 for 9 and 17 neurons for the first hidden layer, respectively); the other 4 sets of ANN parameters used in this publication can be found in \cite{pantale_coefficients_2022}.
 
@@
 %%% appendix sections are then done as normal sections
-%%% \appendix
+\appendix
 %
+\section{Coefficients of the ANN 3-9-7-1-sig\label{sec:appendix-1}}
+
+In this Appendix, we present the values obtained after the training phase of an ANN containing 9 neurons in the first hidden layer and 7 neurons in the second hidden layer.
+
+The training of the neural network was performed using a data set containing $3\,430$ data points defined by:
+\begin{itemize}
+\item $70$ values for $\varepsilon^p\in[0.0,3.0]$, so that $[\varepsilon^p]_{min}=0$ and $[\varepsilon^p]_{max}=3$.
+\item $7$ plastic strain rates $\mdot{\varepsilon}^p\in[1, 10, 50, 500, 5\,000, 50\,000, 500\,000]$, so that $[\ln(\mdot{\varepsilon}^p)]_{min}=0$ and $[\ln(\mdot{\varepsilon}^p)]_{max}=13.12236$.
+\item  $7$ temperatures $T\in[293, 400, 500, 700, 900, 1\,200, 1\,500]$, so that $[T]_{min}=293$ and $[T]_{max}=1\ 500$.
+\end{itemize}
+
+Stresses in the training dataset ranges from $[\sigma]_{min}=171.44$ to $[\sigma]_{max}=2606.12$.
+The results of the training process are given below for quantities $\w_1$, $\w_2$, $\overrightarrow{w}$, $\overrightarrow{b_1}$, $\overrightarrow{b_2}$ and $b$.
+
+\begin{equation*}
+\w_1=\left[
+\begin{array}{rrr}
+ -0.87229 & -0.47675 & -1.50771\\
+ -0.95762 & -0.25619 &  1.65222\\
+ -10.61660 &  0.22003 & -0.11539\\
+  3.67883 &  0.37146 & -1.51069\\
+ -63.39468 &  0.15466 & -0.95431\\
+  0.54807 &  0.25959 & -5.44355\\
+ -1.33883 &  0.36089 & -1.66735\\
+ -0.68125 &  1.02121 &  0.34242\\
+  0.08740 &  0.18764 & -41.32542
+\end{array}\right]
+\end{equation*}
+
+\begin{equation*}
+\w_2^T=\left[
+\begin{array}{rrrrrrrrr}
+  1.66285 & -0.59645 & -3.17333 &  0.20706 &  1.18760 &  2.01250 & -0.82147\\
+ -0.26237 & -2.50330 & -1.45941 & -1.59833 &  4.05169 & -1.21146 &  1.05610\\
+ -0.12958 &  0.67119 & -5.85989 & -2.55061 &  4.85245 &  4.31876 &  3.24070\\
+ -2.12890 &  0.68296 &  0.71183 &  0.81706 & -0.09405 &  0.34919 & -1.41223\\
+  2.33631 & -0.08089 &  14.65789 &  0.12531 &  23.66363 &  2.55872 &  2.15338\\
+  0.11567 &  1.77629 & -1.80448 &  0.77825 & -1.58254 &  1.90442 &  1.23152\\
+  1.49265 &  0.41821 & -3.53803 & -0.48705 & -0.23671 &  0.75887 & -0.37441\\
+  0.95990 &  0.69041 &  0.43870 &  0.28393 & -1.40101 & -0.64569 & -0.38964\\
+  5.89937 & -0.13015 &  2.99264 &  1.78534 & -3.90189 &  1.17494 & -3.78854
+\end{array}\right]
+\end{equation*}
+
+\begin{equation*}
+\overrightarrow{w}=\left[
+\begin{array}{r}
+  0.34701\\
+  1.42079\\
+ -0.96564\\
+  0.62467\\
+ -0.56322\\
+  0.40960\\
+ -0.42810
+\end{array}\right]
+\end{equation*}
+
+\begin{equation*}
+\overrightarrow{b_1}=\left[
+\begin{array}{r}
+  2.57141\\
+  0.22673\\
+ -1.16985\\
+ -0.11246\\
+ -0.82210\\
+ -2.13264\\
+  0.78794\\
+  1.20434\\
+ -3.48681
+\end{array}\right]
+\end{equation*}
+
+\begin{equation*}
+\overrightarrow{b_2}=\left[
+\begin{array}{r}
+ -0.36566\\
+ -1.14445\\
+ -0.79065\\
+ -0.50670\\
+  1.30136\\
+  0.04521\\
+ -0.29995
+\end{array}\right]
+\end{equation*}
+
+\begin{equation*}
+b=0.04213
+\end{equation*}
+
 %%% \section{}

### 2022-09-12 Article.tex
Addition of 1st comments to complete article and suppression of figures of tables
Revision and comment up to line 208 (pdf)

@@
 \usepackage{textcomp} %Permet d'introduire un mu droit à l'aide de \textmu en dehors de l'environnement math
-\usepackage{color}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% To insert highlighted comments with author's name
+% Adapted from https://www.willusher.io/latex/2018/07/10/comments-in-latex
+\usepackage{soul} %Can also be used to highlight text with \hl{highlighted text}
+\usepackage{color}
+\definecolor{VWpink}{RGB}{255,113,206} % VaporWave color palette
+\definecolor{VWblue}{RGB}{1,205,254} % VaporWave color palette
+\definecolor{VWgreen}{RGB}{5,255,161} % VaporWave color palette
+\definecolor{VWviolet}{RGB}{185,103,255} % VaporWave color palette
+\definecolor{VWyellow}{RGB}{255,251,150} % VaporWave color palette
+% We also use DeclareRobustCommand instead of
+% NewCommand so that the command will work in captions
+% and other contexts as well.
+\DeclareRobustCommand{\FD}[1]{ {\begingroup\sethlcolor{VWgreen}\textcolor{black}{\hl{[FD:] #1}}\endgroup} }
+\DeclareRobustCommand{\OP}[1]{ {\begingroup\sethlcolor{VWblue}\textcolor{black}{\hl{[OP:] #1}}\endgroup} }
+% The highlight comment command can then be used in the text: \FD{This is an example comment!}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \journal{CIRP Journal of Manufacturing Science and Technology}
@@
 
-\title{Predictive 3D modelling of free oblique cutting of Ti6Al4V titanium alloy and experimental validation for a wide range of conditions}
+\title{Predictive 3D modelling of free oblique cutting of Ti6Al4V titanium alloy and experimental validation for a wide range of conditions\\ \FD{Include AI?}}
 
@@
 Accuracy of the main cutting force is excellent: the mean difference with the experiments is 3\%.
+
+\FD{Review and update}
 
@@
 
-Selection of the tools and the cutting conditions in machining, but also comprehension of the influence of the process parameters on the quality of a component and its optimisation, are still difficult to achieve because of the high level of complexity and linked nonlinear involved phenomena.
+Selection of the tools and the cutting conditions in machining, but also comprehension of the influence of the process parameters on the quality of a component and its optimisation, are still difficult to achieve because of the high level of complexity and linked nonlinear phenomena.
 In the frame of digital manufacturing and Industry 4.0, modelling of the cutting process supports them, while remaining a challenging task.
@@
 
-The experimental configuration to validate a model must be as close as possible to the simulation.
+\FD{Include info from lit.
+rev.
+CIRP GA v6 from here...}The experimental configuration to validate a model must be as close as possible to the simulation.
 Few configurations in strictly orthogonal cutting conditions are found.
@@
 The empirical Johnson-Cook (JC) model \cite{johnson_constitutive_1983} is still the most used so far.
-One issue of material behaviour modelling for cutting simulation is the identification of the model parameters, moreover as the experimental equipment does not allow to reach the high levels of strains, strain rates and temperature of machining \cite{melkote_advances_2017}.
-Inverse identification is an alternative, but the uniqueness of the solution is not always guaranteed \cite{arrazola_recent_2013}.
-It uses optimisation or Artificial Intelligence based methods \cite{melkote_advances_2017}, such as in \cite{hardt_investigations_2021}, and requires defining the analytical expression of the constitutive model.
+\FD{Add JC equa here with OP's notation + com} One issue of material behaviour modelling for cutting simulation is the identification of the model parameters, moreover as the experimental equipment does not allow to reach the high levels of strains, strain rates and temperature of machining \cite{melkote_advances_2017}.
+\FD{Add info for inverse identification from CMMO: Klocke, etc.} Inverse identification is an alternative, but the uniqueness of the solution is not always guaranteed \cite{arrazola_recent_2013}.
+It uses optimisation or Artificial Intelligence based methods \cite{melkote_advances_2017}, such as in \cite{hardt_investigations_2021}, and requires defining the analytical expression of the constitutive model.\FD{...
+to here}
 
@@
 A broad range of cutting speeds (6), uncut chip thicknesses (3) and inclination angles (2) resulting in 36 different conditions are considered to demonstrate the predictive ability of the FE model for fundamental variables.
-No assumptions are made about the geometry of the machined workpiece in the model (i.e.
+No assumption is made about the geometry of the machined workpiece in the model (i.e.
 its width is the same as in the experiments), while keeping computation time relevant for industrial applications.
@@
 value of 40 m/min).
-The tool cutting edge inclination, $\lambda_s$, results from the orientation of the tool and the sample.
+The tool cutting edge inclination, $\lambda_s$, results from the relative orientation of the tool and the sample.
 Forces are measured with a 3-component Kistler 9257B dynamometer and are amplified by a Kistler 5070A charge amplifier.
@@
 Table \ref{tab:CutCond} shows the cutting conditions, each is repeated 3 times.
+\FD{Add infos valeur effort: mean, filter, etc.
++ get info from section 4}
 
@@
 Uncut chip thickness, $h$ (\textmu{}m) & 40, 60, 80\\
-Cutting edge inclination, $\lambda_s$ & 0, 6\\
+Cutting edge inclination, $\lambda_s$ (\textdegree{}) & 0, 6\\
 Width of the workpiece (mm) & 1\\
@@
 To reduce computation time, the size of the model depends on the value of the uncut chip thickness.
-This results in a Eulerian domain (EC3D8RT linear 3D Eulerian elements with 8 nodes, coupled mechanical-thermal behaviour and reduced integration) composed of 216,550 to 273,350 nodes and a Langrangian domain (C3D8T linear 3D Lagrangian elements with 8 nodes, coupled mechanical-thermal behaviour and reduced integration) of 4,650 nodes.
+This results in a Eulerian domain (EC3D8RT linear 3D Eulerian elements with 8 nodes, coupled mechanical-thermal behaviour and reduced integration) composed of 216,550 to 273,350 nodes and a Langrangian domain (C3D8T linear 3D Lagrangian elements with 8 nodes, coupled mechanical-thermal behaviour) of 4,650 nodes.
 
@@
 JC constitutive model & $A$ (MPa) & 997.9\\
- & $B$ (MPa) & 653.1\\
+\FD{Comment this choice of JC para} & $B$ (MPa) & 653.1\\
  & $C$ & 0.0198\\
@@
 \cite{rech_characterisation_2013}, Coulomb's friction is assumed to occur at the tool-workpiece interface and both friction and heat partition coefficients depend on the cutting speed.
-Limiting shear stress is included + equa.
+\hl{Limiting shear stress is included + equa.
 All the friction energy is converted into heat.
-Table XX shows the friction parameters adopted in this study.
+Table XX shows the friction parameters adopted in this study.}
 
 %
-Table friction
+\hl{Table friction}
 %
@@
 Initial temperature of the tool and the workpiece is set to room temperature (293 K).
+\hl{+ info coefficients}
 
@@
 
-The constitutive model of the Ti6Al4V material used in all the numerical simulations proposed in section \ref{sec:ExpNumResults} is a thermo-elasto-viscoplastic law using a flow criterion based on an artificial neural network (ANN) identified for the selected material and implemented in the Abaqus/Explicit code via a Fortran routine VUHARD as proposed by Pantalé et al.
+The constitutive model of the Ti6Al4V material used in all the numerical simulations proposed in section \ref{sec:ExpNumResults} is a thermo-elasto-viscoplastic law using a flow criterion based on an ANN identified for the selected material and implemented in the Abaqus/Explicit code via a Fortran routine VUHARD as proposed by Pantalé et al.
 in \cite{pantale_efficient_2022}.
 The principle of this approach consists in replacing the analytical formulation of the flow law, based on a Johnson-Cook or Zerilli-Armstrong type model, and allowing the calculation of the flow stress $\sigma^y$ as a function of the plastic strain $\varepsilon^p$, of the plastic strain rate, ${\dot{\varepsilon}}^p$, and of the temperature $T$, by a multi-layer ANN serving as universal approximator.
-Thus, we can directly identify the parameters of the neural network from the experimental data without having to postulate a behavioural model, which simplifies the procedure and allows more flexibility in the definition of the model.
+Thus, the parameters of the neural network can directly be identified from the experimental data without having to postulate a behavioural model, which simplifies the procedure and allows more flexibility in the definition of the model.
 The proposed approach also allows, as shown in Pantalé et al.
@@
 
-In order to verify the influence of the complexity of the neural network on the numerical results of the simulation and the computing time, several architectures of ANN are tested thereafter.
+In order to verify the influence of the complexity of the neural network on the numerical results of the simulation and the computing time, several architectures of ANN are tested thereafter (in \ref{subsec:nberneu}).
 The chosen global architecture has 2 hidden layers with a variable number of neurons for the first hidden layer ($\zeta$ = 9 to 17) and 7 neurons for the second hidden layer, 3 inputs (plastic strain, $\varepsilon^p$, plastic strain rate, ${\dot{\varepsilon}}^p$, and temperature, $T$) and one output (the yield stress, $\sigma^y$).
@@
 
-The output of the neurons in the first hidden layer are given by the following equation:
+The outputs of the neurons in the first hidden layer are given by the following equation:
 
@@
 \end{equation}
-where, a $\sigmoid()$ is the sigmoid activation function defined by equation (\ref{eq:sigmoid}).
+where, $\sigmoid()$ is the sigmoid activation function defined by equation (\ref{eq:sigmoid}):
 \begin{equation}
@@
 
-Then, the output of the neurons in the second hidden layer are given by equation (\ref{eq:ANN-y2}).
+Then, the output of the neurons in the second hidden layer are given by equation (\ref{eq:ANN-y2}):
 \begin{equation}
@@
 
-So, that, the output of the ANN is therefore given by equation (\ref{eq:ANN-vonMises}).
+So, \FD{Olivier: remove?}\hl{that,} the output of the ANN is therefore given by equation (\ref{eq:ANN-vonMises}).
 \begin{equation}
@@
 
-Because of the large number of identified parameters for all the ANN models (from 114 to 202 for 9 and 17 neurons for the first hidden layer, respectively); the other 4 sets of ANN parameters used in this publication can be found in \cite{pantale_coefficients_2022}.
+Because of the large number of identified parameters for all the ANN models (from 114 to 202 for 9 and 17 neurons for the first hidden layer, respectively); the other 4 sets of ANN parameters used in this publication can be found in \cite{pantale_coefficients_2022}.\FD{Inclure dans corps du texte puisque article normal?}
 
@@
 Mass scaling (MS) is introduced in the model to reduce the CPU computation time while checking that it does not influence the results (forces and energies) via a mass scaling sensitivity study.
-MS factors, ${MS}_f$, ranging from 1E6 (theoretical scaling of CPU time of 1000) to 1 (no scaling) have been used for one cutting condition ($\lambda_s$ = 0°, $v_c$ = 30 m/min and h = 60 µm).
-Table \ref{tab:MS} gives the results normalised ($\hat{x}$) by these of the model without MS (x).
-As expected, actual speed-up does not increase linearly with the ${MS}_f$, but it is still significant.
+MS factors, ${MS}_f$, ranging from 1E6 (theoretical scaling of CPU time of 1000\FD{sqrt MSF}) to 1 (no scaling) have been used for one cutting condition ($\lambda_s$ = 0°, $v_c$ = 30 m/min and $h$ = 60 µm).
+Table \ref{tab:MS} gives the results normalised ($\hat{x}$) by these of the model without MS \hl{(x)}.\FD{+ equa and explain that effort is mean, filtered, etc.} As expected, actual speed-up does not increase linearly with the ${MS}_f$, but it is still significant.
 ${MS}_f$ of 1E6 leads to unstable computation and ${MS}_f$ of 1E5 results in erratic forces evolutions.
 These results are confirmed by high values of the kinetic ($KE$) on internal ($IE$) energies ratio (it should not exceed a few \%).
-A ${MS}_f$ value of 1E3 is selected as it provides a good balance between computation time reduction and impact on forces (considered in the analysis), while keeping $\frac{KE}{IE}$ below 1\%.
-To provide an order of magnitude of CPU computation time, between 10 h and 50 h are needed on 4 cores of an Intel i7-5700 HQ at 3.48 GHz.
+A ${MS}_f$ value of 1E3 is selected as it provides a good balance between computation time reduction and impact on forces, while keeping $\frac{KE}{IE}$ below 1\%.
+To provide an order of magnitude of CPU computation time, between 10 h and 50 h (depending on the value of $h$) are needed on 4 cores of an Intel i7-5700HQ CPU at 2.7 -- 3.5 GHz.
 
@@
 \subsection{Sensitivity study of the results to the number of neurons}
+\label{subsec:nberneu}
 

### 2022-09-14 Article.tex
Revision and comments for the rest of the paper
Now, I need to review the paper according to my comments

@@
 \FD{Add infos valeur effort: mean, filter, etc.
-+ get info from section 4}
++ get info from section 4: Experimental and numerical forces are filtered with a second-order low-pass Bessel filter at 750 Hz before computing the mean value of the signal at steady state.}
 
@@
 \begin{center}
-\caption{\label{tab:MS} MS sensitivity study (selected $MS_f$ in bold)}
+\caption{\label{tab:MS} MS sensitivity study (selected $MS_f$ in bold)}\FD{Define $\hat{F_c}$, etc. in caption}
 \begin{tabular}{lllll}
@@
 A sensitivity study on the number of neurons for the first hidden layer is carried out to select the ANN providing the best balance between CPU computation time and quality of the results.
-The study shows no influence on the forces when compared to the built-in Johnson-Cook model, only computation time is influenced (Table \ref{tab:NbNeurons}).
-A first hidden layer with 9 neurons is therefore selected.
+The results of the study are provided in Table \ref{tab:NbNeurons}.
+They show no influence on the forces when compared to the built-in Johnson-Cook model, only computation time is influenced.
+A first hidden layer with 9 neurons is therefore selected as it leads to the lowest CPU computation time increase.
 
@@
 \begin{center}
-\caption{\label{tab:NbNeurons} Sensitivity to the number of neurons of the first layer, $\zeta$
-(selection in bold)}
+\caption{\label{tab:NbNeurons} Sensitivity of the forces to the number of neurons of the first layer, $\zeta$
+(selection in bold)}\FD{Define $\hat{F_c}$, etc. in caption}
 \begin{tabular}{llll}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Experimental and numerical forces are filtered with a second-order low-pass Bessel filter at 750 Hz before computing the mean value of the signal at steady state.
-Mean and standard deviation ($2\sigma$) are computed from the 3 experimental values and are shown in Figures 5 to 7.
-Mean numerical values are plotted inside the experimental bars in Figures 5 to 7.
+\FD{Show chips? + info on side flow? + dedicated subsection on chip thickness?}
+Mean and standard deviation ($2\sigma$) are computed from the 3 experimental values and are shown in Figures \hl{5 to 7}.
+Mean numerical values are plotted inside the experimental bars in Figures \hl{5 to 7}.
+\FD{sigma deja utilise mais equa (5) devrait etre sigma y - voir avec Olivier}
 
@@
 \includegraphics[width=\columnwidth]{Figures/ExpNum_Forces_v10_40µ_6}
-\caption{Temporal evolutions of experimental (E) and numerical (N) forces at 6°, 10 m/min and 40 \textmu{}m: dispersion around mean experimental values and linear extrapolation of numerical values in dashed}
+\caption{Temporal evolutions of experimental (E) and numerical (N) forces at 6°, 10 m/min and 40 \textmu{}m: dispersion around mean experimental values and linear extrapolation of numerical values in dashed}\FD{Style of legend different than text}
 \label{ExpNum_Forces_v10_40µ_6}
@@
 \includegraphics[width=\columnwidth]{Figures/Fx_0}
-\caption{Comparison of experimental (E) and numerical (N) cutting forces at 0°}
+\caption{Comparison of experimental (E) and numerical (N) cutting forces at 0°}\FD{Better explain legend in caption, same for other figures}
 \label{Fx_0}
@@
 
+\FD{Check clearly stated that Ff trend is globally NOK: improve friction and mat para also cf. Metals Kuga + increase with h quite low in the exp.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\FD{Add biblio}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The training of the neural network was performed using a data set containing $3\,430$ data points defined by:
+The training of the neural network was performed using a data set containing $3\,430$ data points defined by: \FD{Add units for min and max values?}
 \begin{itemize}
@@
 Stresses in the training dataset ranges from $[\sigma]_{min}=171.44$ to $[\sigma]_{max}=2606.12$.
-The results of the training process are given below for quantities $\w_1$, $\w_2$, $\overrightarrow{w}$, $\overrightarrow{b_1}$, $\overrightarrow{b_2}$ and $b$.
+The results of the training process are given below for quantities $\w_1$, $\w_2$, $\overrightarrow{w}$, $\overrightarrow{b_1}$, $\overrightarrow{b_2}$ and $b$.\FD{sigma y?}
 

### 2022-09-17 Article.tex
Update of fig. temporal evolution of forces

@@
 \includegraphics[width=\columnwidth]{Figures/ExpNum_Forces_v10_40µ_6}
-\caption{Temporal evolutions of experimental (E) and numerical (N) forces at 6°, 10 m/min and 40 \textmu{}m: dispersion around mean experimental values and linear extrapolation of numerical values in dashed}\FD{Style of legend different than text}
+\caption{Temporal evolutions of experimental (E) and numerical (N) forces at 6°, 10 m/min and 40 \textmu{}m: dispersion around mean experimental values and linear extrapolation of numerical values in dashed}
 \label{ExpNum_Forces_v10_40µ_6}

### 2022-09-21 Article.tex
Revision up to section 3 included
- Revision of the text up to section 3 included
- updated references
- 2 new figures

@@
-%\documentclass[preprint,12pt,times]{elsarticle}
+\documentclass[preprint,12pt,times]{elsarticle}
 
@@
 %% \documentclass[final,5p,times]{elsarticle}
- \documentclass[final,5p,times,twocolumn]{elsarticle}
+% \documentclass[final,5p,times,twocolumn]{elsarticle}
 
@@
 
-\usepackage[leftbars]{changebar} %Pour insérer une barre de mise à  jour (à  gauche car [leftbars]) au moyen de \begin{changebar} %Ne fonctionne pas pour passer du DVI au pdf -> utiliser DV -> PS -> pdf
+%\usepackage[leftbars]{changebar} %Pour insérer une barre de mise à  jour (à  gauche car [leftbars]) au moyen de \begin{changebar} %Ne fonctionne pas pour passer du DVI au pdf -> utiliser DV -> PS -> pdf %Ne fontionne pas avec figure* et table*
 
@@
 \usepackage{accents}
+
+\usepackage{dblfloatfix} % fix for bottom-placement of figure*
 
@@
 As highlighted by Arrazola et al.
-\cite{arrazola_recent_2013}, most finite element (FE) models are developed in 2D (orthogonal cutting configuration usually) although industrial applications require a 3D modelling.
+\cite{arrazola_Recent_2013}, most finite element (FE) models are developed in 2D (orthogonal cutting configuration usually) although industrial applications require a 3D modelling.
 
-\FD{Include info from lit.
-rev.
-CIRP GA v6 from here...}The experimental configuration to validate a model must be as close as possible to the simulation.
-Few configurations in strictly orthogonal cutting conditions are found.
-Broaching \cite{abouridouane_friction_2021} or milling \cite{sela_measurement_2021, ducobu_experimental_2015} machines are mostly used; dedicated machines such as in \cite{afrasiabi_numerical-experimental_2021} allow for high cutting speed.
+Experimental validation of a model is a crucial step in the modelling of the cutting process.
+The experimental configuration must be as close as possible to the simulation.
+For orthogonal cutting validation, a rotating movement usually generates the cutting speed.
+This is often achieved in turning \cite{agmell_Development_2018} or in milling \cite{xu_Simulation_2021} and the diameter of the rotating part must be large enough to reduce the influence of the curvature on the results.
+Experimental configurations in strictly orthogonal cutting conditions are less often adopted, for example, in broaching \cite{abouridouane_Friction_2021} or milling \cite{ducobu_Experimental_2015, sela_Measurement_2021} machines.
+While they remove assumptions linked to the rotating cutting movement, they usually allow for lower cutting speeds (except on a dedicated machine, such as in Afrasiabi et al.
+\cite{afrasiabi_NumericalExperimental_2021}).
 Free oblique cutting with a straight cutting edge has not been studied yet: all the efforts have been focussing on orthogonal cutting (mostly for 2D validation).
@@
 Lagrangian and Eulerian formulations are the most used for FE modelling of the cutting process.
-The Coupled Eulerian-Lagrangian (CEL) formulation has recently been successfully applied to the modelling of cutting (2D orthogonal configuration): it provides accurate results with a realistic chip shape and no mesh distortion \cite{ducobu_application_2016}.
-First applications in 3D are found in recent works \cite{xu_simulation_2021, ducobu_finite_2017, ambrosio_new_2022, vovk_finite_2020, hardt_three_2021}.
-They mostly cover (free) orthogonal cutting, while free oblique cutting still needs to be investigated.
+Combinations of formulations, such as Arbitrary Lagrangian-Eulerian (ALE) and Coupled Eulerian-Lagrangian (CEL) are increasingly used to avoid (or reduce) mesh distortions \cite{ducobu_Application_2016}.
+The Coupled Eulerian-Lagrangian (CEL) formulation has recently been successfully applied to the modelling of cutting (2D orthogonal configuration): it provides accurate results with a realistic chip shape and no mesh distortion \cite{ducobu_Application_2016}.
+First applications in 3D are found in recent works \cite{xu_Simulation_2021, ducobu_Finite_2017, ambrosio_New_2022, vovk_Finite_2020, hardt_Three_2021}.
+They cover (free) orthogonal cutting or a simple 3D operation, while free oblique cutting still needs to be investigated.
 
-The behaviour of the machined material is one of the key aspects of a FE model \cite{arrazola_recent_2013, melkote_advances_2017}.
-Research is very intense in this field, which leads to a growing number of material constitutive models ranging from empirical to physical models \cite{melkote_advances_2017}.
-The empirical Johnson-Cook (JC) model \cite{johnson_constitutive_1983} is still the most used so far.
-\FD{Add JC equa here with OP's notation + com} One issue of material behaviour modelling for cutting simulation is the identification of the model parameters, moreover as the experimental equipment does not allow to reach the high levels of strains, strain rates and temperature of machining \cite{melkote_advances_2017}.
-\FD{Add info for inverse identification from CMMO: Klocke, etc.} Inverse identification is an alternative, but the uniqueness of the solution is not always guaranteed \cite{arrazola_recent_2013}.
-It uses optimisation or Artificial Intelligence based methods \cite{melkote_advances_2017}, such as in \cite{hardt_investigations_2021}, and requires defining the analytical expression of the constitutive model.\FD{...
-to here}
+The behaviour of the machined material is one of the key aspects of a FE model \cite{arrazola_Recent_2013, melkote_Advances_2017}.
+Research is very intense in this field, which leads to a growing number of material constitutive models ranging from empirical to physical models, some including microstructure effects \cite{melkote_Advances_2017}.
+The thermo-elasto-viscoplastic empirical model of Johnson-Cook (JC) \cite{johnson_Constitutive_1983} is still the most used so far:
+%
+\begin{equation}\label{eq:J-C}
+	\sigma^{y} = \left(A + B\ \varepsilon^{p^n} \right) \left(1 + C\ \ln\frac{{\dot{\varepsilon}}^p}{\dot{\varepsilon}_{0}^{p}}\right) \left(1 - \left[\frac{T - T_{\text{room}}}{T_{\text{melt}} - T_{\text{room}}}\right]^{m}\right)
+\end{equation}
+%
+The flow stress, $\sigma^{y}$, is a function of the plastic strain, $\varepsilon^{p}$, of the plastic strain rate, ${\dot{\varepsilon}}^{p}$, and of the temperature, $T$.
+It is composed of 3 terms describing independently plastic, viscous and thermal aspects.
+One of the points in favour of its adoption is the rather limited number of parameters to be identified, 5: $A$, $B$, $C$, $m$ and $n$.
+$\dot{\varepsilon}_{0}^{p}$ is the reference plastic strain rate, while $T_{\text{room}}$ and $T_{\text{melt}}$ are the room temperature and the melting temperature, respectively.
+More recent models developed based on it, such as the one of Calamaz et al.
+\cite{calamaz_New_2008}, increase this number of parameters (for Calamaz's particular model to 9).
+The better (in theory) description of the behaviour is achieved at the cost of greater complexity of the identification process and of a reduction of the link with the physical meaning of the model.
+When a continuous chip is formed, JC model \hl{has moreover proved to be well-suited} \cite{}.
+
+One issue of material behaviour modelling for cutting simulation is the identification of the model parameters, moreover as the experimental equipment does not allow to reach the high levels of strains, strain rates and temperature of machining \cite{melkote_Advances_2017}.
+Inverse identification is an alternative, but the uniqueness of the solution is not always guaranteed \cite{arrazola_Recent_2013, melkote_Advances_2017}.
+The early work of Özel and Altan \cite{ozel_Determination_2000} used  the least squares method to inversely identify the input parameters of a FE model.
+Shrot and Bäker \cite{shrot_Determination_2012} then used the Levenberg–Marquardt algorithm for their identification of the constitutive material parameters.
+They showed that similar results (cutting forces and chip morphology) could be obtained by different sets of parameters and therefore highlighted the non-uniqueness of the solution of the inverse problem.
+In addition to the flow stress parameters, Klocke et al.
+\cite{klocke_Orthogonal_2013} also identified the damage parameters.
+In more recent works, such as Bosetti et al.
+\cite{bosetti_Identification_2013} and Denkena et al.
+\cite{denkena_Inverse_2015}, the approach to tackle the inverse identification problem is moving from optimisation to Artificial Intelligence (AI) based methods.
+The Downhill Simplex Algorithm (DSA) is adopted by Bergs et al.
+\cite{bergs_Determination_2020} and by Hardt et al.
+\cite{hardt_Investigations_2021} for AISI 1045.
+Stampfer et al.
+\cite{stampfer_Material_2021} also selected the DSA when dealing with AISI 4140 tempered at 3 different temperatures.
+In \cite{hardt_Application_2021}, Hardt et al.
+showed that the Particle Swarm Optimization (PSO) was more efficient to solve the inverse problem than the Downhill Simplex Algorithm, even if computation time is still significant.
+In an effort to reduce it, an Efficient Global Optimization (EGO) algorithm has recently been introduced by Kugalur Palanisamy et al.
+\cite{kugalurpalanisamy_Identification_2022}.
+They simultaneously identified the parameters of the material constitutive model and of the friction model for Ti6Al4V.
+Most of these works highlight the non-uniqueness of the identification and they all require the definition of the analytical expression of the constitutive model.
 
 This paper fills the literature gap on oblique cutting by investigating free orthogonal and oblique 3D cutting configurations from both the experimental and the numerical points of view.
-An Artificial Neural Network (ANN), introduced in \cite{pantale_efficient_2022}, is implemented in a FE cutting model for the first time instead of the analytical JC law.
+An Artificial Neural Network (ANN), introduced in Pantalé et al.
+\cite{pantale_Efficient_2022}, is implemented in a FE cutting model for the first time instead of the analytical JC law.
 A broad range of cutting speeds (6), uncut chip thicknesses (3) and inclination angles (2) resulting in 36 different conditions are considered to demonstrate the predictive ability of the FE model for fundamental variables.
@@
 
-A 3-axis GF Mikron VCE 600 Pro milling machine is used to carry out dry free orthogonal and oblique cutting tests on Ti6Al4V (grade 5 annealed at 750°C for 1 h followed by air cooling) with the same kinematics as a shaper.
+A 3-axis GF Mikron VCE 600 Pro milling machine is used to carry out dry free orthogonal and oblique cutting tests on Ti6Al4V (grade 5 annealed at 750\textdegree{}C for 1 h followed by air cooling) with the same kinematics as a shaper.
 As shown in Figure \ref{ExpSetup}, the tungsten carbide tool (modified LCGN160602-0600-FG, CP500 from SECO) is fixed on a dedicated holder (modified CFHN-06 from SECO) and the sample to be cut is clamped in the spindle (no rotation is allowed during the test).
@@
 value of 40 m/min).
-The tool cutting edge inclination, $\lambda_s$, results from the relative orientation of the tool and the sample.
-Forces are measured with a 3-component Kistler 9257B dynamometer and are amplified by a Kistler 5070A charge amplifier.
-Acquisition is performed at 3 kHz with a Kistler 5697A2 data acquisition system and the DynoWare software.
-Table \ref{tab:CutCond} shows the cutting conditions, each is repeated 3 times.
-\FD{Add infos valeur effort: mean, filter, etc.
-+ get info from section 4: Experimental and numerical forces are filtered with a second-order low-pass Bessel filter at 750 Hz before computing the mean value of the signal at steady state.}
+The tool cutting edge inclination, $\lambda_s$, results from the relative angular orientation of the tool and the sample.
+Table \ref{tab:CutCond} shows the cutting conditions: 6 cutting speeds, 3 uncut chip thicknesses and 2 inclination angles, each is repeated 3 times.
 
@@
 \centering
-\includegraphics[width=\columnwidth]{Figures/ExpSetup}
+\includegraphics[width = 140 mm]{Figures/ExpSetup} % 140 mm, 1.5\columnwidth
 \caption{Experimental setup}
@@
 
+Forces are measured with a 3-component Kistler 9257B dynamometer and are amplified by a Kistler 5070A charge amplifier.
+Acquisition is performed at 3 kHz with a Kistler 5697A2 data acquisition system and the DynoWare software.
+Recorded forces are then filtered with a second-order low-pass Bessel filter at 750 Hz before computing the mean value of the signal at steady state.
+
+All the chips are collected and observed with a Dino Lite digital microscope AM7013MZT (5 MP, magnification $20\times$ -- $250\times$).
+Each chip is measured 3 times along its length to get a mean value representative of the whole chip.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The Eulerian formulation enables to form chips without damage properties, removing modelling assumptions.
-These two characteristics contribute to cutting models providing accurate results and realistic chips \cite{ducobu_application_2016}.
+These two characteristics contribute to cutting models providing accurate results and realistic chips \cite{ducobu_Application_2016}.
 
@@
 \centering
-\includegraphics[width=\columnwidth]{Figures/BC}
+\includegraphics[width = 140 mm]{Figures/BC} % 90 mm, \columnwidth
 \caption{Boundary conditions and schematic initial geometry of the model}
@@
 
-As shown in Figure \ref{FEConfig}, the full width of the workpiece (1 mm) is modelled.
+As shown in Figure \ref{FEConfig}, the full width of the workpiece, i.e.
+a rib in the experiments, (1 mm) is modelled.
 To allow chip formation and side flow, the Eulerian domain is wider (it includes the volume in which material can move).
@@
 As in the experiments and to fulfil the hypothesis of free orthogonal and oblique cutting, the tool is wider than the workpiece (it is of 1.1 mm in the model and of 6 mm in the experiments).
-It is very important to stress that the models are the same for both inclination angles: they only differ by the rotation of the tool of 6° about Y axis as in the experiments (Figure \ref{FEConfig}).
-This, coupled to the absence of assumptions when developing the models, contributes to make the models predictive.
+It is very important to stress that the models are the same for both inclination angles: they only differ by the rotation of the tool of 6\textdegree{} about Y axis as in the experiments (Figure \ref{FEConfig}).
+This, coupled to the absence of assumptions when developing the models, contributes to make the models predictive: no input is changed when cutting conditions do.
 
@@
 \centering
-\includegraphics[width=\columnwidth]{Figures/FEConfig}
-\caption{Configuration of the FE model for $\lambda_s$ = 6°}
+\includegraphics[width = 140 mm]{Figures/FEConfig}
+\caption{Configuration of the FE model for $\lambda_s$ = 6\textdegree{}}
 \label{FEConfig}
@@
 
-According to a previous mesh sensitivity study in orthogonal cutting with CEL \cite{ducobu_finite_2017}, elements edge size is 5 µm in the plane parallel to the cutting speed.
-In the direction perpendicular to this plane, it is 5 µm in areas close to the lateral boundaries of the Eulerian domain and 50 µm in the middle of the workpiece.
+According to a previous mesh sensitivity study in orthogonal cutting with the CEL formulation \cite{ducobu_Finite_2017}, elements edge size is 5 \textmu{}m in the plane parallel to the cutting speed.
+In the direction perpendicular to this plane, it is 5 \textmu{}m in areas close to the lateral boundaries of the Eulerian domain and 50 \textmu{}m in the middle of the workpiece.
 To reduce computation time, the size of the model depends on the value of the uncut chip thickness.
@@
 The Ti6Al4V workpiece is assumed to be thermo-elasto-viscoplastic (isotropic) and inelastic heat fraction is 0.9.
+JC set of parameters from Seo et al.
+\cite{seo_Constitutive_2005} is adopted as the value of $A$ corresponds to the typical yield stress value of Ti6Al4V and this set proved to provide the best results among 20 sets available in the literature \cite{ducobu_Importance_2017}.
 The tungsten carbide tool with TiN coating is assumed to be linear elastic.
@@
 \begin{center}
-\caption{\label{tab:prop} Materials properties \cite{Seo2004, Granta, Milosevic}}
+\caption{\label{tab:prop} Materials properties \cite{seo_Constitutive_2005, _GRANTA_2020, milosevic_Thermophysical_2012}}
 \begin{tabular}{lll}
@@
 JC constitutive model & $A$ (MPa) & 997.9\\
-\FD{Comment this choice of JC para} & $B$ (MPa) & 653.1\\
+ & $B$ (MPa) & 653.1\\
  & $C$ & 0.0198\\
@@
 Following the experimental results of Rech et al.
-\cite{rech_characterisation_2013}, Coulomb's friction is assumed to occur at the tool-workpiece interface and both friction and heat partition coefficients depend on the cutting speed.
-\hl{Limiting shear stress is included + equa.
-All the friction energy is converted into heat.
-Table XX shows the friction parameters adopted in this study.}
-
+\cite{rech_Characterisation_2013}, Coulomb's friction is assumed to occur at the tool-workpiece interface and both friction, $\mu$, and heat partition, $\beta$, coefficients depend on the cutting speed.
+Limiting shear stress, $\tau_{\text{max}}$, is included and is given by
 %
-\hl{Table friction}
+\begin{equation}
+\tau_{\text{max}} = \frac{\text{yield stress}}{\sqrt{3}} = \frac{A}{\sqrt{3}}
+\end{equation}
+%
+All the friction energy is converted into heat. Table \ref{tab:fricHeat} shows the friction coefficients adopted in this study.
+%
+\begin{table}[!h]
+\begin{center}
+\caption{\label{tab:fricHeat} Friction and heat transfer coefficients \cite{rech_Characterisation_2013, _GRANTA_2020}}
+\begin{tabular}{lll}
+\hline\noalign{\smallskip}
+Cutting speed, $v_c$ (m/min) & $\mu$ & $\beta$\\
+5 & 0.24 & 1\\
+7.5 & 0.22 & 0.89\\
+10 & 0.21 & 0.80\\
+20 & 0.19 & 0.63\\
+30 & 0.18 & 0.55\\
+40 & 0.17 & 0.50\\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Limiting shear stress, $\tau_{\text{max}}$ (MPa) & 576\\
+Convection, $U$ (W/m$^2$K) & 50\\
+Radiation, $\epsilon$ & 0.3\\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+\end{tabular}
+\end{center}
+\end{table}
 %
 
-Room temperature of 293 K is imposed on the upper and right surfaces of the tool and on the left and bottom surfaces of the workpiece (Figure 2).
+Room temperature of 293 K is imposed on the upper and right surfaces of the tool and on the left and bottom surfaces of the workpiece (Figure \ref{BC}).
 Radiation and convection are assumed to occur on the rake and clearance faces of the tool.
 Initial temperature of the tool and the workpiece is set to room temperature (293 K).
-\hl{+ info coefficients}
+Heat transfer coefficients are provided in Table \ref{tab:fricHeat}.
 
@@
 The constitutive model of the Ti6Al4V material used in all the numerical simulations proposed in section \ref{sec:ExpNumResults} is a thermo-elasto-viscoplastic law using a flow criterion based on an ANN identified for the selected material and implemented in the Abaqus/Explicit code via a Fortran routine VUHARD as proposed by Pantalé et al.
-in \cite{pantale_efficient_2022}.
+in \cite{pantale_Efficient_2022}.
 The principle of this approach consists in replacing the analytical formulation of the flow law, based on a Johnson-Cook or Zerilli-Armstrong type model, and allowing the calculation of the flow stress $\sigma^y$ as a function of the plastic strain $\varepsilon^p$, of the plastic strain rate, ${\dot{\varepsilon}}^p$, and of the temperature $T$, by a multi-layer ANN serving as universal approximator.
@@
 The proposed approach also allows, as shown in Pantalé et al.
-\cite{pantale_efficient_2022}, to compute the derivatives of the flow stress $\sigma^y$ with respect to the three input variables of the model, a necessary step to implement this model as a flow law in the form of a VUHARD subroutine in the Abaqus/Explicit FEM code.
+\cite{pantale_Efficient_2022}, to compute the derivatives of the flow stress $\sigma^y$ with respect to the three input variables of the model, a necessary step to implement this model as a flow law in the form of a VUHARD subroutine in the Abaqus/Explicit FEM code.
 
@@
 Conforming to Pantalé et al.
-\cite{pantale_efficient_2022}, this ANN is referred after the terminology ANN 3-9-7-1-sig, because it has 3 inputs, 9 neurons in the first hidden layer, 7 neurons in the second hidden layer, 1 output and a sigmoid activation function.
+\cite{pantale_Efficient_2022}, this ANN is referred after the terminology ANN 3-9-7-1-sig, because it has 3 inputs, 9 neurons in the first hidden layer, 7 neurons in the second hidden layer, 1 output and a sigmoid activation function.
 
@@
 \centering
-\includegraphics[width=0.8\columnwidth]{Figures/ANN}
+\includegraphics[width = 90 mm]{Figures/ANN}
 \caption{Architecture of the ANN 3-9-7-1-sig used for the flow law}
@@
 
-So, \FD{Olivier: remove?}\hl{that,} the output of the ANN is therefore given by equation (\ref{eq:ANN-vonMises}).
+So, the output of the ANN is therefore given by equation (\ref{eq:ANN-vonMises}).
 \begin{equation}
@@
 
-Because of the large number of identified parameters for all the ANN models (from 114 to 202 for 9 and 17 neurons for the first hidden layer, respectively); the other 4 sets of ANN parameters used in this publication can be found in \cite{pantale_coefficients_2022}.\FD{Inclure dans corps du texte puisque article normal?}
+Because of the large number of identified parameters for all the ANN models (from 114 to 202 for 9 and 17 neurons for the first hidden layer, respectively); the other 4 sets of ANN parameters used in this publication can be found in \cite{pantale_Coefficients_2022}.\FD{Inclure dans corps du texte puisque article normal et rq reviewer?}
 
@@
 
-FE modelling of the cutting process is very expensive in CPU computation time because of the coupling on many nonlinear phenomena and the large amount of tiny finite elements.
+FE modelling of the cutting process is very expensive in CPU computation time because of the coupling fn many nonlinear phenomena and the large amount of tiny finite elements.
 Mass scaling (MS) is introduced in the model to reduce the CPU computation time while checking that it does not influence the results (forces and energies) via a mass scaling sensitivity study.
-MS factors, ${MS}_f$, ranging from 1E6 (theoretical scaling of CPU time of 1000\FD{sqrt MSF}) to 1 (no scaling) have been used for one cutting condition ($\lambda_s$ = 0°, $v_c$ = 30 m/min and $h$ = 60 µm).
-Table \ref{tab:MS} gives the results normalised ($\hat{x}$) by these of the model without MS \hl{(x)}.\FD{+ equa and explain that effort is mean, filtered, etc.} As expected, actual speed-up does not increase linearly with the ${MS}_f$, but it is still significant.
+MS factors, ${MS}_f$, ranging from 1E6 (theoretical scaling of CPU time of $\sqrt{{MS}_f} = 1000$) to 1 (no scaling) have been used for one cutting condition ($\lambda_s$ = 0\textdegree{}, $v_c$ = 30 m/min and $h$ = 60 \textmu{}m).
+The same signal processing procedure is applied to the numerical forces as to the experimental forces (cf.
+\ref{ExpSet}): they are filtered with a second-order low-pass Bessel filter at 750 Hz before computing the mean value at steady state.
+Table \ref{tab:MS} gives the results normalised ($\hat{F_i}$) by these of the model without MS:
+%
+\begin{equation}
+\hat{F_i} = \frac{F_i\text{ with MS}}{F_i\text{ without MS}}
+\end{equation}
+%
+With $i = c$ for the cutting force and $i = f$ for the feed force.
+As expected, actual speed-up does not increase linearly with the ${MS}_f$, but it is still significant.
 ${MS}_f$ of 1E6 leads to unstable computation and ${MS}_f$ of 1E5 results in erratic forces evolutions.
-These results are confirmed by high values of the kinetic ($KE$) on internal ($IE$) energies ratio (it should not exceed a few \%).
+These results are confirmed by high values of the kinetic ($KE$) on internal ($IE$) energies ratio (it should not exceed a few \% \cite{wang_Investigation_2011, ducobu_Introduction_2015}).
 A ${MS}_f$ value of 1E3 is selected as it provides a good balance between computation time reduction and impact on forces, while keeping $\frac{KE}{IE}$ below 1\%.
@@
 \begin{center}
-\caption{\label{tab:MS} MS sensitivity study (selected $MS_f$ in bold)}\FD{Define $\hat{F_c}$, etc. in caption}
-\begin{tabular}{lllll}
+\caption{\label{tab:MS} MS sensitivity study (selected MS factor, $MS_f$, in bold, $\hat{F_c}$: normalized cutting force, $\hat{F_f}$: normalized feed force, $KE$: kinetic energy, $IE$: internal energy)}
+\begin{tabular}{llllll}
 \hline\noalign{\smallskip}
-$MS_f$  & Speed-up & $\hat{F_c}$ & $\hat{F_f}$ & $\frac{KE}{IE}$ (\%)\\
+$MS_f$ & CPU scaling & Speed-up & $\hat{F_c}$ & $\hat{F_f}$ & $\frac{KE}{IE}$ (\%)\\
 \noalign{\smallskip}\hline\noalign{\smallskip}
-1 & 1 & 1 & 1 & 2.3E-4\\
-1E2 & 9 & 1.006 & 0.982 & 2.2E-2\\
-\textbf{1E3} & \textbf{21} & \textbf{1.008} & \textbf{0.940} & \textbf{2.2E-1}\\
-1E4 & 61 & 1.012 & 0.921 & 2.4\\
-1E5 & 173 & Erratic & Erratic & 22\\
-1E6 & 207 & Unstable & Unstable & 58\\
+1 & 1 & 1 & 1 & 1 & 2.3E-4\\
+1E2 & 10 & 9 & 1.006 & 0.982 & 2.2E-2\\
+\textbf{1E3} & \textbf{32} & \textbf{21} & \textbf{1.008} & \textbf{0.940} & \textbf{2.2E-1}\\
+1E4 & 100 & 61 & 1.012 & 0.921 & 2.4\\
+1E5 & 316 & 173 & Erratic & Erratic & 22\\
+1E6 & 1000 & 207 & Unstable & Unstable & 58\\
 \noalign{\smallskip}\hline
@@
 The number of neurons on the hidden layers may influence the results.
-A sensitivity study on the number of neurons for the first hidden layer is carried out to select the ANN providing the best balance between CPU computation time and quality of the results.
+A sensitivity study on the number of neurons for the first hidden layer, $\zeta$, is carried out to select the ANN providing the best balance between CPU computation time and quality of the results.
 The results of the study are provided in Table \ref{tab:NbNeurons}.
+$\check{F_i}$ corresponds to the results normalised by these of the model with the built-in JC model:
+%
+\begin{equation}
+\check{F_i} = \frac{F_i\text{ with ANN}}{F_i\text{ with JC}}
+\end{equation}
+%
 They show no influence on the forces when compared to the built-in Johnson-Cook model, only computation time is influenced.
@@
 \caption{\label{tab:NbNeurons} Sensitivity of the forces to the number of neurons of the first layer, $\zeta$
-(selection in bold)}\FD{Define $\hat{F_c}$, etc. in caption}
+(selection in bold, $\check{F_c}$: normalized cutting force, $\check{F_f}$: normalized feed force)}
 \begin{tabular}{llll}
 \hline\noalign{\smallskip}
-$\zeta$  & Time increase (\%) & $\hat{F_c}$ & $\hat{F_f}$\\
+$\zeta$  & Time increase (\%) & $\check{F_c}$ & $\check{F_f}$\\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%
-\FD{Show chips? + info on side flow? + dedicated subsection on chip thickness?}
+\FD{Show chips? + info on side flow? + dedicated subsection on chip thickness? (give also results in a plot?)}
 Mean and standard deviation ($2\sigma$) are computed from the 3 experimental values and are shown in Figures \hl{5 to 7}.
@@
 \FD{sigma deja utilise mais equa (5) devrait etre sigma y - voir avec Olivier}
+\FD{Add a table with mean differences as a kind of summary of the results?}
 
@@
 \centering
-\includegraphics[width=\columnwidth]{Figures/ExpNum_Forces_v10_40µ_6}
-\caption{Temporal evolutions of experimental (E) and numerical (N) forces at 6°, 10 m/min and 40 \textmu{}m: dispersion around mean experimental values and linear extrapolation of numerical values in dashed}
+\includegraphics[width = 140 mm]{Figures/ExpNum_Forces_v10_40µ_6}
+\caption{Temporal evolutions of experimental (E) and numerical (N) forces at 6\textdegree{}, 10 m/min and 40 \textmu{}m: dispersion around mean experimental values and linear extrapolation of numerical values in dashed}
 \label{ExpNum_Forces_v10_40µ_6}
@@
 \centering
-\includegraphics[width=\columnwidth]{Figures/Fx_0}
-\caption{Comparison of experimental (E) and numerical (N) cutting forces at 0°}\FD{Better explain legend in caption, same for other figures}
+\includegraphics[width = 140 mm]{Figures/Fx_0}
+\caption{Comparison of experimental (E) and numerical (N) cutting forces at 0\textdegree{}}\FD{Better explain legend in caption, same for other figures}
 \label{Fx_0}
@@
 \centering
-\includegraphics[width=\columnwidth]{Figures/Fx_6}
-\caption{Comparison of experimental (E) and numerical (N) cutting forces at 6°}
+\includegraphics[width = 140 mm]{Figures/Fx_6}
+\caption{Comparison of experimental (E) and numerical (N) cutting forces at 6\textdegree{}}
 \label{Fx_6}
@@
 \centering
-\includegraphics[width=\columnwidth]{Figures/Fy_0}
-\caption{Comparison of experimental (E) and numerical (N) feed forces at 0°}
+\includegraphics[width = 140 mm]{Figures/Fy_0}
+\caption{Comparison of experimental (E) and numerical (N) feed forces at 0\textdegree{}}
 \label{Fy_0}
@@
 \centering
-\includegraphics[width=\columnwidth]{Figures/Fy_6}
-\caption{Comparison of experimental (E) and numerical (N) feed forces at 6°}
+\includegraphics[width = 140 mm]{Figures/Fy_6}
+\caption{Comparison of experimental (E) and numerical (N) feed forces at 6\textdegree{}}
 \label{Fy_6}
@@
 \centering
-\includegraphics[width=\columnwidth]{Figures/Fz_6}
-\caption{Comparison of experimental (E) and numerical (N) passive forces at 6°}
+\includegraphics[width = 140 mm]{Figures/Fz_6}
+\caption{Comparison of experimental (E) and numerical (N) passive forces at 6\textdegree{}}
 \label{Fz_6}
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width = 140 mm]{Figures/h0}
+\caption{Comparison of experimental (E) and numerical (N) chip thickness ratios at 0\textdegree{}}
+\label{h0}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width = 140 mm]{Figures/h6}
+\caption{Comparison of experimental (E) and numerical (N) chip thickness ratios at 6\textdegree{}}
+\label{h6}
+\end{figure}
+
+\hl{+ fig with sim chip and show that it is helical/spiral at 6 deg}
+\hl{+ Chip thickness is globally lower at 6 deg than 0 deg}
+\hl{+ Show side flow, non-uniform chip thickness}
+
 The increase of the cutting force with the uncut chip thickness is clearly observed in Figure 5 for both experimental and numerical results at the 2 inclination angles, as well as the decrease of the force with the increase in the cutting speed.
 This shows temperature softening domination on strain rate hardening for Ti6Al4V and that it is accurately modelled.
-The increase of the inclination angle from 0° to 6° reduces the cutting force; this is well captured by the model.
-For cutting speeds of 20-40 m/min, $F_c$ is almost constant for 40 µm and 60 µm, while it slightly decreases for 80 µm; this small stabilisation is less marked for the model.
+The increase of the inclination angle from 0\textdegree{} to 6\textdegree{} reduces the cutting force; this is well captured by the model.
+For cutting speeds of 20-40 m/min, $F_c$ is almost constant for 40 \textmu{}m and 60 \textmu{}m, while it slightly decreases for 80 \textmu{}m; this small stabilisation is less marked for the model.
 Increase in the deviation around the mean value with the cutting speed is noted for values above 10 m/min.
@@
 Figure 6 shows the results for the feed force, where the two clearest trends are its decrease with inclination angle and its increase with the uncut chip thickness for both experimental and numerical results.
-For 80 µm, $F_f$ globally decreases with $v_c$ in the experiments.
-For 40 and 60 µm, the force decreases at lower $v_c$ and then increases for 0°, while a decrease is observed at all $v_c$ for 6°.
+For 80 \textmu{}m, $F_f$ globally decreases with $v_c$ in the experiments.
+For 40 and 60 \textmu{}m, the force decreases at lower $v_c$ and then increases for 0\textdegree{}, while a decrease is observed at all $v_c$ for 6\textdegree{}.
 For the numerical values, the global trend is the same for the 3 uncut chip thicknesses and both inclination angles: a decrease for the lowest $v_c$ values and then an increase.
@@
 Improving the friction model should enhance the results.
-Passive force is non-zero for the inclination angle of 6° (Figure 7).
+Passive force is non-zero for the inclination angle of 6\textdegree{} (Figure 7).
 As the cutting force, it increases with the uncut chip thickness and it decreases with the cutting speed.
@@
 
-\FD{Add biblio}
+\hl{this works opens possibilities in both 3D free orthogonal cutting and ANN based material behaviours}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% References
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%
+%%% Following citation commands can be used in the body text:
+%%% Usage of \cite is as follows:
+%%%   \cite{key}          ==>>  [#]
+%%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
+%%%   \citet{key}         ==>>  Author [#]
+%
+%%% References with bibTeX database:
+%
+\bibliographystyle{model1-num-names}
+\bibliography{Biblio}
+%
+%%% Authors are advised to submit their bibtex database files. They are
+%%% requested to list a bibtex style file in the manuscript if they do
+%%% not want to use model1-num-names.bst.
+%
+%%% References without bibTeX database:
+%
+%% \begin{thebibliography}{00}
+%
+
+%%% \bibitem must have the following form:
+%%%   \bibitem{key}...
+%%%
+%
+%% \bibitem{}
+%
+%% \end{thebibliography}
+%
 
@@
 %
-%%% References
-%%%
-%%% Following citation commands can be used in the body text:
-%%% Usage of \cite is as follows:
-%%%   \cite{key}          ==>>  [#]
-%%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
-%%%   \citet{key}         ==>>  Author [#]
-%
-%%% References with bibTeX database:
-%
-\bibliographystyle{model1-num-names}
-\bibliography{Biblio}
-%
-%%% Authors are advised to submit their bibtex database files. They are
-%%% requested to list a bibtex style file in the manuscript if they do
-%%% not want to use model1-num-names.bst.
-%
-%%% References without bibTeX database:
-%
-%% \begin{thebibliography}{00}
-%
-
-%%% \bibitem must have the following form:
-%%%   \bibitem{key}...
-%%%
-%
-%% \bibitem{}
-%
-%% \end{thebibliography}
-%
 

### 2022-09-26 Article.tex
Revision of the whole article
- Revision of the full text
- Introduction of 3 new figures
- Revision of 2 figures
- Flow stress is \sigma^y in the whole article

@@
 \author[2]{O. Pantal\'{e}}
-\author[1]{E. Rivi\`{e}re-Lorph\`{e}vre}
 \author[3]{B. Lauwers}
@@
 The better (in theory) description of the behaviour is achieved at the cost of greater complexity of the identification process and of a reduction of the link with the physical meaning of the model.
-When a continuous chip is formed, JC model \hl{has moreover proved to be well-suited} \cite{}.
 
@@
 A broad range of cutting speeds (6), uncut chip thicknesses (3) and inclination angles (2) resulting in 36 different conditions are considered to demonstrate the predictive ability of the FE model for fundamental variables.
+The main goals of a predictive model are the accurate modelling of the trends of the results when the conditions change and predicted values in good agreement with the experimental ones (exact values are not looked for due to experimental dispersions).
+This type of models aims at supporting future choices and developments without the need of experimental data.
 No assumption is made about the geometry of the machined workpiece in the model (i.e.
@@
 
-\begin{figure}[h]
+\begin{figure}[!h]
 \centering
@@
 Cutting speed, $v_c$ (m/min) & $\mu$ & $\beta$\\
+\noalign{\smallskip}\hline\noalign{\smallskip}
 5 & 0.24 & 1\\
@@
 \begin{equation}
-\sigma =  \left([\sigma]_{max}-[\sigma]_{min}\right) \left(\overrightarrow{w}^T \dotp \overrightarrow{y_2} + b\right) + [\sigma]_{min} \label{eq:ANN-vonMises}
+\sigma^y =  \left([\sigma^y]_{max}-[\sigma^y]_{min}\right) \left(\overrightarrow{w}^T \dotp \overrightarrow{y_2} + b\right) + [\sigma^y]_{min} \label{eq:ANN-vonMises}
 \end{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%
-\FD{Show chips? + info on side flow? + dedicated subsection on chip thickness? (give also results in a plot?)}
-Mean and standard deviation ($2\sigma$) are computed from the 3 experimental values and are shown in Figures \hl{5 to 7}.
-Mean numerical values are plotted inside the experimental bars in Figures \hl{5 to 7}.
-\FD{sigma deja utilise mais equa (5) devrait etre sigma y - voir avec Olivier}
-\FD{Add a table with mean differences as a kind of summary of the results?}
 
-\begin{figure}[h]
+An example of temporal evolutions of numerical and experimental forces is plotted for the 3 directions in Figure \ref{ExpNum_Forces_v10_40µ_6} at $\lambda_s = 6$\textdegree{}, $v_c = 10$ m/min and $h = 40$ \textmu{}m.
+Computation of the FE models is carried out until a few microseconds after the steady state is reached.
+Then, linear extrapolation (dashed line between the two last markers in Figure \ref{ExpNum_Forces_v10_40µ_6}) is used to provide numerical values during the same time range as the experimental values.
+Mean and standard deviation ($2\,\sigma$) are computed from the 3 experimental values.
+The resulting dispersion is plotted in Figure \ref{ExpNum_Forces_v10_40µ_6} around the mean values of each forces.
+Steady state takes more time to be reached for the experiments than in the numerical model, and particularly for the cutting force.
+Dispersion around the mean force evolution is larger for the feed force than for the cutting force, while the mean feed force value is 46\% of the mean cutting force value.
+The numerical cutting force is very close to the experimental mean cutting force; it is only 4\% larger).
+This difference is computed by
+%
+\begin{equation}\label{eq:diff}
+	\Delta i = \frac{\left|i^\text{(sim)} - i^\text{(exp)}\right|}{i^\text{(exp)}}\times 100
+\end{equation}
+%
+
+ The numerical feed force is underestimated by the model, but it is at the boundary of the 95\% experimental confidence interval.
+The numerical passive force difference is also underestimated, but it is not in the narrower experimental dispersion.
+Difference between the mean values of experimental and numerical feed and passive forces is 25\%.
+\hl{This value for the feed force\ldots + [x] For the passive force\ldots + [x]}
+
+\begin{figure}[!h]
 \centering
 \includegraphics[width = 140 mm]{Figures/ExpNum_Forces_v10_40µ_6}
-\caption{Temporal evolutions of experimental (E) and numerical (N) forces at 6\textdegree{}, 10 m/min and 40 \textmu{}m: dispersion around mean experimental values and linear extrapolation of numerical values in dashed}
+\caption{Temporal evolutions of experimental (E) and numerical (N) forces at $\lambda_s = 6$\textdegree{}, $v_c = 10$ m/min and $h = 40$ \textmu{}m: dispersion around mean experimental values and linear extrapolation of numerical values in dashed}
 \label{ExpNum_Forces_v10_40µ_6}
@@
 
-\begin{figure}[h]
+Numerical chips at $v_c = 10$ m/min and $h = 40$ \textmu{}m for $\lambda_s = 0$\textdegree{} and $\lambda_s = 6$\textdegree{} are provided in Figures \ref{ChipsNum} and \ref{ChipsNumBack}.
+When the cutting edge inclination is 0\textdegree{}, both sides of the chip are identical and a symmetry plane can be drawn in the middle of the workpiece (Figure \ref{ChipsNumBack} (a)).
+On the contrary, for the cutting edge inclination of 6\textdegree{}, the chip is not aligned with the workpiece anymore.
+The chip bends on one side due to the orientation of the tool and the symmetry is lost for both the geometry, and the thermal and mechanical fields as highlighted in Figure \ref{ChipsNumBack} (b).
+This produces helical chips for the inclination angle of 6\textdegree{} as in the experiments.
+Figure \ref{ChipNumTop} shows the variation of the chip thickness across its width: it is thicker in the middle (i.e.
+the body of the chip) than on its sides.
+This stresses on the importance of a 3D modelling, even for the orthogonal cutting configuration as already highlighted \hl{by} \cite{Outeiro?
+Ambrosini?
+Hardt?
+Duco}.
+3D modelling also allows to reproduce the side flow occurring in the experiments for both cutting edge inclination values (Figure \ref{ChipsNum}), contrary to a 2D \hl{model} \cite{}.
+Although this leads to higher computation times, future cutting models should be in 3D, even when orthogonal cutting is considered.
+In this case, it is recommended to take advantage of the symmetry of the configuration to reduce computation time.
+This simplification has not been included in this study to avoid any difference in the FE models between the 2 cutting edge inclinations.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width = 140 mm]{Figures/ChipsNum}
+\caption{Temperature contours (in K) of the numerical chip after 1.5 ms at $v_c = 10$ m/min, $h = 40$ \textmu{}m and (a) $\lambda_s = 0$\textdegree{} and (b) $\lambda_s = 6$\textdegree{}}
+\label{ChipsNum}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width = 140 mm]{Figures/ChipsNumBack}
+\caption{Temperature contours (in K) of the back of the numerical chip (tool is removed) after 1.5 ms at $v_c = 10$ m/min, $h = 40$ \textmu{}m and (a) $\lambda_s = 0$\textdegree{} and (b) $\lambda_s = 6$\textdegree{}}
+\label{ChipsNumBack}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width = 140 mm]{Figures/ChipNumTop}
+\caption{Temperature contours (in K) of the top of the numerical chip after 1.5 ms at $v_c = 10$ m/min, $h = 40$ \textmu{}m and $\lambda_s = 0$\textdegree{}}
+\label{ChipNumTop}
+\end{figure}
+
+Mean values of the experimental forces and their dispersion are shown in Figures \ref{Fx_0} to \ref{Fz_6} together with the mean numerical values.
+Passive force values are of course only plotted for $\lambda_s = 6$\textdegree{} as they are equal to zero when $\lambda_s = 0$\textdegree{}.
+
+\begin{figure}[!h]
 \centering
 \includegraphics[width = 140 mm]{Figures/Fx_0}
-\caption{Comparison of experimental (E) and numerical (N) cutting forces at 0\textdegree{}}\FD{Better explain legend in caption, same for other figures}
+\caption{Comparison of experimental (E) and numerical (N) cutting forces at the cutting edge inclination of 0\textdegree{} for the 3 uncut chip thicknesses (40, 60 and 80 \textmu{}m) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and 40 m/min)}
 \label{Fx_0}
@@
 
-\begin{figure}[h]
+\begin{figure}[!h]
 \centering
 \includegraphics[width = 140 mm]{Figures/Fx_6}
-\caption{Comparison of experimental (E) and numerical (N) cutting forces at 6\textdegree{}}
+\caption{Comparison of experimental (E) and numerical (N) cutting forces at the cutting edge inclination of 6\textdegree{} for the 3 uncut chip thicknesses (40, 60 and 80 \textmu{}m) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and 40 m/min)}
 \label{Fx_6}
@@
 
-\begin{figure}[h]
+\begin{figure}[!h]
 \centering
 \includegraphics[width = 140 mm]{Figures/Fy_0}
-\caption{Comparison of experimental (E) and numerical (N) feed forces at 0\textdegree{}}
+\caption{Comparison of experimental (E) and numerical (N) feed forces at the cutting edge inclination of 0\textdegree{} for the 3 uncut chip thicknesses (40, 60 and 80 \textmu{}m) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and 40 m/min)}
 \label{Fy_0}
@@
 
-\begin{figure}[h]
+\begin{figure}[!h]
 \centering
 \includegraphics[width = 140 mm]{Figures/Fy_6}
-\caption{Comparison of experimental (E) and numerical (N) feed forces at 6\textdegree{}}
+\caption{Comparison of experimental (E) and numerical (N) feed forces at the cutting edge inclination of 6\textdegree{} for the 3 uncut chip thicknesses (40, 60 and 80 \textmu{}m) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and 40 m/min)}
 \label{Fy_6}
@@
 
-\begin{figure}[h]
+\begin{figure}[!h]
 \centering
 \includegraphics[width = 140 mm]{Figures/Fz_6}
-\caption{Comparison of experimental (E) and numerical (N) passive forces at 6\textdegree{}}
+\caption{Comparison of experimental (E) and numerical (N) passive forces at the cutting edge inclination of 6\textdegree{} for the 3 uncut chip thicknesses (40, 60 and 80 \textmu{}m) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and 40 m/min)}
 \label{Fz_6}
@@
 
-\begin{figure}[h]
+The increase of the cutting force with the uncut chip thickness is clearly observed in Figures \ref{Fx_0} and \ref{Fx_6} for both experimental and numerical results at the 2 inclination angles, as well as the decrease of the force with the increase in the cutting speed.
+This shows temperature softening domination on strain rate hardening for Ti6Al4V and that it is accurately modelled.
+The increase of the inclination angle from 0\textdegree{} to 6\textdegree{} slightly reduces the cutting force; this is well captured by the model.
+For cutting speeds of 20--40 m/min and inclination angle of 0\textdegree{}, $F_c$ is almost constant with the cutting speed for uncut chip thicknesses of 40 \textmu{}m and 60 \textmu{}m, while it slightly decreases for 80 \textmu{}m; this small stabilisation is less marked for the modelling.
+
+An increase in the deviation around the mean value with the cutting speed is noted for values above 10 m/min.
+All numerical values are within a confidence interval of 95\% of the experiments (35 out of 36 conditions are within a confidence interval of 68\%) and the mean difference with the experiments is 3\%, which is remarkable, moreover given the wide range of cutting conditions considered and the absence of tuning of the model.
+This highlights the predictive ability of the FE model for both inclination angles.
+
+Figures \ref{Fy_0} and \ref{Fy_6} show the results for the feed force, where the two clearest trends for the experiments are its decrease with inclination angle and its increase with the uncut chip thickness (even if it is smaller that the expectations).
+For 80 \textmu{}m, $F_f$ globally decreases with $v_c$ in the experiments.
+For 40 \textmu{}m and 60 \textmu{}m, the force decreases at lower $v_c$ and then increases for 0\textdegree{}, while a decrease is observed at all $v_c$ for 6\textdegree{}.
+For the numerical values, the global trend is the same for the 3 uncut chip thicknesses and both inclination angles: a decrease for the lowest $v_c$ values and then an increase.
+It must be noted that the numerical model does not handle correctly the feed force trends: as clearly shown by Figure \ref{Fy_6}, the numerical forces have globally an increasing trend with the cutting speed, while their mean value mostly decreases when the uncut chip thickness increases.
+Differences between the mean numerical and experimental values increase with the uncut chip thickness: forces are closer at 40 \textmu{}m than at 80 \textmu{}m.
+The numerical values are mostly not within the 95\% confidence interval (it has no clear evolution with the cutting conditions).
+Coupled with the differences in trends, it shows that $F_f$ is less well modelled (mean difference is 35\%) than $F_c$ as usual in FE modelling of the cutting \hl{process} \cite{}.
+The influence of the uncut chip thickness on the feed force should therefore be improved.
+Material constitutive model parameters are known to have an impact on the forces (and on the chip \hl{morphology)} \cite{duco}.
+The friction model should be improved as well to enhance the results.
+
+Passive force is non-zero for the inclination angle of 6\textdegree{} (Figure \ref{Fz_6}).
+As the cutting force, it increases with the uncut chip thickness and it decreases with the cutting speed.
+Comparison with the experiments is globally the same as for $F_c$, except for a larger difference in the magnitude of $F_p$ (mean difference is 26\%, but it is small in absolute – less than 5 N).
+The numerical values are mostly not in the 95\% experimental confidence interval.
+
+Regarding the chips morphology, all the chips are continuous. For both the simulation and the experiments, the chip thickness ratio, $\lambda_h$:
+\begin{equation}
+\lambda_h = \frac{h'}{h}
+\end{equation}
+with $h$ the uncut chip thickness and $h'$ the chip thickness, is almost independent of the uncut chip thickness.
+It is slightly reduced from $\lambda_s = 0$\textdegree{} to $\lambda_s = 6$\textdegree{}, meaning that the chip thickness is reduced with the inclination angle.
+This influence is underestimated by the model: the reduction of $\lambda_h$ is lower than in the experiments.
+The mean difference between experimental and numerical $\lambda_h$ is 17\% across the whole range of cutting conditions.
+The chip thickness ratio decreases with the cutting speed because of the reduction of friction, which is correctly captured by the model.
+As for the feed force, the results should be improved by more complex friction models and a set of material constitutive parameters for which the identification includes the forces and the chip thickness \cite{kugalurpalanisamy_Identification_2022}.
+
+\begin{figure}[!h]
 \centering
 \includegraphics[width = 140 mm]{Figures/h0}
-\caption{Comparison of experimental (E) and numerical (N) chip thickness ratios at 0\textdegree{}}
+\caption{Comparison of experimental (E) and numerical (N) chip thickness ratios at the cutting edge inclination of 0\textdegree{} for the 3 uncut chip thicknesses (40, 60 and 80 \textmu{}m) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and 40 m/min)}
 \label{h0}
@@
 
-\begin{figure}[h]
+\begin{figure}[!h]
 \centering
 \includegraphics[width = 140 mm]{Figures/h6}
-\caption{Comparison of experimental (E) and numerical (N) chip thickness ratios at 6\textdegree{}}
+\caption{Comparison of experimental (E) and numerical (N) chip thickness ratios at the cutting edge inclination of 6\textdegree{} for the 3 uncut chip thicknesses (40, 60 and 80 \textmu{}m) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and 40 m/min)}
 \label{h6}
@@
 
-\hl{+ fig with sim chip and show that it is helical/spiral at 6 deg}
-\hl{+ Chip thickness is globally lower at 6 deg than 0 deg}
-\hl{+ Show side flow, non-uniform chip thickness}
+Differences computed according to equation \ref{eq:diff} \hl{+ comment} and link to Table \ref{tab:Synth}
 
-The increase of the cutting force with the uncut chip thickness is clearly observed in Figure 5 for both experimental and numerical results at the 2 inclination angles, as well as the decrease of the force with the increase in the cutting speed.
-This shows temperature softening domination on strain rate hardening for Ti6Al4V and that it is accurately modelled.
-The increase of the inclination angle from 0\textdegree{} to 6\textdegree{} reduces the cutting force; this is well captured by the model.
-For cutting speeds of 20-40 m/min, $F_c$ is almost constant for 40 \textmu{}m and 60 \textmu{}m, while it slightly decreases for 80 \textmu{}m; this small stabilisation is less marked for the model.
-Increase in the deviation around the mean value with the cutting speed is noted for values above 10 m/min.
-All numerical values are within a confidence interval of 95\% of the experiments (35 out of 36 conditions are within a confidence interval of 68\%) and the mean difference with the experiments is 3\%, which is remarkable, moreover given the wide range of cutting conditions considered.
-This highlights the predictive qualities of the FE model for both inclination angles.
-Figure 6 shows the results for the feed force, where the two clearest trends are its decrease with inclination angle and its increase with the uncut chip thickness for both experimental and numerical results.
-For 80 \textmu{}m, $F_f$ globally decreases with $v_c$ in the experiments.
-For 40 and 60 \textmu{}m, the force decreases at lower $v_c$ and then increases for 0\textdegree{}, while a decrease is observed at all $v_c$ for 6\textdegree{}.
-For the numerical values, the global trend is the same for the 3 uncut chip thicknesses and both inclination angles: a decrease for the lowest $v_c$ values and then an increase.
-The numerical values are mostly not within the 95\% confidence interval (it has no clear evolution with the cutting conditions).
-Coupled with the differences in trends, it shows that $F_f$ is less well modelled (mean difference is 35\%) as usual in FE modelling of the cutting process.
-Improving the friction model should enhance the results.
-Passive force is non-zero for the inclination angle of 6\textdegree{} (Figure 7).
-As the cutting force, it increases with the uncut chip thickness and it decreases with the cutting speed.
-Comparison with the experiments is globally the same as for $F_c$, except for a larger difference in the magnitude of $F_p$ (mean difference is 26\%, but it is small in absolute – less than 5 N).
-The numerical values are mostly not in the 95\% experimental confidence interval.
-Regarding the chips morphology, all of them are continuous.
-For both the simulation and the experiments, the chip thickness ratio, $\lambda_h$, decreases with the cutting speed because of reduction of friction and it is almost independent of the uncut chip thickness.
-The mean difference between experimental and numerical $\lambda_h$ is 13\% across the whole range of cutting conditions.
+%
+\begin{table}[!h]
+\begin{center}
+\caption{\label{tab:Synth} Synthetic overview of the results: differences between the experimental and the numerical results (mean difference for each cutting edge inclination, and maximal, minimal and mean differences for all the conditions) for the cutting force, $\Delta F_c$, the feed force, $\Delta F_f$, the passive force, $\Delta F_p$, and the chip thickness ratio, $\Delta \lambda_h$}
+\begin{tabular}{lllll}
+\hline\noalign{\smallskip}
+Difference & $\Delta F_c$ (\%) & $\Delta F_f$ (\%) & $\Delta F_p$ (\%) & $\Delta \lambda_h$ (\%)\\
+\hline\noalign{\smallskip}
+Mean $\lambda_s = 0$\textdegree{} & 3 & 38 & -- & 14\\
+Mean $\lambda_s = 6$\textdegree{} & 4 & 40 & 26 & 21\\
+Max global & 10 & 60 & 29 & 38\\
+Min global & 1 & 10 & 19 & 2\\
+Mean global & 4 & 39 & 26 & 17\\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+\end{tabular}
+\end{center}
+\end{table}
+%
 
-\FD{Check clearly stated that Ff trend is globally NOK: improve friction and mat para also cf. Metals Kuga + increase with h quite low in the exp.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In this paper, an experimental study has been carried out in free orthogonal and oblique cutting for Ti6Al4V.
+In this paper, an experimental study has been carried out in free orthogonal and oblique cutting of the titanium alloy Ti6Al4V.
 It is a reference to assess the performances of the 3D FE model introducing an ANN-based constitutive model and developed in the same conditions.
-An unpreviously seen wide range of cutting conditions, 36, is considered, including 2 inclination angles.
+An unpreviously seen wide range of cutting conditions, 36, is considered, including 2 cutting edge inclinations.
 Accurate evaluation of fundamental variables in 3D with the absence of tuning of both numerical parameters and model features when cutting conditions and inclination angle are significantly modified is a strong novelty of this work.
 Only changing the inclination angle to move from free orthogonal to oblique cutting while maintaining the quality of the results has no equivalent in the current literature, moreover as no study on free oblique cutting is available.
-Predictive abilities of the model make it adequate for development of tools with a straight cutting edge, for example.
-
-\hl{this works opens possibilities in both 3D free orthogonal cutting and ANN based material behaviours}
+Predictive abilities of the model make it adequate for development of tools with a straight cutting edge, for example, providing the modelling of the feed force is improved if it is relevant for the study.
+This work moreover demonstrates the ability to model materials behaviour with ANN and opens possibilities in this promising direction.
 
@@
 
-The training of the neural network was performed using a data set containing $3\,430$ data points defined by: \FD{Add units for min and max values?}
+The training of the neural network was performed using a data set containing $3\,430$ data points defined by:
 \begin{itemize}
@@
 \item $7$ plastic strain rates $\mdot{\varepsilon}^p\in[1, 10, 50, 500, 5\,000, 50\,000, 500\,000]$, so that $[\ln(\mdot{\varepsilon}^p)]_{min}=0$ and $[\ln(\mdot{\varepsilon}^p)]_{max}=13.12236$.
-\item  $7$ temperatures $T\in[293, 400, 500, 700, 900, 1\,200, 1\,500]$, so that $[T]_{min}=293$ and $[T]_{max}=1\ 500$.
+\FD{Add units to values?}
+\item  $7$ temperatures $T\in[293, 400, 500, 700, 900, 1\,200, 1\,500]$, so that $[T]_{min}=293$ and $[T]_{max}=1\ 500$. \FD{Add units to values?}
 \end{itemize}
 
-Stresses in the training dataset ranges from $[\sigma]_{min}=171.44$ to $[\sigma]_{max}=2606.12$.
-The results of the training process are given below for quantities $\w_1$, $\w_2$, $\overrightarrow{w}$, $\overrightarrow{b_1}$, $\overrightarrow{b_2}$ and $b$.\FD{sigma y?}
+Stresses in the training dataset ranges from $[\sigma^y]_{min}=171.44$ to $[\sigma^y]_{max}=2606.12$.
+The results of the training process are given below for quantities $\w_1$, $\w_2$, $\overrightarrow{w}$, $\overrightarrow{b_1}$, $\overrightarrow{b_2}$ and $b$.
 

### 2022-10-07 Article.tex
Update of text and references to reach 1st version

--- 2022-09-21 Article.tex
@@
 
-%% The lineno packages adds line numbers. Start line numbering with
+%% The lineno package adds line numbers. Start line numbering with
 %% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
@@
 \usepackage{textcomp} %Permet d'introduire un mu droit à l'aide de \textmu en dehors de l'environnement math
-
 %\usepackage[leftbars]{changebar} %Pour insérer une barre de mise à  jour (à  gauche car [leftbars]) au moyen de \begin{changebar} %Ne fonctionne pas pour passer du DVI au pdf -> utiliser DV -> PS -> pdf %Ne fontionne pas avec figure* et table*
-
 \usepackage{multirow}
 %\usepackage{rotating} %Pour effectuer la rotation d'un tableau à  l'aide de "\begin{sidewaystable} et \end{}" et supprimer "\begin{table} et \end{}"
+%\usepackage{dblfloatfix} % fix for bottom-placement of figure*
+\usepackage{siunitx}
+\sisetup{
+  per-mode = symbol,
+  range-units = single,
+  range-phrase = --,
+  bracket-unit-denominator = false,
+  output-decimal-marker = {.},
+%  output-decimal-marker = {,},
+  group-digits = integer,
+  output-exponent-marker = \mathrm{E},
+  tight-spacing = true,
+  text-series-to-math = true,
+  locale = UK,
+%  locale = FR
+}%
+
 \usepackage{pdflscape}
@@
 \usepackage{accents}
-
-\usepackage{dblfloatfix} % fix for bottom-placement of figure*
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% To insert highlighted comments with author's name
+% To insert highlighted comments with the author's name
 % Adapted from https://www.willusher.io/latex/2018/07/10/comments-in-latex
@@
 
-\title{Predictive 3D modelling of free oblique cutting of Ti6Al4V titanium alloy and experimental validation for a wide range of conditions\\ \FD{Include AI?}}
+\title{Predictive 3D modelling of free oblique cutting with an ANN-based material constitutive model and experimental validation over a wide range of conditions}
 
@@
 
-Modelling of the cutting process needs to move from a 2D to a 3D configuration to get closer to industrial applications.
-The study introduces a predictive 3D finite element model of free orthogonal and oblique cutting with an ANN-based material constitutive model and experimental validation in strictly the same conditions (cutting and geometrical).
-Predictive performance of the model is high for the forces in the 3 directions and the chip thickness ratio on all 36 cutting conditions (including 2 inclination angles).
-Accuracy of the main cutting force is excellent: the mean difference with the experiments is 3\%.
+Modelling of the cutting process needs to move from 2D to 3D configurations to get closer to industrial applications.
+This study introduces a predictive 3D finite element model of free orthogonal and oblique cutting with an ANN-based material constitutive model and experimental validation in strictly the same conditions (cutting and geometrical).
+The developments are applied to the formation of continuous chips for the titanium alloy Ti6Al4V and an unseen broad range of 36 cutting conditions is considered: 2 cutting edge inclinations, 3 uncut chip thicknesses and 6 cutting speeds.
+The predictive performance of the model (i.e., the evaluation of the trends of fundamental variables with the absence of tuning of both numerical parameters and model features when cutting conditions are significantly modified) is high for the forces, mainly cutting and passive, and the chip thickness ratio on all 36 cutting conditions.
+The accuracy of the main cutting force is excellent: the mean difference with the experiments is 4\%, within the experimental dispersion.
+No significant degradation of the results is brought by the apparition of the third, out-of-plane, force, which shows the ability of the model to handle orthogonal and oblique cutting configurations.
 
-\FD{Review and update}
+\FD{Add a comment on ANN?}
 
@@
 
-Selection of the tools and the cutting conditions in machining, but also comprehension of the influence of the process parameters on the quality of a component and its optimisation, are still difficult to achieve because of the high level of complexity and linked nonlinear phenomena.
-In the frame of digital manufacturing and Industry 4.0, modelling of the cutting process supports them, while remaining a challenging task.
+Selection of the tools and the cutting conditions in machining, but also comprehension of the influence of the process parameters on the quality of a component and its optimization, are still difficult to achieve because of the high level of complexity and linked nonlinear phenomena.
+In the frame of digital manufacturing and Industry 4.0, modelling the cutting process supports them, while remaining a challenging task.
 As highlighted by Arrazola et al.
-\cite{arrazola_Recent_2013}, most finite element (FE) models are developed in 2D (orthogonal cutting configuration usually) although industrial applications require a 3D modelling.
+\cite{arrazola_Recent_2013}, most finite element (FE) models are developed in 2D (orthogonal cutting configuration usually) although industrial applications require 3D modelling.
 
@@
 This is often achieved in turning \cite{agmell_Development_2018} or in milling \cite{xu_Simulation_2021} and the diameter of the rotating part must be large enough to reduce the influence of the curvature on the results.
-Experimental configurations in strictly orthogonal cutting conditions are less often adopted, for example, in broaching \cite{abouridouane_Friction_2021} or milling \cite{ducobu_Experimental_2015, sela_Measurement_2021} machines.
+Experimental configurations in strictly orthogonal cutting conditions are less often adopted, for example, on broaching \cite{abouridouane_Friction_2021} or milling \cite{ducobu_Experimental_2015, sela_Measurement_2021} machines.
 While they remove assumptions linked to the rotating cutting movement, they usually allow for lower cutting speeds (except on a dedicated machine, such as in Afrasiabi et al.
@@
 %
-The flow stress, $\sigma^{y}$, is a function of the plastic strain, $\varepsilon^{p}$, of the plastic strain rate, ${\dot{\varepsilon}}^{p}$, and of the temperature, $T$.
+In this model, the flow stress, $\sigma^{y}$, is a function of the plastic strain, $\varepsilon^{p}$, of the plastic strain rate, ${\dot{\varepsilon}}^{p}$, and of the temperature, $T$.
 It is composed of 3 terms describing independently plastic, viscous and thermal aspects.
@@
 \cite{calamaz_New_2008}, increase this number of parameters (for Calamaz's particular model to 9).
-The better (in theory) description of the behaviour is achieved at the cost of greater complexity of the identification process and of a reduction of the link with the physical meaning of the model.
-When a continuous chip is formed, JC model \hl{has moreover proved to be well-suited} \cite{}.
+The better (in theory) description of the behaviour is achieved at the cost of a greater complexity of the identification process and of a reduction of the link with the physical meaning of the model.
 
-One issue of material behaviour modelling for cutting simulation is the identification of the model parameters, moreover as the experimental equipment does not allow to reach the high levels of strains, strain rates and temperature of machining \cite{melkote_Advances_2017}.
+One issue of material behaviour modelling for cutting simulation is the identification of the parameters, moreover, as the experimental equipment does not allow to reach the high levels of strains, strain rates and temperature of machining \cite{melkote_Advances_2017}.
 Inverse identification is an alternative, but the uniqueness of the solution is not always guaranteed \cite{arrazola_Recent_2013, melkote_Advances_2017}.
@@
 \cite{bosetti_Identification_2013} and Denkena et al.
-\cite{denkena_Inverse_2015}, the approach to tackle the inverse identification problem is moving from optimisation to Artificial Intelligence (AI) based methods.
+\cite{denkena_Inverse_2015}, the approach to tackle the inverse identification problem is moving from optimization to Artificial Intelligence (AI) based methods.
 The Downhill Simplex Algorithm (DSA) is adopted by Bergs et al.
 \cite{bergs_Determination_2020} and by Hardt et al.
-\cite{hardt_Investigations_2021} for AISI 1045.
+\cite{hardt_Investigations_2021} for AISI~1045.
 Stampfer et al.
-\cite{stampfer_Material_2021} also selected the DSA when dealing with AISI 4140 tempered at 3 different temperatures.
+\cite{stampfer_Material_2021} also selected the DSA when dealing with AISI~4140 tempered at 3 different temperatures.
 In \cite{hardt_Application_2021}, Hardt et al.
-showed that the Particle Swarm Optimization (PSO) was more efficient to solve the inverse problem than the Downhill Simplex Algorithm, even if computation time is still significant.
+showed that the Particle Swarm Optimization (PSO) was more efficient to solve the inverse problem than the DSA, even if computation time is still significant.
 In an effort to reduce it, an Efficient Global Optimization (EGO) algorithm has recently been introduced by Kugalur Palanisamy et al.
@@
 \cite{pantale_Efficient_2022}, is implemented in a FE cutting model for the first time instead of the analytical JC law.
-A broad range of cutting speeds (6), uncut chip thicknesses (3) and inclination angles (2) resulting in 36 different conditions are considered to demonstrate the predictive ability of the FE model for fundamental variables.
-No assumption is made about the geometry of the machined workpiece in the model (i.e.
-its width is the same as in the experiments), while keeping computation time relevant for industrial applications.
-The developments apply to the titanium alloy Ti6Al4V.
+A broad range of cutting speeds (6), uncut chip thicknesses (3) and cutting edge inclination angles (2) resulting in 36 different conditions is considered to demonstrate the predictive ability of the FE model for fundamental variables.
+The main goals of a predictive model are the accurate modelling of the trends of the results when the conditions change and the good agreement of the predicted values with the experimental ones (exact values are not looked for due to experimental dispersions).
+This type of models aims at supporting future choices and developments without the need for experimental data.
+No assumption is made about the geometry of the machined workpiece in the model (i.e., its width is the same as in the experiments), while keeping computation time relevant for industrial applications.
+The developments are applied to the formation of continuous chips of titanium alloy Ti6Al4V.
 
@@
 
-A 3-axis GF Mikron VCE 600 Pro milling machine is used to carry out dry free orthogonal and oblique cutting tests on Ti6Al4V (grade 5 annealed at 750\textdegree{}C for 1 h followed by air cooling) with the same kinematics as a shaper.
-As shown in Figure \ref{ExpSetup}, the tungsten carbide tool (modified LCGN160602-0600-FG, CP500 from SECO) is fixed on a dedicated holder (modified CFHN-06 from SECO) and the sample to be cut is clamped in the spindle (no rotation is allowed during the test).
-The top of the sample includes 3 ribs of 1 mm in width (width of the tool is 6 mm) and 10 mm in length.
+A 3-axis GF Mikron VCE 600 Pro milling machine is used to carry out dry free orthogonal and oblique cutting tests on Ti6Al4V (grade 5 annealed at \qty{750}{\degreeCelsius} for \qty{1}{\hour} followed by air cooling) with the same kinematics as a shaper.
+As shown in Figure \ref{fig:ExpSetup}, the tungsten carbide tool (modified LCGN160602-0600-FG, CP500 from SECO) is fixed on a dedicated holder (modified CFHN-06 from SECO) and the sample to be cut is clamped in the spindle (no rotation is allowed during the test).
+The top of the sample includes 3 ribs of \qty{1}{\mm} in width (the width of the tool is \qty{6}{\mm}) and \qty{10}{\mm} in length.
 The test consists of removing the upper layer (its height is the uncut chip thickness, $h$) of one rib at the prescribed cutting speed, $v_c$.
 The cutting speed is provided by the feed rate, $v_f$, of the machine (max.
-value of 40 m/min).
+value of \qty{40}{\metre\per\min}).
 The tool cutting edge inclination, $\lambda_s$, results from the relative angular orientation of the tool and the sample.
@@
 \caption{Experimental setup}
-\label{ExpSetup}
+\label{fig:ExpSetup}
 \end{figure}
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-Cutting speed, $v_c$ (m/min) & 5, 7.5, 10, 20, 30, 40\\
-Uncut chip thickness, $h$ (\textmu{}m) & 40, 60, 80\\
-Cutting edge inclination, $\lambda_s$ (\textdegree{}) & 0, 6\\
-Width of the workpiece (mm) & 1\\
-Length of the workpiece (mm) & 10\\
-Width of the cutting edge (mm) & 6 (1.1 in the model)\\
-Cutting edge radius, $r_\beta$ (\textmu{}m) & 20\\
-Rake angle, $\gamma_0$ (\textdegree{}) & 15\\
-Clearance angle, $\alpha_0$ (\textdegree{}) & 2\\
+Cutting speed, $v_c$ (\unit{\metre\per\min}) & 5, 7.5, 10, 20, 30, 40\\
+Uncut chip thickness, $h$ (\unit{\um}) & 40, 60, 80\\
+Cutting edge inclination, $\lambda_s$ (\unit{\degree}) & 0, 6\\
+Width of the workpiece (\unit{\mm}) & 1\\
+Length of the workpiece (\unit{\mm}) & 10\\
+Width of the cutting edge (\unit{\mm}) & 6 (1.1 in the model)\\
+Cutting edge radius, $r_\beta$ (\unit{\um}) & 20\\
+Rake angle, $\gamma_0$ (\unit{\degree}) & 15\\
+Clearance angle, $\alpha_0$ (\unit{\degree}) & 2\\
 \noalign{\smallskip}\hline
@@
 Forces are measured with a 3-component Kistler 9257B dynamometer and are amplified by a Kistler 5070A charge amplifier.
-Acquisition is performed at 3 kHz with a Kistler 5697A2 data acquisition system and the DynoWare software.
-Recorded forces are then filtered with a second-order low-pass Bessel filter at 750 Hz before computing the mean value of the signal at steady state.
+The acquisition is performed at \qty{3}{\kHz} with a Kistler 5697A2 data acquisition system and the DynoWare software.
+Recorded forces are then filtered with a second-order low-pass Bessel filter at \qty{750}{\Hz} before computing the mean value of the signal at the steady state.
 
-All the chips are collected and observed with a Dino Lite digital microscope AM7013MZT (5 MP, magnification $20\times$ -- $250\times$).
+All the chips are collected and observed with a Dino Lite digital microscope AM7013MZT (5~MP, magnification $20\times$ -- $250\times$).
 Each chip is measured 3 times along its length to get a mean value representative of the whole chip.
@@
 The CEL formulation is adopted to model the dry free orthogonal and oblique cutting tests with Abaqus/Explicit 2020.
-The 3D model is composed of a fixed Lagrangian tool and a Eulerian workpiece (Figure \ref{BC}).
+The 3D model is composed of a fixed Lagrangian tool and a Eulerian workpiece (Figure \ref{fig:BC}).
 Chip formation occurs by plastic flow across the Eulerian domain with no mesh distortion.
@@
 \caption{Boundary conditions and schematic initial geometry of the model}
-\label{BC}
+\label{fig:BC}
 \end{figure}
 
-As shown in Figure \ref{FEConfig}, the full width of the workpiece, i.e.
-a rib in the experiments, (1 mm) is modelled.
+As shown in Figure \ref{fig:FEConfig}, the full width of the workpiece (\qty{1}{\mm}), i.e., a rib in the experiments, is modelled.
 To allow chip formation and side flow, the Eulerian domain is wider (it includes the volume in which material can move).
 The volume above the initial workpiece is also meshed with Eulerian elements for the same reasons.
-As in the experiments and to fulfil the hypothesis of free orthogonal and oblique cutting, the tool is wider than the workpiece (it is of 1.1 mm in the model and of 6 mm in the experiments).
-It is very important to stress that the models are the same for both inclination angles: they only differ by the rotation of the tool of 6\textdegree{} about Y axis as in the experiments (Figure \ref{FEConfig}).
-This, coupled to the absence of assumptions when developing the models, contributes to make the models predictive: no input is changed when cutting conditions do.
+As in the experiments and to fulfil the hypothesis of free orthogonal and oblique cutting, the tool is wider than the workpiece (it is \qty{1.1}{\mm} in the model and \qty{6}{\mm} in the experiments).
+It is very important to stress that the models are the same for both inclination angles: they only differ by the rotation of the tool of \qty{6}{\degree} about Y axis as in the experiments (Figure \ref{fig:FEConfig}).
+This, coupled with the absence of assumptions when developing the models, contributes to make the models predictive: no input is changed when cutting conditions do.
 
-\begin{figure}[h]
+\begin{figure}[!h]
 \centering
 \includegraphics[width = 140 mm]{Figures/FEConfig}
-\caption{Configuration of the FE model for $\lambda_s$ = 6\textdegree{}}
-\label{FEConfig}
+\caption{Configuration of the FE model for $\lambda_s$ = \qty{6}{\degree}}
+\label{fig:FEConfig}
 \end{figure}
 
-According to a previous mesh sensitivity study in orthogonal cutting with the CEL formulation \cite{ducobu_Finite_2017}, elements edge size is 5 \textmu{}m in the plane parallel to the cutting speed.
-In the direction perpendicular to this plane, it is 5 \textmu{}m in areas close to the lateral boundaries of the Eulerian domain and 50 \textmu{}m in the middle of the workpiece.
+According to a previous mesh sensitivity study in orthogonal cutting with the CEL formulation \cite{ducobu_Finite_2017}, elements edge size is \qty{5}{\um} in the plane parallel to the cutting speed.
+In the direction perpendicular to this plane, it is \qty{5}{\um} in areas close to the lateral boundaries of the Eulerian domain and \qty{50}{\um} in the middle of the workpiece.
 To reduce computation time, the size of the model depends on the value of the uncut chip thickness.
-This results in a Eulerian domain (EC3D8RT linear 3D Eulerian elements with 8 nodes, coupled mechanical-thermal behaviour and reduced integration) composed of 216,550 to 273,350 nodes and a Langrangian domain (C3D8T linear 3D Lagrangian elements with 8 nodes, coupled mechanical-thermal behaviour) of 4,650 nodes.
+This results in a Eulerian domain (EC3D8RT linear 3D Eulerian elements with 8 nodes, coupled mechanical-thermal behaviour and reduced integration) composed of \num{216550} to \num{273350} nodes and a Lagrangian domain (C3D8T linear 3D Lagrangian elements with 8 nodes, coupled mechanical-thermal behaviour) of \num{4650} nodes.
 
-The Ti6Al4V workpiece is assumed to be thermo-elasto-viscoplastic (isotropic) and inelastic heat fraction is 0.9.
+The Ti6Al4V workpiece is assumed to be thermo-elasto-viscoplastic (isotropic) and the inelastic heat fraction is 0.9.
 JC set of parameters from Seo et al.
@@
 \hline\noalign{\smallskip}
-Young's modulus, $E$ (GPa) & Ti6Al4V & 113.8$^*$\\
+Young's modulus, $E$ (\unit{\GPa}) & Ti6Al4V & 113.8$^*$\\
  & WC & 650\\
@@
  & WC & 0.2\\
-Density, $\rho$ (kg/m$^3$) & Ti6Al4V & 4,430\\
- & WC & 14,850\\
-Conductivity, $k$ (W/mK) & Ti6Al4V & 6.3$^*$\\
+Density, $\rho$ (\unit{\kg\per\cubic\m}) & Ti6Al4V & \num{4430}\\
+ & WC & \num{14850}\\
+Conductivity, $k$ (\unit{\W\per\metre\per\K}) & Ti6Al4V & 6.3$^*$\\
  & WC & 100\\
-Expansion, $\alpha$ (K$^{-1}$) & Ti6Al4V & 8.6 e$^{-6*}$\\
- & WC & 5 e$^{-6}$\\
-Specific heat, $c_{p}$ (J/KgK) & Ti6Al4V & 531$^*$\\
+Expansion, $\alpha$ (\unit{\per\K}) & Ti6Al4V & \num{8.6e-6}$^{*}$\\
+ & WC & \num{5e-6}\\
+Specific heat, $c_{p}$ (\unit{\J\per\kg\per\K}) & Ti6Al4V & 531$^*$\\
  & WC & 202\\
 \noalign{\smallskip}\hline\noalign{\smallskip}
-JC constitutive model & $A$ (MPa) & 997.9\\
- & $B$ (MPa) & 653.1\\
- & $C$ & 0.0198\\
+JC constitutive model & $A$ (\unit{\MPa}) & 997.9\\
+ & $B$ (\unit{\MPa}) & 653.1\\
+ & $C$ & \num{0.0198}\\
  & $m$ & 0.7\\
  & $n$ & 0.45\\
- & $\dot{\varepsilon}_{0}$ (s$^{-1}$) & 1\\
- & $T_{\text{room}}$ (K) & 293\\
- & $T_{\text{melt}}$ (K) & 1873\\
+ & $\dot{\varepsilon}_{0}$ (\unit{\per\s}) & 1\\
+ & $T_{\text{room}}$ (\unit{\K}) & 293\\
+ & $T_{\text{melt}}$ (\unit{\K}) & 1873\\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 \end{center}
-\vspace{-0.4cm}$^*$: Dependence to the temperature, value provided at 293 K
+\vspace{-0.4cm}$^*$: Dependence on the temperature, value provided at \qty{293}{\K}
 \end{table}
@@
 \hline\noalign{\smallskip}
-Cutting speed, $v_c$ (m/min) & $\mu$ & $\beta$\\
+Cutting speed, $v_c$ (\unit{\m\per\min}) & $\mu$ & $\beta$\\
+\noalign{\smallskip}\hline\noalign{\smallskip}
 5 & 0.24 & 1\\
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-Limiting shear stress, $\tau_{\text{max}}$ (MPa) & 576\\
-Convection, $U$ (W/m$^2$K) & 50\\
+Limiting shear stress, $\tau_{\text{max}}$ (\unit{\MPa}) & 576\\
+Convection, $U$ (\unit{\W\per\square\m\per\K}) & 50\\
 Radiation, $\epsilon$ & 0.3\\
@@
 
-Room temperature of 293 K is imposed on the upper and right surfaces of the tool and on the left and bottom surfaces of the workpiece (Figure \ref{BC}).
+A room temperature of \qty{293}{\K} is imposed on the upper and right surfaces of the tool and on the left and bottom surfaces of the workpiece (Figure \ref{fig:BC}).
 Radiation and convection are assumed to occur on the rake and clearance faces of the tool.
-Initial temperature of the tool and the workpiece is set to room temperature (293 K).
+The initial temperature of the tool and the workpiece is set to room temperature (\qty{293}{\K}).
 Heat transfer coefficients are provided in Table \ref{tab:fricHeat}.
@@
 in \cite{pantale_Efficient_2022}.
-The principle of this approach consists in replacing the analytical formulation of the flow law, based on a Johnson-Cook or Zerilli-Armstrong type model, and allowing the calculation of the flow stress $\sigma^y$ as a function of the plastic strain $\varepsilon^p$, of the plastic strain rate, ${\dot{\varepsilon}}^p$, and of the temperature $T$, by a multi-layer ANN serving as universal approximator.
+The principle of this approach consists in replacing the analytical formulation of the flow law, based on a Johnson-Cook or Zerilli-Armstrong type model, and allowing the calculation of the flow stress $\sigma^y$ as a function of the plastic strain $\varepsilon^p$, of the plastic strain rate, ${\dot{\varepsilon}}^p$, and of the temperature $T$, by a multi-layer ANN serving as a universal approximator.
 Thus, the parameters of the neural network can directly be identified from the experimental data without having to postulate a behavioural model, which simplifies the procedure and allows more flexibility in the definition of the model.
@@
 
-In order to verify the influence of the complexity of the neural network on the numerical results of the simulation and the computing time, several architectures of ANN are tested thereafter (in \ref{subsec:nberneu}).
+In order to verify the influence of the complexity of the neural network on the numerical results of the simulation and on the computing time, several architectures of ANN are tested thereafter (in \ref{subsec:nberneu}).
 The chosen global architecture has 2 hidden layers with a variable number of neurons for the first hidden layer ($\zeta$ = 9 to 17) and 7 neurons for the second hidden layer, 3 inputs (plastic strain, $\varepsilon^p$, plastic strain rate, ${\dot{\varepsilon}}^p$, and temperature, $T$) and one output (the yield stress, $\sigma^y$).
-The global architecture of this kind of ANN is given in Figure \ref{ANN} for 9 neurons in the first hidden layer.
+The global architecture of this kind of ANN is given in Figure \ref{fig:ANN} for 9 neurons in the first hidden layer.
 Conforming to Pantalé et al.
-\cite{pantale_Efficient_2022}, this ANN is referred after the terminology ANN 3-9-7-1-sig, because it has 3 inputs, 9 neurons in the first hidden layer, 7 neurons in the second hidden layer, 1 output and a sigmoid activation function.
+\cite{pantale_Efficient_2022}, this ANN is referred to after the terminology ANN 3-9-7-1-sig, because it has 3 inputs, 9 neurons in the first hidden layer, 7 neurons in the second hidden layer, 1 output and a sigmoid activation function.
 
-\begin{figure}[h]
+\begin{figure}[!h]
 \centering
@@
 \caption{Architecture of the ANN 3-9-7-1-sig used for the flow law}
-\label{ANN}
+\label{fig:ANN}
 \end{figure}
@@
 
-Because of the large number of identified parameters for all the ANN models (from 114 to 202 for 9 and 17 neurons for the first hidden layer, respectively); the other 4 sets of ANN parameters used in this publication can be found in \cite{pantale_Coefficients_2022}.\FD{Inclure dans corps du texte puisque article normal et rq reviewer?}
+Because of the large number of identified parameters for all the ANN models (from 114 to 202 for 9 and 17 neurons for the first hidden layer, respectively), the other 4 sets of ANN parameters used in this publication can be found in \cite{pantale_Coefficients_2022}.\FD{Inclure dans corps du texte puisque article normal et rq reviewer?}
 
@@
 
-FE modelling of the cutting process is very expensive in CPU computation time because of the coupling fn many nonlinear phenomena and the large amount of tiny finite elements.
+FE modelling of the cutting process is very expensive in CPU computation time because of the coupling of many nonlinear phenomena and the large amount of tiny finite elements.
 Mass scaling (MS) is introduced in the model to reduce the CPU computation time while checking that it does not influence the results (forces and energies) via a mass scaling sensitivity study.
-MS factors, ${MS}_f$, ranging from 1E6 (theoretical scaling of CPU time of $\sqrt{{MS}_f} = 1000$) to 1 (no scaling) have been used for one cutting condition ($\lambda_s$ = 0\textdegree{}, $v_c$ = 30 m/min and $h$ = 60 \textmu{}m).
+MS factors, ${MS}_f$, ranging from \num{1E6} (theoretical scaling of CPU time of $\sqrt{{MS}_f} = \num{1000}$) to 1 (no scaling) have been used for one cutting condition ($\lambda_s$ = \qty{0}{\degree}, $v_c$ = \qty{30}{\m\per\min} and $h$ = \qty{60}{\um}).
 The same signal processing procedure is applied to the numerical forces as to the experimental forces (cf.
-\ref{ExpSet}): they are filtered with a second-order low-pass Bessel filter at 750 Hz before computing the mean value at steady state.
-Table \ref{tab:MS} gives the results normalised ($\hat{F_i}$) by these of the model without MS:
+\ref{ExpSet}): they are filtered with a second-order low-pass Bessel filter at \qty{750}{\Hz} before computing the mean value at steady state.
+Table \ref{tab:MS} gives the results of the model with MS normalized ($\hat{F_i}$) by these of the model without MS:
 %
@@
 %
-With $i = c$ for the cutting force and $i = f$ for the feed force.
+with $i = c$ for the cutting force and $i = f$ for the feed force.
 As expected, actual speed-up does not increase linearly with the ${MS}_f$, but it is still significant.
-${MS}_f$ of 1E6 leads to unstable computation and ${MS}_f$ of 1E5 results in erratic forces evolutions.
+${MS}_f$ of \num{1E6} leads to unstable computation and ${MS}_f$ of 1E5 results in erratic forces evolutions.
 These results are confirmed by high values of the kinetic ($KE$) on internal ($IE$) energies ratio (it should not exceed a few \% \cite{wang_Investigation_2011, ducobu_Introduction_2015}).
-A ${MS}_f$ value of 1E3 is selected as it provides a good balance between computation time reduction and impact on forces, while keeping $\frac{KE}{IE}$ below 1\%.
-To provide an order of magnitude of CPU computation time, between 10 h and 50 h (depending on the value of $h$) are needed on 4 cores of an Intel i7-5700HQ CPU at 2.7 -- 3.5 GHz.
+An ${MS}_f$ value of 1E3 is selected as it provides a good balance between computation time reduction and impact on forces, while keeping $\frac{KE}{IE}$ below 1\%.
+To provide an order of magnitude of CPU computation time, between \qty{10}{\hour} and \qty{50}{\hour} (depending on the value of $h$) are needed on 4 cores of an Intel i7-5700HQ CPU at \qtyrange{2.7}{3.5}{\GHz}.
 
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-1 & 1 & 1 & 1 & 1 & 2.3E-4\\
-1E2 & 10 & 9 & 1.006 & 0.982 & 2.2E-2\\
-\textbf{1E3} & \textbf{32} & \textbf{21} & \textbf{1.008} & \textbf{0.940} & \textbf{2.2E-1}\\
-1E4 & 100 & 61 & 1.012 & 0.921 & 2.4\\
-1E5 & 316 & 173 & Erratic & Erratic & 22\\
-1E6 & 1000 & 207 & Unstable & Unstable & 58\\
+1 & 1 & 1 & 1 & 1 & \num{2.3E-4}\\
+\num{1E2} & 10 & 9 & 1.006 & 0.982 & \num{2.2E-2}\\
+\textbf{\num{1E3}} & \textbf{32} & \textbf{21} & \textbf{1.008} & \textbf{0.940} & \textbf{\num{2.2E-1}}\\
+\num{1E4} & 100 & 61 & 1.012 & 0.921 & 2.4\\
+\num{1E5} & 316 & 173 & Erratic & Erratic & 22\\
+\num{1E6} & 1000 & 207 & Unstable & Unstable & 58\\
 \noalign{\smallskip}\hline
@@
 The results of the study are provided in Table \ref{tab:NbNeurons}.
-$\check{F_i}$ corresponds to the results normalised by these of the model with the built-in JC model:
+$\check{F_i}$ corresponds to the results of the model with ANN normalized by these of the model with the built-in JC model:
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%
-\FD{Show chips? + info on side flow? + dedicated subsection on chip thickness? (give also results in a plot?)}
-Mean and standard deviation ($2\sigma$) are computed from the 3 experimental values and are shown in Figures \hl{5 to 7}.
-Mean numerical values are plotted inside the experimental bars in Figures \hl{5 to 7}.
-\FD{sigma deja utilise mais equa (5) devrait etre sigma y - voir avec Olivier}
-\FD{Add a table with mean differences as a kind of summary of the results?}
 
-\begin{figure}[h]
+An example of temporal evolutions of numerical and experimental forces is plotted for the 3 directions in Figure \ref{fig:ExpNum_Forces_v10_40µ_6} at $\lambda_s =$ \qty{6}{\degree}, $v_c =$ \qty{10}{\m\per\min} and $h =$ \qty{40}{\m\per\min}.
+Computation of the FE models is carried out until a few microseconds after the steady state is reached.
+Then, linear extrapolation (dashed line between the two last markers in Figure \ref{fig:ExpNum_Forces_v10_40µ_6}) is used to provide numerical values during the same time range as the experimental values.
+Mean and standard deviation ($2\,\sigma$) are computed from the 3 experimental values.
+The resulting dispersion is plotted in Figure \ref{fig:ExpNum_Forces_v10_40µ_6} around the mean values of each force.
+Steady state takes more time to be reached for the experiments than in the numerical model, particularly for the cutting force.
+Dispersion around the mean force evolution is larger for the feed force than for the cutting force, while the mean feed force value is 46\% of the mean cutting force value.
+The numerical cutting force is very close to the experimental mean cutting force; it is only 4\% larger.
+This difference, $\Delta j$, is computed by
+%
+\begin{equation}\label{eq:diff}
+	\Delta j = \frac{\left|j^\text{(sim)} - j^\text{(exp)}\right|}{j^\text{(exp)}}\times 100
+\end{equation}
+%
+with $j$ the cutting force, the feed force, the passive force or the chip thickness. $j^\text{(sim)}$ is the mean value from the simulation, while $j^\text{(exp)}$ is the mean experimental value.
+
+The numerical feed force is underestimated by the model, but it is at the boundary of the 95\% experimental confidence interval.
+The numerical passive force difference is also underestimated and it is not in the narrower experimental dispersion.
+The difference between the mean values of experimental and numerical feed and passive forces is 25\%.
+A feed force less well modelled than the cutting force is typical of FE models of the cutting process and the difference with the experimental value is similar to other studies for a less extensive range of cutting conditions \cite{sima_Modified_2010, ducobu_Material_2016, karpat_Temperature_2011, zhang_Chip_2011,afrasiabi_NumericalExperimental_2021}.
+Hardt and Bergs \cite{hardt_Three_2021} also obtained higher differences for the feed and the passive force than for the cutting force.
+The difference for the passive force was higher than for the feed force, which is the opposite observation from this work.
+
+\begin{figure}[!h]
 \centering
 \includegraphics[width = 140 mm]{Figures/ExpNum_Forces_v10_40µ_6}
-\caption{Temporal evolutions of experimental (E) and numerical (N) forces at 6\textdegree{}, 10 m/min and 40 \textmu{}m: dispersion around mean experimental values and linear extrapolation of numerical values in dashed}
-\label{ExpNum_Forces_v10_40µ_6}
+\caption{Temporal evolutions of experimental (E) and numerical (N) forces at $\lambda_s =$ \qty{6}{\degree}, $v_c =$ \qty{10}{\m\per\min} and $h =$ \qty{40}{\um} with dispersion around mean experimental values (linear extrapolation of numerical values in dashed)}
+\label{fig:ExpNum_Forces_v10_40µ_6}
 \end{figure}
 
-\begin{figure}[h]
+Numerical chips at $v_c =$ \qty{10}{\m\per\min} and $h =$ \qty{40}{\um} for $\lambda_s =$ \qty{0}{\degree} and $\lambda_s =$ \qty{6}{\degree} are provided in Figures \ref{fig:ChipsNum} and \ref{fig:ChipsNumBack}.
+When the cutting edge inclination is \qty{0}{\degree}, both sides of the chip are identical and a symmetry plane can be drawn in the middle of the workpiece (Figure \ref{fig:ChipsNumBack} (a)).
+On the contrary, for the cutting edge inclination of \qty{6}{\degree}, the chip is not aligned with the workpiece any more.
+The chip bends on one side due to the orientation of the tool and the symmetry is lost for both the geometry, and the thermal and mechanical fields as highlighted in Figure \ref{fig:ChipsNumBack} (b).
+This produces helical chips for the inclination angle of \qty{6}{\degree} as in the experiments.
+Figure \ref{fig:ChipNumTop} shows the variation of the chip thickness across its width: it is thicker in the middle (i.e., the body of the chip) than on its sides.
+This stresses the importance of 3D modelling, even for the orthogonal cutting configuration as previously highlighted \cite{ducobu_Finite_2017}.
+3D modelling also allows to reproduce the side flow occurring in the experiments for both cutting edge inclination values (Figure \ref{fig:ChipsNum}), contrary to a 2D model \cite{xu_Simulation_2021, ambrosio_New_2022, ducobu_Finite_2017}.
+Although this leads to higher computation times, future cutting models should be in 3D, even when orthogonal cutting is considered.
+In this case, it is recommended to take advantage of the symmetry of the configuration to reduce computation time.
+This simplification has not been included in this study to avoid any difference in the FE models between the 2 cutting edge inclinations.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width = 140 mm]{Figures/ChipsNum}
+\caption{Temperature contours (in \unit{\K}) of the numerical chip after \qty{1.5}{\ms} at $v_c =$ \qty{10}{\m\per\min}, $h =$ \qty{40}{\um} and (a) $\lambda_s =$ \qty{0}{\degree}, (b) $\lambda_s =$ \qty{6}{\degree}}
+\label{fig:ChipsNum}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width = 140 mm]{Figures/ChipsNumBack}
+\caption{Temperature contours (in \unit{\K}) of the back of the numerical chip (tool is removed) after \qty{1.5}{\ms} at $v_c =$ \qty{10}{\m\per\min}, $h =$ \qty{40}{\um} and (a) $\lambda_s =$ \qty{0}{\degree}, (b) $\lambda_s =$ \qty{6}{\degree}}
+\label{fig:ChipsNumBack}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width = 140 mm]{Figures/ChipNumTop}
+\caption{Temperature contours (in \unit{\K}) of the top of the numerical chip after \qty{1.5}{\ms} at $v_c =$ \qty{10}{\m\per\min}, $h =$ \qty{40}{\um} and $\lambda_s =$ \qty{0}{\degree}}
+\label{fig:ChipNumTop}
+\end{figure}
+
+Mean values of the experimental forces and their dispersion are shown in Figures \ref{fig:Fx_0} to \ref{fig:Fz_6} together with the mean numerical values.
+Passive force values are of course only plotted for $\lambda_s =$ \qty{6}{\degree} as they are equal to zero when $\lambda_s =$ \qty{0}{\degree}.
+
+\begin{figure}[!h]
 \centering
 \includegraphics[width = 140 mm]{Figures/Fx_0}
-\caption{Comparison of experimental (E) and numerical (N) cutting forces at 0\textdegree{}}\FD{Better explain legend in caption, same for other figures}
-\label{Fx_0}
+\caption{Comparison of experimental (E) and numerical (N) cutting forces at the cutting edge inclination of \qty{0}{\degree} for the 3 uncut chip thicknesses (40, 60 and \qty{40}{\um}) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and \qty{40}{\m\per\min})}
+\label{fig:Fx_0}
 \end{figure}
 
-\begin{figure}[h]
+\begin{figure}[!h]
 \centering
 \includegraphics[width = 140 mm]{Figures/Fx_6}
-\caption{Comparison of experimental (E) and numerical (N) cutting forces at 6\textdegree{}}
-\label{Fx_6}
+\caption{Comparison of experimental (E) and numerical (N) cutting forces at the cutting edge inclination of \qty{6}{\degree} for the 3 uncut chip thicknesses (40, 60 and \qty{80}{\um}) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and \qty{40}{\m\per\min})}
+\label{fig:Fx_6}
 \end{figure}
 
-\begin{figure}[h]
+\begin{figure}[!h]
 \centering
 \includegraphics[width = 140 mm]{Figures/Fy_0}
-\caption{Comparison of experimental (E) and numerical (N) feed forces at 0\textdegree{}}
-\label{Fy_0}
+\caption{Comparison of experimental (E) and numerical (N) feed forces at the cutting edge inclination of \qty{0}{\degree} for the 3 uncut chip thicknesses (40, 60 and \qty{80}{\um}) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and \qty{40}{\m\per\min})}
+\label{fig:Fy_0}
 \end{figure}
 
-\begin{figure}[h]
+\begin{figure}[!h]
 \centering
 \includegraphics[width = 140 mm]{Figures/Fy_6}
-\caption{Comparison of experimental (E) and numerical (N) feed forces at 6\textdegree{}}
-\label{Fy_6}
+\caption{Comparison of experimental (E) and numerical (N) feed forces at the cutting edge inclination of \qty{6}{\degree} for the 3 uncut chip thicknesses (40, 60 and \qty{80}{\um}) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and \qty{40}{\m\per\min})}
+\label{fig:Fy_6}
 \end{figure}
 
-\begin{figure}[h]
+\begin{figure}[!h]
 \centering
 \includegraphics[width = 140 mm]{Figures/Fz_6}
-\caption{Comparison of experimental (E) and numerical (N) passive forces at 6\textdegree{}}
-\label{Fz_6}
+\caption{Comparison of experimental (E) and numerical (N) passive forces at the cutting edge inclination of \qty{6}{\degree} for the 3 uncut chip thicknesses (40, 60 and \qty{80}{\um}) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and \qty{40}{\m\per\min})}
+\label{fig:Fz_6}
 \end{figure}
 
-\begin{figure}[h]
+The increase of the cutting force with the uncut chip thickness is clearly observed in Figures \ref{fig:Fx_0} and \ref{fig:Fx_6} for both experimental and numerical results at the 2 inclination angles, as well as the decrease of the force with the increase in the cutting speed.
+This shows temperature softening domination on strain rate hardening for Ti6Al4V and that it is accurately modelled.
+The increase of the inclination angle from \qty{0}{\degree} to \qty{6}{\degree} slightly reduces the cutting force; this is well captured by the model.
+For cutting speeds of \qtyrange{20}{40}{\m\per\min} and inclination angle of \qty{0}{\degree}, $F_c$ is almost constant with the cutting speed for uncut chip thicknesses of \qty{40}{\um} and \qty{60}{\um}, while it slightly decreases for \qty{80}{\um}; this small stabilization is less marked for the modelling.
+
+An increase in the deviation around the mean value with the cutting speed is noted for values above \qty{10}{\m\per\min}.
+All numerical values are within a confidence interval of 95\% of the experiments (35 out of 36 conditions are within a confidence interval of 68\%).
+The mean difference with the experiments is 4\%, which is remarkable, moreover given the wide range of cutting conditions considered and the absence of tuning of the model.
+This highlights the predictive ability and the accuracy of the FE model for both inclination angles.
+
+Figures \ref{fig:Fy_0} and \ref{fig:Fy_6} show the results for the feed force, where the two clearest trends for the experiments are its decrease with inclination angle and its increase with the uncut chip thickness (even if it is smaller than the expectations).
+For \qty{80}{\um}, $F_f$ globally decreases with $v_c$ in the experiments.
+For \qty{40}{\um} and \qty{60}{\um}, the force decreases at lower $v_c$ and then increases for \qty{0}{\degree}, while a decrease is observed at all $v_c$ for \qty{6}{\degree} (experimental dispersion is high for both inclination angles, but the mean trend with the cutting speed is clear at \qty{6}{\degree}, not at \qty{0}{\degree}).
+For the numerical values, the global trend is the same for the 3 uncut chip thicknesses and both inclination angles: a decrease for the lowest $v_c$ values and then an increase.
+It must be noted that the numerical model does not handle correctly the feed force trends: as clearly shown by Figure \ref{fig:Fy_6}, the numerical forces have globally an increasing trend with the cutting speed, while their mean value mostly decreases when the uncut chip thickness increases.
+Differences between the mean numerical and experimental values increase with the uncut chip thickness: forces are closer at \qty{40}{\um} than at \qty{80}{\um}.
+The numerical values are mostly not within the 95\% confidence interval (it has no clear evolution with the cutting conditions).
+Coupled with the differences in trends, it shows that $F_f$ is less well modelled (mean difference is 39\%) than $F_c$ as usual in FE modelling of the cutting process and even more so in 3D \cite{hardt_Three_2021}.
+The influence of the uncut chip thickness on the feed force should therefore be improved.
+Material constitutive model parameters are known to have an impact on the forces (and on the chip morphology) \cite{ducobu_Importance_2017,kugalurpalanisamy_Identification_2022}.
+The friction model should be improved as well to enhance the results \cite{hardt_Three_2021}.
+
+Passive force is non-zero for the inclination angle of \qty{6}{\degree} (Figure \ref{fig:Fz_6}).
+As the cutting force, it increases with the uncut chip thickness and it decreases with the cutting speed.
+Comparison with the experiments is globally the same as for $F_c$, except for a larger difference in the magnitude of $F_p$ (mean difference is 26\%, but it is small in absolute – less than \qty{5}{N}).
+The numerical values are mostly not in the 95\% experimental confidence interval.
+A lower magnitude of the passive force from the simulation than from the experiments with the right trends when the cutting conditions changed was also observed by Hardt and Bergs \cite{hardt_Three_2021}.
+Differences were mainly attributed to differences in the cutting edge radius, the modelling of friction and the material constitutive model.
+In this work, impact of the cutting edge radius can be neglected as it is the same in the model as in the experiments.
+
+Regarding the chips morphology, all the chips are continuous. For both the simulation and the experiments, the chip thickness ratio, $\lambda_h$:
+%
+\begin{equation}
+\lambda_h = \frac{h'}{h}
+\end{equation}
+%
+with $h$ the uncut chip thickness and $h'$ the chip thickness, is almost independent of the uncut chip thickness (Figures \ref{fig:h0} and \ref{fig:h6}).
+It is slightly reduced from $\lambda_s =$ \qty{0}{\degree} to $\lambda_s =$ \qty{6}{\degree}, meaning that the chip thickness decreases with the inclination angle.
+This influence is underestimated by the model: the reduction of $\lambda_h$ is lower than in the experiments.
+The mean difference between experimental and numerical $\lambda_h$ is 17\% across the whole range of cutting conditions.
+The chip thickness ratio decreases with the cutting speed because of the reduction of friction, which is correctly captured by the model.
+As for the feed force, the results should be improved by more complex friction models and a set of material constitutive parameters for which the identification includes the forces and the chip thickness \cite{kugalurpalanisamy_Identification_2022}.
+
+\begin{figure}[!h]
 \centering
 \includegraphics[width = 140 mm]{Figures/h0}
-\caption{Comparison of experimental (E) and numerical (N) chip thickness ratios at 0\textdegree{}}
-\label{h0}
+\caption{Comparison of experimental (E) and numerical (N) chip thickness ratios at the cutting edge inclination of \qty{0}{\degree} for the 3 uncut chip thicknesses (40, 60 and \qty{80}{\um}) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and \qty{40}{\m\per\min})}
+\label{fig:h0}
 \end{figure}
 
-\begin{figure}[h]
+\begin{figure}[!h]
 \centering
 \includegraphics[width = 140 mm]{Figures/h6}
-\caption{Comparison of experimental (E) and numerical (N) chip thickness ratios at 6\textdegree{}}
-\label{h6}
+\caption{Comparison of experimental (E) and numerical (N) chip thickness ratios at the cutting edge inclination of \qty{6}{\degree} for the 3 uncut chip thicknesses (40, 60 and \qty{80}{\um}) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and \qty{40}{\m\per\min})}
+\label{fig:h6}
 \end{figure}
 
-\hl{+ fig with sim chip and show that it is helical/spiral at 6 deg}
-\hl{+ Chip thickness is globally lower at 6 deg than 0 deg}
-\hl{+ Show side flow, non-uniform chip thickness}
+Differences computed according to equation \ref{eq:diff} are shown in Table \ref{tab:Synth} to provide a quantitative overview of the results.
+The cutting force is the best modelled quantity as observed in the literature.
+This results could be expected as the set of parameters of the constitutive model was selected mainly thanks to its good approximation of the cutting force \cite{ducobu_Importance_2017}.
+As that selection was carried out with a 2D model, the results show the capacity of the model to correctly handle the third (passive) force.
+Based on the mean differences, the performance of the model is very close for the cutting and the feed forces for both cutting edge inclinations, even if a small degradation (1\% and 2\%, respectively) is noted for \qty{6}{\degree}.
+This degradation is larger (7\%) for the chip thickness ratio and should be linked with the difference in the passive force.
+Indeed, the modellings of the chip thickness and of the out-of-plane force are deeply linked.
+Improving the friction at the tool -- workpiece interface should be a key point.
+It must be noted that the chip thickness is very well modelled in some cutting conditions with a minimal difference of \qty{2}{\%}.
+The difference is larger for the feed force than for the passive force, an opposite trend to Hardt and Bergs' \cite{hardt_Three_2021}.
+Both mean and range (min -- max) of differences are larger for the feed force.
+The smaller range of the passive force confirms an offset for all the cutting conditions, similarly to the results of Hardt and Bergs \cite{hardt_Three_2021}.
+Again, the modelling of friction should be the first aspect of the model to improve in future developments.
 
-The increase of the cutting force with the uncut chip thickness is clearly observed in Figure 5 for both experimental and numerical results at the 2 inclination angles, as well as the decrease of the force with the increase in the cutting speed.
-This shows temperature softening domination on strain rate hardening for Ti6Al4V and that it is accurately modelled.
-The increase of the inclination angle from 0\textdegree{} to 6\textdegree{} reduces the cutting force; this is well captured by the model.
-For cutting speeds of 20-40 m/min, $F_c$ is almost constant for 40 \textmu{}m and 60 \textmu{}m, while it slightly decreases for 80 \textmu{}m; this small stabilisation is less marked for the model.
-Increase in the deviation around the mean value with the cutting speed is noted for values above 10 m/min.
-All numerical values are within a confidence interval of 95\% of the experiments (35 out of 36 conditions are within a confidence interval of 68\%) and the mean difference with the experiments is 3\%, which is remarkable, moreover given the wide range of cutting conditions considered.
-This highlights the predictive qualities of the FE model for both inclination angles.
-Figure 6 shows the results for the feed force, where the two clearest trends are its decrease with inclination angle and its increase with the uncut chip thickness for both experimental and numerical results.
-For 80 \textmu{}m, $F_f$ globally decreases with $v_c$ in the experiments.
-For 40 and 60 \textmu{}m, the force decreases at lower $v_c$ and then increases for 0\textdegree{}, while a decrease is observed at all $v_c$ for 6\textdegree{}.
-For the numerical values, the global trend is the same for the 3 uncut chip thicknesses and both inclination angles: a decrease for the lowest $v_c$ values and then an increase.
-The numerical values are mostly not within the 95\% confidence interval (it has no clear evolution with the cutting conditions).
-Coupled with the differences in trends, it shows that $F_f$ is less well modelled (mean difference is 35\%) as usual in FE modelling of the cutting process.
-Improving the friction model should enhance the results.
-Passive force is non-zero for the inclination angle of 6\textdegree{} (Figure 7).
-As the cutting force, it increases with the uncut chip thickness and it decreases with the cutting speed.
-Comparison with the experiments is globally the same as for $F_c$, except for a larger difference in the magnitude of $F_p$ (mean difference is 26\%, but it is small in absolute – less than 5 N).
-The numerical values are mostly not in the 95\% experimental confidence interval.
-Regarding the chips morphology, all of them are continuous.
-For both the simulation and the experiments, the chip thickness ratio, $\lambda_h$, decreases with the cutting speed because of reduction of friction and it is almost independent of the uncut chip thickness.
-The mean difference between experimental and numerical $\lambda_h$ is 13\% across the whole range of cutting conditions.
+%
+\begin{table}[!h]
+\begin{center}
+\caption{\label{tab:Synth} Synthetic quantitative overview of the results: differences between the experimental and the numerical results (mean difference for each cutting edge inclination, and maximal, minimal and mean differences for all the conditions) for the cutting force, $\Delta F_c$, the feed force, $\Delta F_f$, the passive force, $\Delta F_p$, and the chip thickness ratio, $\Delta \lambda_h$}
+\begin{tabular}{lllll}
+\hline\noalign{\smallskip}
+Difference & $\Delta F_c$ (\%) & $\Delta F_f$ (\%) & $\Delta F_p$ (\%) & $\Delta \lambda_h$ (\%)\\
+\hline\noalign{\smallskip}
+Mean $\lambda_s =$ \qty{0}{\degree} & 3 & 38 & -- & 14\\
+Mean $\lambda_s =$ \qty{6}{\degree} & 4 & 40 & 26 & 21\\
+Max global & 10 & 60 & 29 & 38\\
+Min global & 1 & 10 & 19 & 2\\
+Mean global & 4 & 39 & 26 & 17\\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+\end{tabular}
+\end{center}
+\end{table}
+%
 
-\FD{Check clearly stated that Ff trend is globally NOK: improve friction and mat para also cf. Metals Kuga + increase with h quite low in the exp.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In this paper, an experimental study has been carried out in free orthogonal and oblique cutting for Ti6Al4V.
+An experimental and numerical study of the free orthogonal and oblique cutting of Ti6Al4V has been carried out for a wide range of cutting conditions using an ANN-based material constitutive model.
+The following main conclusions are drawn:
+\begin{itemize}
+  \item The experimental study has been carried out with the same setup in free orthogonal and free oblique cutting for the titanium alloy Ti6Al4V (the only change is the cutting edge inclination).
 It is a reference to assess the performances of the 3D FE model introducing an ANN-based constitutive model and developed in the same conditions.
-An unpreviously seen wide range of cutting conditions, 36, is considered, including 2 inclination angles.
-Accurate evaluation of fundamental variables in 3D with the absence of tuning of both numerical parameters and model features when cutting conditions and inclination angle are significantly modified is a strong novelty of this work.
-Only changing the inclination angle to move from free orthogonal to oblique cutting while maintaining the quality of the results has no equivalent in the current literature, moreover as no study on free oblique cutting is available.
-Predictive abilities of the model make it adequate for development of tools with a straight cutting edge, for example.
-
-\hl{this works opens possibilities in both 3D free orthogonal cutting and ANN based material behaviours}
+An unpreviously seen wide range of cutting conditions, 36, is considered, including 2 cutting edge inclinations.
+  \item Accurate evaluation of fundamental variables and their trends in 3D with the absence of tuning of both numerical parameters and model features when cutting conditions and inclination angle are significantly modified is a strong novelty of this work.
+Only changing the inclination angle to move from free orthogonal to oblique cutting while maintaining the quality of the results has no equivalent in the current literature, moreover as no study (experimental or numerical) on free oblique cutting is available.
+  \item \FD{Add one bullet on ANN and the associated future works?}
+  \item The cutting force is the best modelled quantity with a mean difference of \qty{4}{\%} with the experiments.
+The chip thickness ratio and the passive force show a higher deviation with the experiments (17\% and 26\%, respectively), while their trends when the cutting conditions change are accurate.
+This corresponds to the expected results provided by a predictive model.
+The difference for the feed force is higher (39\%), and opposite trends by comparison with the experimental reference are observed.
+The absence of influence of the uncut chip thickness on friction in the model seems to be one of the aspects to include first in future works.
+The model turns out to handle the apparition of the third, out-of-plane, force well with no significant degradation of the results.
+  \item Predictive abilities of the model make it adequate for the development of tools with a straight cutting edge, for example.
+This work moreover demonstrates the ability to model materials' behaviour with ANN and opens possibilities in this promising direction.
+\end{itemize}
 

### 2022-10-07 Article.tex
Update of superscript symbol for temperature dependence in Table 2

@@
 \hline\noalign{\smallskip}
-Young's modulus, $E$ (\unit{\GPa}) & Ti6Al4V & 113.8$^*$\\
+Young's modulus, $E$ (\unit{\GPa}) & Ti6Al4V & 113.8\textsuperscript{\textdagger}\\
  & WC & 650\\
@@
  & WC & \num{14850}\\
-Conductivity, $k$ (\unit{\W\per\metre\per\K}) & Ti6Al4V & 6.3$^*$\\
+Conductivity, $k$ (\unit{\W\per\metre\per\K}) & Ti6Al4V & 6.3\textsuperscript{\textdagger}\\
  & WC & 100\\
-Expansion, $\alpha$ (\unit{\per\K}) & Ti6Al4V & \num{8.6e-6}$^{*}$\\
+Expansion, $\alpha$ (\unit{\per\K}) & Ti6Al4V & \num{8.6e-6}\textsuperscript{\textdagger}\\
  & WC & \num{5e-6}\\
-Specific heat, $c_{p}$ (\unit{\J\per\kg\per\K}) & Ti6Al4V & 531$^*$\\
+Specific heat, $c_{p}$ (\unit{\J\per\kg\per\K}) & Ti6Al4V & 531\textsuperscript{\textdagger}\\
  & WC & 202\\
@@
 \end{center}
-\vspace{-0.4cm}$^*$: Dependence on the temperature, value provided at \qty{293}{\K}
+\vspace{-0.4cm}\textsuperscript{\textdagger}: Dependence on the temperature, value provided at \qty{293}{\K}
 \end{table}

### 2022-10-11 Article.tex
Update of the Publication by O.Pantalé

@@
 \DeclareMathOperator{\sigmoid}{sig}
-\newcommand{\lay}[1]{^{(#1)}}
+%\newcommand{\lay}[1]{^{(#1)}}
 \newcommand{\dotp}{\boldsymbol{\cdot}}
 \newcommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
-\newcommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
+\newcommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}} % for a bigger dot
+\newcommand{\ccirc}{\kern0.5ex\vcenter{\hbox{$\scriptstyle\circ$}}\kern0.5ex}
 
@@
 Modelling of the cutting process needs to move from 2D to 3D configurations to get closer to industrial applications.
-This study introduces a predictive 3D finite element model of free orthogonal and oblique cutting with an ANN-based material constitutive model and experimental validation in strictly the same conditions (cutting and geometrical).
+This study introduces a predictive 3D finite element model of free orthogonal and oblique cutting with an ANN-based material flow law and experimental validation in strictly the same conditions (cutting and geometrical).
+The flow law based on a neural network allows simulating the cutting process based on data coming from the material characterization tests without requiring any postulate concerning the expression of the flow law.
 The developments are applied to the formation of continuous chips for the titanium alloy Ti6Al4V and an unseen broad range of 36 cutting conditions is considered: 2 cutting edge inclinations, 3 uncut chip thicknesses and 6 cutting speeds.
 The predictive performance of the model (i.e., the evaluation of the trends of fundamental variables with the absence of tuning of both numerical parameters and model features when cutting conditions are significantly modified) is high for the forces, mainly cutting and passive, and the chip thickness ratio on all 36 cutting conditions.
-The accuracy of the main cutting force is excellent: the mean difference with the experiments is 4\%, within the experimental dispersion.
+The accuracy of the main cutting force is excellent: the mean difference with the experiments is \qty{4}{\%}, within the experimental dispersion.
 No significant degradation of the results is brought by the apparition of the third, out-of-plane, force, which shows the ability of the model to handle orthogonal and oblique cutting configurations.
@@
 \FD{Add a comment on ANN?}
+\OP{A new sentence has been introduced in the abstract}
 
@@
 
-Selection of the tools and the cutting conditions in machining, but also comprehension of the influence of the process parameters on the quality of a component and its optimization, are still difficult to achieve because of the high level of complexity and linked nonlinear phenomena.
+Selection of the tools and the cutting conditions in machining, but also comprehension of the influence of the process parameters on the quality of a component and its optimization, are still difficult to achieve because of the high level of complexity and the related nonlinear phenomena.
 In the frame of digital manufacturing and Industry 4.0, modelling the cutting process supports them, while remaining a challenging task.
@@
 
-Experimental validation of a model is a crucial step in the modelling of the cutting process.
-The experimental configuration must be as close as possible to the simulation.
-For orthogonal cutting validation, a rotating movement usually generates the cutting speed.
-This is often achieved in turning \cite{agmell_Development_2018} or in milling \cite{xu_Simulation_2021} and the diameter of the rotating part must be large enough to reduce the influence of the curvature on the results.
-Experimental configurations in strictly orthogonal cutting conditions are less often adopted, for example, on broaching \cite{abouridouane_Friction_2021} or milling \cite{ducobu_Experimental_2015, sela_Measurement_2021} machines.
-While they remove assumptions linked to the rotating cutting movement, they usually allow for lower cutting speeds (except on a dedicated machine, such as in Afrasiabi et al.
+Experimental validation of a model is a crucial step in modelling the cutting process.
+The experimental configuration should be as close as possible to the simulation.
+For the validation of orthogonal cutting, a rotational motion usually generates the cutting speed.
+This is often done in turning \cite{agmell_Development_2018} or milling \cite{xu_Simulation_2021} and the diameter of the rotating workpiece must be large enough to reduce the influence of curvature on the results.
+Experimental configurations under strictly orthogonal cutting conditions are less often adopted, for example on broaching machines \cite{abouridouane_Friction_2021} or milling machines \cite{ducobu_Experimental_2015, sela_Measurement_2021}.
+If they remove the assumptions related to the rotary cutting motion, they generally allow lower cutting speeds (except on a dedicated machine, as in Afrasiabi et al.
 \cite{afrasiabi_NumericalExperimental_2021}).
-Free oblique cutting with a straight cutting edge has not been studied yet: all the efforts have been focussing on orthogonal cutting (mostly for 2D validation).
+Free oblique cutting with a straight cutting edge has not yet been studied: all efforts have been concentrated on orthogonal cutting (mainly for 2D validation).
 
 Lagrangian and Eulerian formulations are the most used for FE modelling of the cutting process.
-Combinations of formulations, such as Arbitrary Lagrangian-Eulerian (ALE) and Coupled Eulerian-Lagrangian (CEL) are increasingly used to avoid (or reduce) mesh distortions \cite{ducobu_Application_2016}.
-The Coupled Eulerian-Lagrangian (CEL) formulation has recently been successfully applied to the modelling of cutting (2D orthogonal configuration): it provides accurate results with a realistic chip shape and no mesh distortion \cite{ducobu_Application_2016}.
-First applications in 3D are found in recent works \cite{xu_Simulation_2021, ducobu_Finite_2017, ambrosio_New_2022, vovk_Finite_2020, hardt_Three_2021}.
-They cover (free) orthogonal cutting or a simple 3D operation, while free oblique cutting still needs to be investigated.
+Combinations of formulations, such as Arbitrary Lagrangian-Eulerian (ALE) and Coupled Eulerian-Lagrangian (CEL), are increasingly being used to avoid (or reduce) mesh distortions \cite{ducobu_Application_2016}.
+The Coupled Eulerian-Lagrangian (CEL) formulation has recently been successfully applied to the modelling of cutting (2D orthogonal configuration): it provides accurate results with realistic chip shape and no mesh distortion.
+The first 3D applications are found in recent works \cite{xu_Simulation_2021, ducobu_Finite_2017, ambrosio_New_2022, vovk_Finite_2020, hardt_Three_2021}.
+They cover orthogonal (free) cutting or a simple 3D operation, while free oblique cutting has yet to be studied.
 
 The behaviour of the machined material is one of the key aspects of a FE model \cite{arrazola_Recent_2013, melkote_Advances_2017}.
-Research is very intense in this field, which leads to a growing number of material constitutive models ranging from empirical to physical models, some including microstructure effects \cite{melkote_Advances_2017}.
-The thermo-elasto-viscoplastic empirical model of Johnson-Cook (JC) \cite{johnson_Constitutive_1983} is still the most used so far:
+Research is very intense in this area, leading to a growing number of constitutive material models ranging from empirical models to physical models, some including microstructure effects \cite{melkote_Advances_2017}.
+The empirical thermo-elasto-viscoplastic Johnson-Cook (JC) model \cite{johnson_Constitutive_1983} is still the most widely used to this day:
 %
 \begin{equation}\label{eq:J-C}
-	\sigma^{y} = \left(A + B\ \varepsilon^{p^n} \right) \left(1 + C\ \ln\frac{{\dot{\varepsilon}}^p}{\dot{\varepsilon}_{0}^{p}}\right) \left(1 - \left[\frac{T - T_{\text{room}}}{T_{\text{melt}} - T_{\text{room}}}\right]^{m}\right)
+	\sigma^y = \left(A + B\ \varepsilon^{p^n} \right) \left(1 + C\ \ln\frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0^p}\right) \left(1 - \left[\frac{T - T_{\text{room}}}{T_{\text{melt}} - T_{\text{room}}}\right]^{m}\right)
 \end{equation}
 %
-In this model, the flow stress, $\sigma^{y}$, is a function of the plastic strain, $\varepsilon^{p}$, of the plastic strain rate, ${\dot{\varepsilon}}^{p}$, and of the temperature, $T$.
-It is composed of 3 terms describing independently plastic, viscous and thermal aspects.
+In this model, the flow stress, $\sigma^y$, is a function of the plastic strain, $\varepsilon^p$, the plastic strain rate, $\mdot{\varepsilon}^p$, and the temperature, $T$.
+It is composed of 3 terms describing independently the plastic, viscous and thermal aspects.
 One of the points in favour of its adoption is the rather limited number of parameters to be identified, 5: $A$, $B$, $C$, $m$ and $n$.
-$\dot{\varepsilon}_{0}^{p}$ is the reference plastic strain rate, while $T_{\text{room}}$ and $T_{\text{melt}}$ are the room temperature and the melting temperature, respectively.
-More recent models developed based on it, such as the one of Calamaz et al.
-\cite{calamaz_New_2008}, increase this number of parameters (for Calamaz's particular model to 9).
-The better (in theory) description of the behaviour is achieved at the cost of a greater complexity of the identification process and of a reduction of the link with the physical meaning of the model.
+$\mdot{\varepsilon}_0^p$ is the reference plastic strain rate, while $T_{\text{room}}$ and $T_{\text{melt}}$ are respectively the ambient (room) and melting temperature.
+More recent models developed on this basis, such as that of Calamaz et al.
+\cite{calamaz_New_2008}, increase this number of parameters (for the particular Calamaz model to 9).
+Other authors have also used Zerilli-Armstrong model to simulate cutting processes \cite{Muralli-2017-Performance}.
+The best description (in theory) of the behaviour is obtained at the cost of a greater complexity of the identification process and a reduction of the link with the physical meaning of the model.
 
-One issue of material behaviour modelling for cutting simulation is the identification of the parameters, moreover, as the experimental equipment does not allow to reach the high levels of strains, strain rates and temperature of machining \cite{melkote_Advances_2017}.
+One of the problems of modelling material behaviour for cutting simulation is the identification of parameters, especially as the experimental equipment does not allow the high levels of strain, strain rate and temperature of machining to be achieved \cite{melkote_Advances_2017}.
 Inverse identification is an alternative, but the uniqueness of the solution is not always guaranteed \cite{arrazola_Recent_2013, melkote_Advances_2017}.
-The early work of Özel and Altan \cite{ozel_Determination_2000} used the least squares method to inversely identify the input parameters of a FE model.
-Shrot and Bäker \cite{shrot_Determination_2012} then used the Levenberg–Marquardt algorithm for their identification of the constitutive material parameters.
-They showed that similar results (cutting forces and chip morphology) could be obtained by different sets of parameters and therefore highlighted the non-uniqueness of the solution of the inverse problem.
+Early work by Özel and Altan \cite{ozel_Determination_2000} used the least squares method to identify the input parameters of a FE model in an inverse manner.
+Shrot and Bäker \cite{shrot_Determination_2012} then used the Levenberg-Marquardt algorithm for their identification of the material parameters.
+They showed that similar results (cutting forces and chip morphology) could be obtained by different sets of parameters and thus highlighted the non-uniqueness of the solution of the inverse problem.
 In addition to the flow stress parameters, Klocke et al.
 \cite{klocke_Orthogonal_2013} also identified the damage parameters.
-In more recent works, such as Bosetti et al.
+In more recent work, such as Bosetti et al.
 \cite{bosetti_Identification_2013} and Denkena et al.
-\cite{denkena_Inverse_2015}, the approach to tackle the inverse identification problem is moving from optimization to Artificial Intelligence (AI) based methods.
+\cite{denkena_Inverse_2015}, the approach to the inverse identification problem is shifting from optimization to Artificial Intelligence (AI) based methods.
 The Downhill Simplex Algorithm (DSA) is adopted by Bergs et al.
@@
 Stampfer et al.
-\cite{stampfer_Material_2021} also selected the DSA when dealing with AISI~4140 tempered at 3 different temperatures.
+\cite{stampfer_Material_2021} also chose DSA when treating AISI~4140 quenched at 3 different temperatures.
 In \cite{hardt_Application_2021}, Hardt et al.
-showed that the Particle Swarm Optimization (PSO) was more efficient to solve the inverse problem than the DSA, even if computation time is still significant.
-In an effort to reduce it, an Efficient Global Optimization (EGO) algorithm has recently been introduced by Kugalur Palanisamy et al.
+showed that Particle Swarm Optimization (PSO) was more efficient in solving the inverse problem than DSA, even though the computational time is still significant.
+In order to reduce the computational time, an Efficient Global Optimization algorithm (EGO) was recently introduced by Kugalur Palanisamy et al.
 \cite{kugalurpalanisamy_Identification_2022}.
-They simultaneously identified the parameters of the material constitutive model and of the friction model for Ti6Al4V.
+They identified simultaneously the parameters of the material constitutive model and the friction model for Ti6Al4V.
 Most of these works highlight the non-uniqueness of the identification and they all require the definition of the analytical expression of the constitutive model.
 
-This paper fills the literature gap on oblique cutting by investigating free orthogonal and oblique 3D cutting configurations from both the experimental and the numerical points of view.
-An Artificial Neural Network (ANN), introduced in Pantalé et al.
-\cite{pantale_Efficient_2022}, is implemented in a FE cutting model for the first time instead of the analytical JC law.
-A broad range of cutting speeds (6), uncut chip thicknesses (3) and cutting edge inclination angles (2) resulting in 36 different conditions is considered to demonstrate the predictive ability of the FE model for fundamental variables.
-The main goals of a predictive model are the accurate modelling of the trends of the results when the conditions change and the good agreement of the predicted values with the experimental ones (exact values are not looked for due to experimental dispersions).
-This type of models aims at supporting future choices and developments without the need for experimental data.
-No assumption is made about the geometry of the machined workpiece in the model (i.e., its width is the same as in the experiments), while keeping computation time relevant for industrial applications.
-The developments are applied to the formation of continuous chips of titanium alloy Ti6Al4V.
+This paper fills the gap in the oblique cutting literature by investigating both orthogonal and free oblique 3D cutting configurations, both experimentally and numerically.
+An artificial neural network (ANN), introduced in Pantalé et al.
+\cite{pantale_Efficient_2022}, is implemented in a FE cutting model for the first time in place of the JC analytical law.
+A wide range of cutting speeds (6), uncut chip thicknesses (3) and cutting edge inclination angles (2) resulting in 36 different conditions are considered to demonstrate the predictive capability of the FE model for the fundamental variables.
+The main objectives of a predictive model are the accurate modelling of trends in results as conditions change and the good agreement of predicted values with experimental values (exact values are not sought due to experimental dispersions).
+This type of model is intended to support future choices and developments without the need for experimental data.
+No assumptions are made about the geometry of the workpiece in the model (i.e.
+its width is the same as in experiments), while keeping the calculation time relevant for industrial applications.
+The developments are applied to the formation of continuous chips of the titanium alloy Ti6Al4V.
 
@@
 
-A 3-axis GF Mikron VCE 600 Pro milling machine is used to carry out dry free orthogonal and oblique cutting tests on Ti6Al4V (grade 5 annealed at \qty{750}{\degreeCelsius} for \qty{1}{\hour} followed by air cooling) with the same kinematics as a shaper.
+A 3-axis GF Mikron VCE 600 Pro milling machine is used to perform dry orthogonal and oblique cutting tests on Ti6Al4V (grade 5 annealed at \qty{750}{\degreeCelsius} for \qty{1}{\hour} followed by air cooling) with the same kinematics as a shaper.
 As shown in Figure \ref{fig:ExpSetup}, the tungsten carbide tool (modified LCGN160602-0600-FG, CP500 from SECO) is fixed on a dedicated holder (modified CFHN-06 from SECO) and the sample to be cut is clamped in the spindle (no rotation is allowed during the test).
-The top of the sample includes 3 ribs of \qty{1}{\mm} in width (the width of the tool is \qty{6}{\mm}) and \qty{10}{\mm} in length.
-The test consists of removing the upper layer (its height is the uncut chip thickness, $h$) of one rib at the prescribed cutting speed, $v_c$.
-The cutting speed is provided by the feed rate, $v_f$, of the machine (max.
-value of \qty{40}{\metre\per\min}).
-The tool cutting edge inclination, $\lambda_s$, results from the relative angular orientation of the tool and the sample.
-Table \ref{tab:CutCond} shows the cutting conditions: 6 cutting speeds, 3 uncut chip thicknesses and 2 inclination angles, each is repeated 3 times.
+The top of the sample has 3 ribs of \qty{1}{\mm} width (the width of the tool is \qty{6}{\mm}) and \qty{10}{\mm} length.
+The test consists of removing the top layer (its height is the thickness of the uncut chip, $h$) of a rib at the prescribed cutting speed, $v_c$.
+The cutting speed is provided by the feed rate, $v_f$, of the machine (maximum value of \qty{40}{\metre\per\min}).
+The inclination of the cutting edge of the tool, $\lambda_s$, results from the relative angular orientation of the tool and the sample.
+Table \ref{tab:CutCond} shows the cutting conditions: 6 cutting speeds, 3 uncut chip thicknesses and 2 inclination angles, each repeated 3 times.
 
@@
 Forces are measured with a 3-component Kistler 9257B dynamometer and are amplified by a Kistler 5070A charge amplifier.
-The acquisition is performed at \qty{3}{\kHz} with a Kistler 5697A2 data acquisition system and the DynoWare software.
-Recorded forces are then filtered with a second-order low-pass Bessel filter at \qty{750}{\Hz} before computing the mean value of the signal at the steady state.
+Acquisition is performed at \qty{3}{\kHz} using a Kistler 5697A2 data acquisition system and DynoWare software.
+The recorded forces are then filtered with a second-order low-pass Bessel filter at \qty{750}{\Hz} before calculating the mean value of the steady state signal.
 
-All the chips are collected and observed with a Dino Lite digital microscope AM7013MZT (5~MP, magnification $20\times$ -- $250\times$).
-Each chip is measured 3 times along its length to get a mean value representative of the whole chip.
+All chips are collected and observed with a Dino Lite digital microscope AM7013MZT (5~MP, magnification $20\times$ -- $250\times$).
+Each chip is measured 3 times along its length in order to obtain an average value representative of the whole chip.
 
@@
 
-The CEL formulation is adopted to model the dry free orthogonal and oblique cutting tests with Abaqus/Explicit 2020.
-The 3D model is composed of a fixed Lagrangian tool and a Eulerian workpiece (Figure \ref{fig:BC}).
-Chip formation occurs by plastic flow across the Eulerian domain with no mesh distortion.
-The Eulerian formulation enables to form chips without damage properties, removing modelling assumptions.
-These two characteristics contribute to cutting models providing accurate results and realistic chips \cite{ducobu_Application_2016}.
+The CEL formulation is adopted to model the dry orthogonal and oblique cutting tests with Abaqus/Explicit 2020.
+The 3D model is composed of a fixed Lagrangian tool and an Eulerian part (Figure \ref{fig:BC}).
+Chip formation occurs by plastic flow through the Eulerian domain without mesh distortion.
+The Eulerian formulation allows for chip formation without damage properties, by removing modelling assumptions.
+These two features contribute to the cutting models providing accurate results and realistic chips \cite{ducobu_Application_2016}.
 
@@
 
-As shown in Figure \ref{fig:FEConfig}, the full width of the workpiece (\qty{1}{\mm}), i.e., a rib in the experiments, is modelled.
-To allow chip formation and side flow, the Eulerian domain is wider (it includes the volume in which material can move).
-The volume above the initial workpiece is also meshed with Eulerian elements for the same reasons.
-As in the experiments and to fulfil the hypothesis of free orthogonal and oblique cutting, the tool is wider than the workpiece (it is \qty{1.1}{\mm} in the model and \qty{6}{\mm} in the experiments).
-It is very important to stress that the models are the same for both inclination angles: they only differ by the rotation of the tool of \qty{6}{\degree} about Y axis as in the experiments (Figure \ref{fig:FEConfig}).
-This, coupled with the absence of assumptions when developing the models, contributes to make the models predictive: no input is changed when cutting conditions do.
+As shown in Figure \ref{fig:FEConfig}, the full width of the workpiece (\qty{1}{\mm}), i.e.
+one rib in the experiments, is modelled.
+To allow for chip formation and lateral flow, the Eulerian domain is wider (it includes the volume in which the material can move).
+The volume above the initial part is also meshed with Eulerian elements for the same reasons.
+As in the experiments and to satisfy the assumption of an orthogonal and oblique free cut, the tool is wider than the workpiece (it is \qty{1.1}{\mm} in the model and \qty{6}{\mm} in the experiments).
+It is very important to note that the models are the same for both inclination angles: they differ only in the rotation of the tool by \qty{6}{\degree} around the Y axis as in the experiments (Figure \ref{fig:FEConfig}).
+This, together with the absence of assumptions when developing the models, contributes to make the models predictive: no input is changed when the cutting conditions are changed.
 
@@
 
-According to a previous mesh sensitivity study in orthogonal cutting with the CEL formulation \cite{ducobu_Finite_2017}, elements edge size is \qty{5}{\um} in the plane parallel to the cutting speed.
-In the direction perpendicular to this plane, it is \qty{5}{\um} in areas close to the lateral boundaries of the Eulerian domain and \qty{50}{\um} in the middle of the workpiece.
-To reduce computation time, the size of the model depends on the value of the uncut chip thickness.
-This results in a Eulerian domain (EC3D8RT linear 3D Eulerian elements with 8 nodes, coupled mechanical-thermal behaviour and reduced integration) composed of \num{216550} to \num{273350} nodes and a Lagrangian domain (C3D8T linear 3D Lagrangian elements with 8 nodes, coupled mechanical-thermal behaviour) of \num{4650} nodes.
+According to a previous sensitivity study of the mesh in orthogonal section with the CEL formulation \cite{ducobu_Finite_2017}, the edge size of the elements is \qty{5}{\um} in the plane parallel to the cutting velocity.
+In the direction perpendicular to this plane, it is \qty{5}{\um} in the areas close to the lateral limits of the Eulerian domain and \qty{50}{\um} in the middle of the part.
+To reduce the computation time, the size of the model depends on the value of the uncut chip thickness.
+This results in an Eulerian domain (EC3D8RT 8-node 3D linear Eulerian elements, coupled mechanical-thermal behaviour and reduced integration) composed of \num{216550} to \num{273350} nodes and a Lagrangian domain (C3D8T 8-node 3D linear Lagrangian elements, coupled mechanical-thermal behaviour) of \num{4650} nodes.
 
-The Ti6Al4V workpiece is assumed to be thermo-elasto-viscoplastic (isotropic) and the inelastic heat fraction is 0.9.
-JC set of parameters from Seo et al.
-\cite{seo_Constitutive_2005} is adopted as the value of $A$ corresponds to the typical yield stress value of Ti6Al4V and this set proved to provide the best results among 20 sets available in the literature \cite{ducobu_Importance_2017}.
-The tungsten carbide tool with TiN coating is assumed to be linear elastic.
-Material properties are provided in Table \ref{tab:prop}.
+The Ti6Al4V part is assumed to be thermo-elasto-viscoplastic (isotropic) and the inelastic thermal fraction is 0.9.
+The JC parameter set of Seo et al.
+\cite{seo_Constitutive_2005} is adopted because the value of $A$ corresponds to the value of the typical yield strength of Ti6Al4V and this set was found to provide the best results among the 20 sets available in the literature \cite{ducobu_Importance_2017}.
+The TiN coated tungsten carbide tool is assumed to have linear elasticity.
+The material properties are given in Table \ref{tab:prop}.
 
@@
  & $n$ & 0.45\\
- & $\dot{\varepsilon}_{0}$ (\unit{\per\s}) & 1\\
+ & $\mdot{\varepsilon}_0$ (\unit{\per\s}) & 1\\
  & $T_{\text{room}}$ (\unit{\K}) & 293\\
@@
 
-Following the experimental results of Rech et al.
-\cite{rech_Characterisation_2013}, Coulomb's friction is assumed to occur at the tool-workpiece interface and both friction, $\mu$, and heat partition, $\beta$, coefficients depend on the cutting speed.
-Limiting shear stress, $\tau_{\text{max}}$, is included and is given by
-%
+According to the experimental results of Rech et al.
+\cite{rech_Characterisation_2013}, it is assumed that Coulomb friction occurs at the tool-piece interface and that the coefficients of friction, $\mu$, and heat sharing, $\beta$, depend on the cutting speed.
+The limiting shear stress, $\tau_{\text{max}}$, is included and is given by:
+
 \begin{equation}
@@
 \end{equation}
-%
+
 All the friction energy is converted into heat. Table \ref{tab:fricHeat} shows the friction coefficients adopted in this study.
-%
+
 \begin{table}[!h]
@@
 
-A room temperature of \qty{293}{\K} is imposed on the upper and right surfaces of the tool and on the left and bottom surfaces of the workpiece (Figure \ref{fig:BC}).
-Radiation and convection are assumed to occur on the rake and clearance faces of the tool.
-The initial temperature of the tool and the workpiece is set to room temperature (\qty{293}{\K}).
-Heat transfer coefficients are provided in Table \ref{tab:fricHeat}.
+An ambient temperature of \qty{293}{\K} is imposed on the top and right surfaces of the tool and on the left and bottom surfaces of the workpiece (Figure \ref{fig:BC}).
+It is assumed that radiation and convection occur on the rake and clearance faces of the tool.
+The initial temperature of the tool and workpiece is set to the room temperature (\qty{293}{\K}).
+The heat transfer coefficients are provided in Table \ref{tab:fricHeat}.
 
 \subsection{Material constitutive model of Ti6Al4V}
+\OP{This section has been enhanced and completed}
 
-The constitutive model of the Ti6Al4V material used in all the numerical simulations proposed in section \ref{sec:ExpNumResults} is a thermo-elasto-viscoplastic law using a flow criterion based on an ANN identified for the selected material and implemented in the Abaqus/Explicit code via a Fortran routine VUHARD as proposed by Pantalé et al.
+The constitutive model of the Ti6Al4V material used in all the numerical simulations proposed in the section \ref{sec:ExpNumResults} is a thermo-elasto-viscoplastic law using a flow criterion based on an Artificial Neural Network (ANN) identified for the chosen material and implemented in the Abaqus/Explicit code via a Fortran subroutine VUHARD as proposed by Pantalé et al.
 in \cite{pantale_Efficient_2022}.
-The principle of this approach consists in replacing the analytical formulation of the flow law, based on a Johnson-Cook or Zerilli-Armstrong type model, and allowing the calculation of the flow stress $\sigma^y$ as a function of the plastic strain $\varepsilon^p$, of the plastic strain rate, ${\dot{\varepsilon}}^p$, and of the temperature $T$, by a multi-layer ANN serving as a universal approximator.
-Thus, the parameters of the neural network can directly be identified from the experimental data without having to postulate a behavioural model, which simplifies the procedure and allows more flexibility in the definition of the model.
+The principle of this approach consists in replacing the analytical formulation of the flow law, based on a Johnson-Cook or Zerilli-Armstrong type model, and allowing the calculation of the flow stress $\sigma^y$ as a function of the plastic strain $\varepsilon^p$, the plastic strain rate, $\mdot{\varepsilon}^p$, and the temperature $T$, by a multi-layer ANN serving as universal approximator.
+Thus, the parameters of the neural network can be directly identified from the experimental data without having to postulate a behavioural model, which simplifies the procedure and allows greater flexibility in the definition of the model.
 The proposed approach also allows, as shown in Pantalé et al.
-\cite{pantale_Efficient_2022}, to compute the derivatives of the flow stress $\sigma^y$ with respect to the three input variables of the model, a necessary step to implement this model as a flow law in the form of a VUHARD subroutine in the Abaqus/Explicit FEM code.
+\cite{pantale_Efficient_2022}, to compute the three derivatives of the flow stress $\sigma^y$ with respect to the three input variables of the model, a necessary step to implement this model as a flow law in the form of a VUHARD subroutine in the FEM code Abaqus/Explicit, using the exact same network architecture and identified trained parameters as the one used to compute the flow stress $\sigma^y$.
 
-In order to verify the influence of the complexity of the neural network on the numerical results of the simulation and on the computing time, several architectures of ANN are tested thereafter (in \ref{subsec:nberneu}).
-The chosen global architecture has 2 hidden layers with a variable number of neurons for the first hidden layer ($\zeta$ = 9 to 17) and 7 neurons for the second hidden layer, 3 inputs (plastic strain, $\varepsilon^p$, plastic strain rate, ${\dot{\varepsilon}}^p$, and temperature, $T$) and one output (the yield stress, $\sigma^y$).
-The global architecture of this kind of ANN is given in Figure \ref{fig:ANN} for 9 neurons in the first hidden layer.
-Conforming to Pantalé et al.
-\cite{pantale_Efficient_2022}, this ANN is referred to after the terminology ANN 3-9-7-1-sig, because it has 3 inputs, 9 neurons in the first hidden layer, 7 neurons in the second hidden layer, 1 output and a sigmoid activation function.
+In order to verify the influence of the neural network complexity on the numerical results of the simulation and on the computation time, several ANN architectures are tested afterwards (in \ref{subsec:nberneu}).
+The chosen global architecture has 2 hidden layers with a variable number of neurons for the first hidden layer ($\zeta$ = 9 to 17) and 7 neurons for the second hidden layer, 3 inputs (the plastic strain, $\varepsilon^p$, the plastic strain rate, $\mdot{\varepsilon}^p$, and the temperature, $T$) and one output (the yield strength, $\sigma^y$).
+The global architecture of this type of ANN is given in Figure \ref{fig:ANN} for 9 neurons in the first hidden layer.
+According to Pantalé et al.
+\cite{pantale_Efficient_2022}, this ANN is referred to as ANN 3-9-7-1-sig, as it has 3 inputs, 9 neurons in the first hidden layer, 7 neurons in the second hidden layer, 1 output and a sigmoid activation function.
 
@@
 
-The main advantage of this approach (the use of an ANN), after the training phase, is that the output $\sigma^y$ of the network is related to the inputs $\varepsilon^p$, ${\dot{\varepsilon}}^p$, and $T$ through equations (\ref{eq:ANN-preprocess}) to (\ref{eq:ANN-vonMises}).
+In a preliminary phase, after having selected the global architecture of the neural network, it is necessary to proceed to its training from experimental data resulting from tests on a Gleeble-type thermomechanical simulator.
+These experimental data, presented in the form of a data table containing the plastic strain $\varepsilon^p$, the plastic strain rate $\mdot{\varepsilon}^p$, the temperature $T$ and the flow stress $\sigma^y$, are processed by a learning algorithm, developed at LGP, in Python, using the Tensorflow library.
+Generally, one to two hours of training on a Dell XPS13 7390 laptop running Ubuntu 20.04 64~bits with 16~GiB of Ram and an Intel 4-core i7-10510U processor allow obtaining a model with a sufficient convergence for the application.
+
+Once this learning phase is completed, the neural network parameters resulting from the learning process are used directly by a Python program, in charge of automatically generating the Fortran source code of the VUHARD subroutine in order to compute the flow stress $\sigma^y$ and its three derivatives, required for the explicit Abaqus FEM code.
+
+The main advantage of this approach (the use of an ANN), after the learning phase, is that, for example, the output $\sigma^y$ of the network is now linked to the inputs $\varepsilon^p$, $\mdot{\varepsilon}^p$, and $T$ by the equations (\ref{eq:ANN-preprocess}) to (\ref{eq:ANN-vonMises}) for a two hidden layers neural network with a sigmoid activation function as presented previously.
+
+Thus, in the VUHARD subroutine, the computation of the flow constraint $\sigma^y$ from the 3 input variables $\varepsilon^p$, $\mdot{\varepsilon}^p$, and $T$ is performed using the following procedure.
 The first step is to scale the input data to the interval $[0,1]$ using the following equation:
@@
 \end{equation}
-
-The outputs of the neurons in the first hidden layer are given by the following equation:
-
+where quantities $[\ ]_{min}$ and $[\ ]_{max}$  are the boundaries of the range of the corresponding field during the training phase.
+Corresponding values, for the proposed case, are given in \ref{sec:appendix-1}.
+According to the architecture of the network, the outputs of the neurons of the first hidden layer $\overrightarrow{y_1}$ are given by the following equation:
 \begin{equation}
@@
 \end{equation}
-where, $\sigmoid()$ is the sigmoid activation function defined by equation (\ref{eq:sigmoid}):
+where, $\w_1$ and $\overrightarrow{b_1}$ are the weights and biases associated with the first hidden layer and $\sigmoid()$ is the sigmoid activation function defined by the equation (\ref{eq:sigmoid}) :
 \begin{equation}
@@
 
-Then, the output of the neurons in the second hidden layer are given by equation (\ref{eq:ANN-y2}):
+Then, the output of the neurons of the second hidden layer is given by the equation (\ref{eq:ANN-y2}) :
 \begin{equation}
@@
 \end{equation}
-
-So, the output of the ANN is therefore given by equation (\ref{eq:ANN-vonMises}).
+where, $\w_2$ and $\overrightarrow{b_2}$ are the weights and biases associated with the second hidden layer.
+Finally, the $\sigma^y$ output of the ANN is thus given by the equation (\ref{eq:ANN-vonMises}) :
 \begin{equation}
@@
 \end{equation}
+where, $\overrightarrow{w}$ and $b$ are the weights and bias associated with the output layer.
 
-In equations (\ref{eq:ANN-preprocess}) to (\ref{eq:ANN-vonMises}), quantities $\w_1$, $\w_2$, $\overrightarrow{w}$, $\overrightarrow{b_1}$, $\overrightarrow{b_2}$ and $b$ are given by the training procedure of the ANN.
-Corresponding values for an ANN containing 9 neurons in the first hidden layer are reported in \ref{sec:appendix-1}.
-Quantities $[\ ]_{min}$ and $[\ ]_{max}$  are the boundaries of the range of the corresponding field during the training phase, values are also given in \ref{sec:appendix-1}.
+On the other hand, the three derivatives of the yield stress $\sigma^y$ with respect to the three input variables $\varepsilon^p$, $\mdot{\varepsilon}^p$, and $T$ are given by the following equations:
+\begin{equation}
+\begin{cases}
+\partial \sigma^y/\partial \varepsilon^p = s'_1 \frac{[\sigma^y]_{max} -[\sigma^y]_{min}}{[\varepsilon^p]_{max} -[\varepsilon^p]_{min}}\\
+\partial \sigma^y/\partial\mdot{\varepsilon}^p = s'_2 \frac{[\sigma^y]_{max} -[\sigma^y]_{min}}{\left[[\mdot{\varepsilon}^p]_{max} -[\mdot{\varepsilon}^p]_{min}\right]\mdot{\varepsilon}^p}\\
+\partial \sigma^y/\partial T = s'_3 \frac{[\sigma^y]_{max} -[\sigma^y]_{min}}{[T]_{max} -[T]_{min}}
+\end{cases}\label{eq:derivatives-ANN}
+\end{equation}
 
-Because of the large number of identified parameters for all the ANN models (from 114 to 202 for 9 and 17 neurons for the first hidden layer, respectively), the other 4 sets of ANN parameters used in this publication can be found in \cite{pantale_Coefficients_2022}.\FD{Inclure dans corps du texte puisque article normal et rq reviewer?}
+where $s'_i$ is the $i^{th}$ component of the vector $\overrightarrow{s}'$ defined by the following equation:
+\begin{equation}
+\overrightarrow{s}' =\w_1^T \dotp \left[\w_2^T \dotp \left( 
+\frac{\overrightarrow{w} \ccirc \e{-\overrightarrow{y_2}}}
+{\left[1 + \e{-\overrightarrow{y_2}}\right]^2}\right)\ccirc \left(\frac{
+\e{-\overrightarrow{y_1}}}
+{\left[1 + \e{-\overrightarrow{y_1}}\right]^2}
+\right)\right]\label{eq:der-2-sig}
+\end{equation}
+and $\ccirc$ is the elements-wise product, known as the Hadamard product.
+In equations (\ref{eq:ANN-preprocess}) to (\ref{eq:der-2-sig}), quantities $\w_1$, $\w_2$, $\overrightarrow{w}$, $\overrightarrow{b_1}$, $\overrightarrow{b_2}$ and $b$ are evaluated by the training procedure of the ANN.
+Corresponding values for an ANN containing 9 neurons in the first hidden layer and 7 neurons in the second hidden layer are reported in \ref{sec:appendix-1}.
+The set of equations (\ref{eq:ANN-preprocess}) to (\ref{eq:der-2-sig}), together with the network parameters identified in the learning phase, is automatically translated into a VUHARD Fortran subroutine used by the FEM code Abaqus to simulate the cutting model.
+
+Because of the large number of identified parameters for all the ANN models (from 114 to 202 for 9 and 17 neurons for the first hidden layer, respectively), the other 4 sets of ANN parameters used in this publication can be found in \cite{pantale_Coefficients_2022}.
+
+\FD{Inclure dans corps du texte puisque article normal et rq reviewer?}
+
+\OP{I think it should still be enough as we put a complete set in the appendix, no need to put everything concerning all networds (see final remark in Appendix)}
 
@@
 
-FE modelling of the cutting process is very expensive in CPU computation time because of the coupling of many nonlinear phenomena and the large amount of tiny finite elements.
-Mass scaling (MS) is introduced in the model to reduce the CPU computation time while checking that it does not influence the results (forces and energies) via a mass scaling sensitivity study.
-MS factors, ${MS}_f$, ranging from \num{1E6} (theoretical scaling of CPU time of $\sqrt{{MS}_f} = \num{1000}$) to 1 (no scaling) have been used for one cutting condition ($\lambda_s$ = \qty{0}{\degree}, $v_c$ = \qty{30}{\m\per\min} and $h$ = \qty{60}{\um}).
+FE modelling of the cutting process is very expensive in terms of CPU time due to the coupling of many nonlinear phenomena and the large amount of tiny finite elements.
+Mass scaling (MS) is introduced into the model to reduce the CPU computation time while checking that it does not influence the results (forces and energies) via a mass scaling sensitivity study.
+MS factors, ${MS}_f$, ranging from \num{1E6} (theoretical CPU time scale of $\sqrt{{MS}_f} = \num{1000}$) to 1 (no scale) were used for a cut condition ($\lambda_s$ = \qty{0}{\degree}, $v_c$ = \qty{30}{\m\per\min} and $h$ = \qty{60}{\um}).
 The same signal processing procedure is applied to the numerical forces as to the experimental forces (cf.
-\ref{ExpSet}): they are filtered with a second-order low-pass Bessel filter at \qty{750}{\Hz} before computing the mean value at steady state.
-Table \ref{tab:MS} gives the results of the model with MS normalized ($\hat{F_i}$) by these of the model without MS:
-%
+\ref{ExpSet}): they are filtered with a second order low-pass Bessel filter at \qty{750}{\Hz} before calculating the steady state mean value.
+Table \ref{tab:MS} gives the results of the model with MS normalized ($\hat{F_i}$) by those of the model without MS:
+
 \begin{equation}
@@
 with $i = c$ for the cutting force and $i = f$ for the feed force.
-As expected, actual speed-up does not increase linearly with the ${MS}_f$, but it is still significant.
-${MS}_f$ of \num{1E6} leads to unstable computation and ${MS}_f$ of 1E5 results in erratic forces evolutions.
-These results are confirmed by high values of the kinetic ($KE$) on internal ($IE$) energies ratio (it should not exceed a few \% \cite{wang_Investigation_2011, ducobu_Introduction_2015}).
-An ${MS}_f$ value of 1E3 is selected as it provides a good balance between computation time reduction and impact on forces, while keeping $\frac{KE}{IE}$ below 1\%.
-To provide an order of magnitude of CPU computation time, between \qty{10}{\hour} and \qty{50}{\hour} (depending on the value of $h$) are needed on 4 cores of an Intel i7-5700HQ CPU at \qtyrange{2.7}{3.5}{\GHz}.
-
+As expected, the real speed does not increase linearly with the ${MS}_f$, but it remains significant.
+A ${MS}_f$ of \num{1E6} leads to an unstable computation and a ${MS}_f$ of \num{1E5} leads to erratic force evolutions.
+These results are confirmed by high values of the ratio of the kinetic ($KE$) to the internal ($IE$) energies (it should not exceed a few \unit{\%} \cite{wang_Investigation_2011, ducobu_Introduction_2015}).
+A value of ${MS}_f$ of 1E3 is chosen as it offers a good balance between reducing the computation time and the impact on the forces, while keeping the $\frac{KE}{IE}$ below \qty{1}{\%}.
+To provide an order of magnitude of CPU computation time, between \qty{10}{\hour} and \qty{50}{\hour} (depending on the value of $h$) are required on 4 cores of an Intel i7-5700HQ CPU at \qtyrange{2.7}{3.5}{\GHz}.
 %
@@
 \hline\noalign{\smallskip}
-$MS_f$ & CPU scaling & Speed-up & $\hat{F_c}$ & $\hat{F_f}$ & $\frac{KE}{IE}$ (\%)\\
+$MS_f$ & CPU scaling & Speed-up & $\hat{F_c}$ & $\hat{F_f}$ & $\frac{KE}{IE}$ (\unit{\%})\\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 
-The number of neurons on the hidden layers may influence the results.
-A sensitivity study on the number of neurons for the first hidden layer, $\zeta$, is carried out to select the ANN providing the best balance between CPU computation time and quality of the results.
+The number of neurons in the hidden layers may influence the results.
+A sensitivity study on the number of neurons of the first hidden layer, $\zeta$, is performed in order to select the ANN offering the best balance between CPU computation time and quality of the results.
 The results of the study are provided in Table \ref{tab:NbNeurons}.
-$\check{F_i}$ corresponds to the results of the model with ANN normalized by these of the model with the built-in JC model:
-%
+The $\check{F_i}$ corresponds to the results of the model with ANN normalized by those of the model with the built-in JC model:
+
 \begin{equation}
@@
 %
-They show no influence on the forces when compared to the built-in Johnson-Cook model, only computation time is influenced.
-A first hidden layer with 9 neurons is therefore selected as it leads to the lowest CPU computation time increase.
+They show no influence on the numerical results for the forces compared to the built-in Johnson-Cook model, only the computation time is influenced by the number of neurons in the first hidden layer and increases with it.
+A first hidden layer of 9 neurons is therefore selected as it leads to the smallest increase in CPU computation time, without influence on the final result.
 
@@
 \hline\noalign{\smallskip}
-$\zeta$  & Time increase (\%) & $\check{F_c}$ & $\check{F_f}$\\
+$\zeta$  & Time increase (\unit{\%}) & $\check{F_c}$ & $\check{F_f}$\\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 
-An example of temporal evolutions of numerical and experimental forces is plotted for the 3 directions in Figure \ref{fig:ExpNum_Forces_v10_40µ_6} at $\lambda_s =$ \qty{6}{\degree}, $v_c =$ \qty{10}{\m\per\min} and $h =$ \qty{40}{\m\per\min}.
-Computation of the FE models is carried out until a few microseconds after the steady state is reached.
-Then, linear extrapolation (dashed line between the two last markers in Figure \ref{fig:ExpNum_Forces_v10_40µ_6}) is used to provide numerical values during the same time range as the experimental values.
-Mean and standard deviation ($2\,\sigma$) are computed from the 3 experimental values.
-The resulting dispersion is plotted in Figure \ref{fig:ExpNum_Forces_v10_40µ_6} around the mean values of each force.
-Steady state takes more time to be reached for the experiments than in the numerical model, particularly for the cutting force.
-Dispersion around the mean force evolution is larger for the feed force than for the cutting force, while the mean feed force value is 46\% of the mean cutting force value.
-The numerical cutting force is very close to the experimental mean cutting force; it is only 4\% larger.
-This difference, $\Delta j$, is computed by
+An example of the time evolution of the numerical and experimental forces is plotted for the 3 directions in Figure \ref{fig:ExpNum_Forces_v10_40µ_6} at $\lambda_s =$ \qty{6}{\degree}, $v_c =$ \qty{10}{\m\per\min} and $h =$ \qty{40}{\m\per\min}.
+The FE models are calculated up to a few microseconds after the stationary state is reached.
+Then, a linear extrapolation (dashed line between the last two markers in Figure \ref{fig:ExpNum_Forces_v10_40µ_6}) is used to provide numerical values for the same time range as the experimental values.
+The mean and standard deviation ($2\,\sigma$) are calculated from the 3 experimental values.
+The resulting dispersion is shown in Figure \ref{fig:ExpNum_Forces_v10_40µ_6} around the mean values of each force.
+Steady state takes longer to be reached for the experiments than for the numerical model, in particular for the cutting force.
+The dispersion around the evolution of the mean force is greater for the feed force than for the cutting force, while the mean value of the feed force is \qty{46}{\%} of the mean value of the cutting force.
+The numerical cutting force is very close to the experimental average cutting force; it is only \qty{4}{\%} higher.
+This difference, $\Delta j$, is calculated by :
+
 %
@@
 %
-with $j$ the cutting force, the feed force, the passive force or the chip thickness. $j^\text{(sim)}$ is the mean value from the simulation, while $j^\text{(exp)}$ is the mean experimental value.
+where $j$ is the cutting force, the feed force, the passive force or the chip thickness.
+$j^\text{(sim)}$ is the average value from the simulation, while $j^\text{(exp)}$ is the average experimental value.
 
-The numerical feed force is underestimated by the model, but it is at the boundary of the 95\% experimental confidence interval.
-The numerical passive force difference is also underestimated and it is not in the narrower experimental dispersion.
-The difference between the mean values of experimental and numerical feed and passive forces is 25\%.
-A feed force less well modelled than the cutting force is typical of FE models of the cutting process and the difference with the experimental value is similar to other studies for a less extensive range of cutting conditions \cite{sima_Modified_2010, ducobu_Material_2016, karpat_Temperature_2011, zhang_Chip_2011,afrasiabi_NumericalExperimental_2021}.
-Hardt and Bergs \cite{hardt_Three_2021} also obtained higher differences for the feed and the passive force than for the cutting force.
-The difference for the passive force was higher than for the feed force, which is the opposite observation from this work.
+The numerical feed force is underestimated by the model, but is within the \qty{95}{\%} experimental confidence interval.
+The numerical passive force difference is also underestimated and is not within the narrowest experimental dispersion.
+The difference between the mean values of the experimental and numerical feed and passive forces is \qty{25}{\%}.
+A less well modelled feed force than the cutting force is typical of FE models of the cutting process and the difference with the experimental value is similar to other studies for a narrower range of cutting conditions \cite{sima_Modified_2010, ducobu_Material_2016, karpat_Temperature_2011, zhang_Chip_2011,afrasiabi_NumericalExperimental_2021}.
+Hardt and Bergs \cite{hardt_Three_2021} also obtained larger differences for feed and passive force than for cutting force.
+The difference for passive force was higher than for feed force, which is the opposite observation of this work.
 
@@
 Numerical chips at $v_c =$ \qty{10}{\m\per\min} and $h =$ \qty{40}{\um} for $\lambda_s =$ \qty{0}{\degree} and $\lambda_s =$ \qty{6}{\degree} are provided in Figures \ref{fig:ChipsNum} and \ref{fig:ChipsNumBack}.
-When the cutting edge inclination is \qty{0}{\degree}, both sides of the chip are identical and a symmetry plane can be drawn in the middle of the workpiece (Figure \ref{fig:ChipsNumBack} (a)).
-On the contrary, for the cutting edge inclination of \qty{6}{\degree}, the chip is not aligned with the workpiece any more.
-The chip bends on one side due to the orientation of the tool and the symmetry is lost for both the geometry, and the thermal and mechanical fields as highlighted in Figure \ref{fig:ChipsNumBack} (b).
-This produces helical chips for the inclination angle of \qty{6}{\degree} as in the experiments.
-Figure \ref{fig:ChipNumTop} shows the variation of the chip thickness across its width: it is thicker in the middle (i.e., the body of the chip) than on its sides.
-This stresses the importance of 3D modelling, even for the orthogonal cutting configuration as previously highlighted \cite{ducobu_Finite_2017}.
-3D modelling also allows to reproduce the side flow occurring in the experiments for both cutting edge inclination values (Figure \ref{fig:ChipsNum}), contrary to a 2D model \cite{xu_Simulation_2021, ambrosio_New_2022, ducobu_Finite_2017}.
+When the inclination of the cutting edge is \qty{0}{\degree}, both sides of the chip are identical and a symmetry plane can be drawn in the middle of the workpiece (Figure \ref{fig:ChipsNumBack} (a)).
+On the other hand, for a slope of the cutting edge of \qty{6}{degree}, the chip is no longer aligned with the workpiece.
+The chip bends to one side due to the orientation of the tool and symmetry is lost in both the geometry and the thermal and mechanical fields, as shown in figure \ref{fig:ChipsNumBack} (b).
+This produces helical chips for the inclination angle of \qty{6}{degree} as in the experiments.
+Figure \ref{fig:ChipNumTop} shows the variation of the chip thickness across its width: it is thicker in the middle (i.e.
+the body of the chip) than on its sides.
+This underlines the importance of 3D modelling, even for the orthogonal cutting configuration as highlighted earlier \cite{ducobu_Finite_2017}.
+The 3D modelling also allows reproducing the lateral flow that occurs in the experiments for both values of cutting edge inclination (Figure \ref{fig:ChipsNum}), unlike a 2D model \cite{xu_Simulation_2021, ambrosio_New_2022, ducobu_Finite_2017}.
 Although this leads to higher computation times, future cutting models should be in 3D, even when orthogonal cutting is considered.
-In this case, it is recommended to take advantage of the symmetry of the configuration to reduce computation time.
-This simplification has not been included in this study to avoid any difference in the FE models between the 2 cutting edge inclinations.
+In this case, it is recommended to take advantage of the symmetry of the configuration to reduce the computation time.
+This simplification has not been included in this study to avoid any difference in the FE models between the 2 inclinations of the cutting edge.
 
@@
 
-The increase of the cutting force with the uncut chip thickness is clearly observed in Figures \ref{fig:Fx_0} and \ref{fig:Fx_6} for both experimental and numerical results at the 2 inclination angles, as well as the decrease of the force with the increase in the cutting speed.
-This shows temperature softening domination on strain rate hardening for Ti6Al4V and that it is accurately modelled.
-The increase of the inclination angle from \qty{0}{\degree} to \qty{6}{\degree} slightly reduces the cutting force; this is well captured by the model.
-For cutting speeds of \qtyrange{20}{40}{\m\per\min} and inclination angle of \qty{0}{\degree}, $F_c$ is almost constant with the cutting speed for uncut chip thicknesses of \qty{40}{\um} and \qty{60}{\um}, while it slightly decreases for \qty{80}{\um}; this small stabilization is less marked for the modelling.
+The increase in cutting force with uncut chip thickness is clearly observed in Figures \ref{fig:Fx_0} and \ref{fig:Fx_6} for both experimental and numerical results at the 2 inclination angles, as well as the decrease in force with increasing cutting speed.
+This shows that temperature softening dominates strain rate hardening for Ti6Al4V and is accurately modelled.
+Increasing the inclination angle from \qty{0}{\degree} to \qty{6}{\degree} slightly reduces the cutting force; this is well captured by the model.
+For cutting speeds of \qtyrange{20}{40}{\m\per\min} and an inclination angle of \qty{0}{\degree}, $F_c$ is almost constant with cutting speed for uncut chip thicknesses of \qty{40}{\um} and \qty{60}{\um}, while it decreases slightly for \qty{80}{\um}; this small stabilization is less marked for the model.
 
 An increase in the deviation around the mean value with the cutting speed is noted for values above \qty{10}{\m\per\min}.
-All numerical values are within a confidence interval of 95\% of the experiments (35 out of 36 conditions are within a confidence interval of 68\%).
-The mean difference with the experiments is 4\%, which is remarkable, moreover given the wide range of cutting conditions considered and the absence of tuning of the model.
-This highlights the predictive ability and the accuracy of the FE model for both inclination angles.
+All numerical values are within \qty{95}{\%} confidence of the experiments (35 of the 36 conditions are within \qty{68}{\%} confidence).
+The average difference with the experiments is \qty{4}{\%}, which is remarkable, also considering the wide range of cutting conditions considered and the absence of model tuning.
+This underlines the predictive ability and accuracy of the FE model for both inclination angles.
 
-Figures \ref{fig:Fy_0} and \ref{fig:Fy_6} show the results for the feed force, where the two clearest trends for the experiments are its decrease with inclination angle and its increase with the uncut chip thickness (even if it is smaller than the expectations).
-For \qty{80}{\um}, $F_f$ globally decreases with $v_c$ in the experiments.
-For \qty{40}{\um} and \qty{60}{\um}, the force decreases at lower $v_c$ and then increases for \qty{0}{\degree}, while a decrease is observed at all $v_c$ for \qty{6}{\degree} (experimental dispersion is high for both inclination angles, but the mean trend with the cutting speed is clear at \qty{6}{\degree}, not at \qty{0}{\degree}).
-For the numerical values, the global trend is the same for the 3 uncut chip thicknesses and both inclination angles: a decrease for the lowest $v_c$ values and then an increase.
-It must be noted that the numerical model does not handle correctly the feed force trends: as clearly shown by Figure \ref{fig:Fy_6}, the numerical forces have globally an increasing trend with the cutting speed, while their mean value mostly decreases when the uncut chip thickness increases.
-Differences between the mean numerical and experimental values increase with the uncut chip thickness: forces are closer at \qty{40}{\um} than at \qty{80}{\um}.
-The numerical values are mostly not within the 95\% confidence interval (it has no clear evolution with the cutting conditions).
-Coupled with the differences in trends, it shows that $F_f$ is less well modelled (mean difference is 39\%) than $F_c$ as usual in FE modelling of the cutting process and even more so in 3D \cite{hardt_Three_2021}.
+Figures \ref{fig:Fy_0} and \ref{fig:Fy_6} show the results for the feed force, where the two clearest trends for the experiments are its decrease with the inclination angle and its increase with the thickness of the uncut chip (even though it is lower than expected).
+For \qty{80}{\um}, $F_f$ decreases overall with $v_c$ in the experiments.
+For \qty{40}{\um} and \qty{60}{\um}, the force decreases at lower $v_c$, then increases for \qty{0}{\degree}, while a decrease is observed at all $v_c$ for \qty{6}{\degree} (the experimental dispersion is high for both inclination angles, but the average trend with cutting speed is clear at \qty{6}{\degree}, not at \qty{0}{\degree}).
+For the numerical values, the overall trend is the same for the 3 uncut chip thicknesses and the two inclination angles: a decrease for the lowest values of $v_c$ and then an increase.
+It should be noted that the numerical model does not correctly handle the trends of the feed forces: as Figure \ref{fig:Fy_6} clearly shows, the numerical forces have an overall increasing trend with the cutting speed, while their average value mainly decreases when the uncut chip thickness increases.
+The differences between the average numerical and experimental values increase with the thickness of the uncut chip: the forces are closer at \qty{40}{\um} than at \qty{80}{\um}.
+The numerical values are generally not within the \qty{95}{\%} confidence interval (they do not clearly change with the cutting conditions).
+Coupled with the differences in trends, this shows that $F_f$ is less well modelled (the average difference is \qty{39}{\%}) than $F_c$ as usual in FE modelling of the cutting process and even more so in 3D \cite{hardt_Three_2021}.
 The influence of the uncut chip thickness on the feed force should therefore be improved.
-Material constitutive model parameters are known to have an impact on the forces (and on the chip morphology) \cite{ducobu_Importance_2017,kugalurpalanisamy_Identification_2022}.
-The friction model should be improved as well to enhance the results \cite{hardt_Three_2021}.
+The parameters of the material constitutive model are known to have an impact on the forces (and on the chip morphology) \cite{ducobu_Importance_2017,kugalurpalanisamy_Identification_2022}.
+The friction model should also be improved to strengthen the results \cite{hardt_Three_2021}.
 
-Passive force is non-zero for the inclination angle of \qty{6}{\degree} (Figure \ref{fig:Fz_6}).
-As the cutting force, it increases with the uncut chip thickness and it decreases with the cutting speed.
-Comparison with the experiments is globally the same as for $F_c$, except for a larger difference in the magnitude of $F_p$ (mean difference is 26\%, but it is small in absolute – less than \qty{5}{N}).
-The numerical values are mostly not in the 95\% experimental confidence interval.
-A lower magnitude of the passive force from the simulation than from the experiments with the right trends when the cutting conditions changed was also observed by Hardt and Bergs \cite{hardt_Three_2021}.
-Differences were mainly attributed to differences in the cutting edge radius, the modelling of friction and the material constitutive model.
-In this work, impact of the cutting edge radius can be neglected as it is the same in the model as in the experiments.
+The passive force is non-zero for the inclination angle of \qty{6}{\degree} (Figure \ref{fig:Fz_6}).
+Like the cutting force, it increases with the thickness of the uncut chip and decreases with the cutting speed.
+The comparison with experiments is broadly the same as for $F_c$, except for a greater difference in the magnitude of $F_p$ (the average difference is \qty{26}{\%}, but it is small in absolute terms - less than \qty{5}{N}).
+Most of the numerical values do not fall within the experimental \qty{95}{\%} confidence interval.
+A lower magnitude of the passive force from the simulation than from the experiments with the correct trends when the cutting conditions change was also observed by Hardt and Bergs \cite{hardt_Three_2021}.
+The differences were mainly attributed to differences in cutting edge radius, friction modelling and material constitutive model.
+In this work, the impact of the cutting edge radius can be neglected as it is the same in the model as in the experiments.
 
-Regarding the chips morphology, all the chips are continuous. For both the simulation and the experiments, the chip thickness ratio, $\lambda_h$:
+As far as the chip morphology is concerned, all chips are continuous. For both the simulation and the experiments, the chip thickness ratio, $\lambda_h$ :
 %
@@
 %
-with $h$ the uncut chip thickness and $h'$ the chip thickness, is almost independent of the uncut chip thickness (Figures \ref{fig:h0} and \ref{fig:h6}).
-It is slightly reduced from $\lambda_s =$ \qty{0}{\degree} to $\lambda_s =$ \qty{6}{\degree}, meaning that the chip thickness decreases with the inclination angle.
-This influence is underestimated by the model: the reduction of $\lambda_h$ is lower than in the experiments.
-The mean difference between experimental and numerical $\lambda_h$ is 17\% across the whole range of cutting conditions.
-The chip thickness ratio decreases with the cutting speed because of the reduction of friction, which is correctly captured by the model.
-As for the feed force, the results should be improved by more complex friction models and a set of material constitutive parameters for which the identification includes the forces and the chip thickness \cite{kugalurpalanisamy_Identification_2022}.
+with $h$ the thickness of the uncut chip and $h'$ the thickness of the chip, is almost independent of the thickness of the uncut chip (Figures \ref{fig:h0} and \ref{fig:h6}).
+It is slightly reduced from $\lambda_s =$ \qty{0}{\degree} to $\lambda_s =$ \qty{6}{\degree}, which means that the chip thickness decreases with the angle of inclination.
+This influence is underestimated by the model: the reduction of $\lambda_h$ is smaller than in the experiments.
+The average difference between the experimental and numerical $\lambda_h$ is \qty{17}{\%} over the whole range of cutting conditions.
+The chip thickness ratio decreases with cutting speed due to the reduction in friction, which is correctly accounted for by the model.
+As with the feed force, the results should be improved by more complex friction models and a set of material parameters for which the identification includes forces and chip thickness: \cite{kugalurpalanisamy_Identification_2022}.
 
@@
 
-Differences computed according to equation \ref{eq:diff} are shown in Table \ref{tab:Synth} to provide a quantitative overview of the results.
+The differences calculated according to the equation \ref{eq:diff} are presented in Table \ref{tab:Synth} to provide a quantitative overview of the results.
 The cutting force is the best modelled quantity as observed in the literature.
-This results could be expected as the set of parameters of the constitutive model was selected mainly thanks to its good approximation of the cutting force \cite{ducobu_Importance_2017}.
-As that selection was carried out with a 2D model, the results show the capacity of the model to correctly handle the third (passive) force.
-Based on the mean differences, the performance of the model is very close for the cutting and the feed forces for both cutting edge inclinations, even if a small degradation (1\% and 2\%, respectively) is noted for \qty{6}{\degree}.
-This degradation is larger (7\%) for the chip thickness ratio and should be linked with the difference in the passive force.
-Indeed, the modellings of the chip thickness and of the out-of-plane force are deeply linked.
-Improving the friction at the tool -- workpiece interface should be a key point.
-It must be noted that the chip thickness is very well modelled in some cutting conditions with a minimal difference of \qty{2}{\%}.
-The difference is larger for the feed force than for the passive force, an opposite trend to Hardt and Bergs' \cite{hardt_Three_2021}.
-Both mean and range (min -- max) of differences are larger for the feed force.
-The smaller range of the passive force confirms an offset for all the cutting conditions, similarly to the results of Hardt and Bergs \cite{hardt_Three_2021}.
-Again, the modelling of friction should be the first aspect of the model to improve in future developments.
+This result was to be expected as the parameter set of the constitutive model was selected mainly due to its good approximation of the cutting force \cite{ducobu_Importance_2017}.
+As this selection was made with a 2D model, the results show the ability of the model to correctly handle the third (passive) force.
+Based on the mean differences, the performance of the model is very close for the cutting and feed forces for both inclinations of the cutting edge, although a small degradation (\qty{1}{\%} and \qty{2}{\%}, respectively) is noted for \qty{6}{\degree}.
+This degradation is more important (\qty{7}{\%}) for the chip thickness ratio and must be linked to the difference in passive force.
+Indeed, the chip thickness and out-of-plane force models are deeply linked.
+Improving the friction at the tool-workpiece interface should be a key point.
+It should be noted that the chip thickness is very well modelled under certain cutting conditions with a minimum difference of \qty{2}{\%}.
+The difference is larger for the feed force than for the passive force, a trend opposite to that of Hardt and Bergs.
+The mean and range (min -- max) of the differences are larger for the forward force.
+The smaller range of the passive force confirms a shift for all cutting conditions, similar to the results of Hardt and Bergs \cite{hardt_Three_2021}.
+Again, the friction modelling should be the first aspect of the model to be improved in future developments.
 
@@
 \hline\noalign{\smallskip}
-Difference & $\Delta F_c$ (\%) & $\Delta F_f$ (\%) & $\Delta F_p$ (\%) & $\Delta \lambda_h$ (\%)\\
+Difference & $\Delta F_c$ (\unit{\%}) & $\Delta F_f$ (\unit{\%}) & $\Delta F_p$ (\unit{\%}) & $\Delta \lambda_h$ (\unit{\%})\\
 \hline\noalign{\smallskip}
@@
 
-An experimental and numerical study of the free orthogonal and oblique cutting of Ti6Al4V has been carried out for a wide range of cutting conditions using an ANN-based material constitutive model.
+An experimental and numerical study of the orthogonal and oblique free cutting of Ti6Al4V was carried out for a wide range of cutting conditions using an ANN-based material constitutive model.
 The following main conclusions are drawn:
 \begin{itemize}
-  \item The experimental study has been carried out with the same setup in free orthogonal and free oblique cutting for the titanium alloy Ti6Al4V (the only change is the cutting edge inclination).
-It is a reference to assess the performances of the 3D FE model introducing an ANN-based constitutive model and developed in the same conditions.
-An unpreviously seen wide range of cutting conditions, 36, is considered, including 2 cutting edge inclinations.
-  \item Accurate evaluation of fundamental variables and their trends in 3D with the absence of tuning of both numerical parameters and model features when cutting conditions and inclination angle are significantly modified is a strong novelty of this work.
-Only changing the inclination angle to move from free orthogonal to oblique cutting while maintaining the quality of the results has no equivalent in the current literature, moreover as no study (experimental or numerical) on free oblique cutting is available.
-  \item \FD{Add one bullet on ANN and the associated future works?}
-  \item The cutting force is the best modelled quantity with a mean difference of \qty{4}{\%} with the experiments.
-The chip thickness ratio and the passive force show a higher deviation with the experiments (17\% and 26\%, respectively), while their trends when the cutting conditions change are accurate.
-This corresponds to the expected results provided by a predictive model.
-The difference for the feed force is higher (39\%), and opposite trends by comparison with the experimental reference are observed.
-The absence of influence of the uncut chip thickness on friction in the model seems to be one of the aspects to include first in future works.
-The model turns out to handle the apparition of the third, out-of-plane, force well with no significant degradation of the results.
-  \item Predictive abilities of the model make it adequate for the development of tools with a straight cutting edge, for example.
-This work moreover demonstrates the ability to model materials' behaviour with ANN and opens possibilities in this promising direction.
+  \item The experimental study was carried out with the same set-up in free orthogonal and free oblique cuts for the titanium alloy Ti6Al4V (the only change is the inclination of the cutting edge).
+This is a reference to evaluate the performance of the FE 3D model introducing an ANN-based constitutive model developed under the same conditions.
+A wide range of novel cutting conditions, 36, is considered, including 2 cutting edge inclinations.
+  \item A major novelty of this work is the accurate evaluation of the fundamental variables and their trends in 3D, without the need to adjust the numerical parameters and the model characteristics when the cutting conditions and the inclination angle are changed significantly.
+The mere fact of changing the inclination angle from free orthogonal cutting to oblique cutting while maintaining the quality of the results has no equivalent in the current literature, especially since no studies (experimental or numerical) on free oblique cutting are available.
+  \item Taking into account the material's flow law by means of a neural network makes it possible to overcome the limitations of conventional flow laws and to reduce the approximations associated with the establishment of an analytical formulation of the flow law as conventionally adopted.
+The numerical model is then able to better reproduce the real behaviour of the material and to take into account thermomechanical transformations which are sources of non-linearities, difficult to take into account with an analytical flow law model.
+Current work, in the LGP, on the behaviour of a modified carbon alloy AISI P20 shows the advantages of this approach compared to models in the literature such as Johnson-Cook, Zerilli-Armstrong \cite{Muralli-2017-Performance} or Hansel-Spittel \cite{chadha2018approach}.
+  \item The cutting force is the best modelled quantity with an average difference of \qty{4}{\%} with the experiments.
+Chip thickness ratio and passive force show a larger deviation from the experiments (\qty{17}{\%} and \qty{26}{\%}, respectively), but their trends as the cutting conditions change are accurate.
+This is in line with the expected results provided by a predictive model.
+The deviation for feed force is higher (\qty{39}{\%}), and opposite trends compared to the experimental reference are observed.
+The lack of influence of uncut chip thickness on friction in the model seems to be one of the aspects to be included as a priority in future work.
+The model is found to handle the occurrence of the third force, out of plane, well without significant degradation of the results.
+  \item The predictive capabilities of the model make it suitable for the development of straight-edged tools, for example.
+This work also demonstrates the ability to model material behaviour with ANN and opens up possibilities in this promising direction.
 \end{itemize}
@@
 
-In this Appendix, we present the values obtained after the training phase of an ANN containing 9 neurons in the first hidden layer and 7 neurons in the second hidden layer.
-
-The training of the neural network was performed using a data set containing $3\,430$ data points defined by:
+In this appendix, we present the values obtained after the training phase of an ANN containing 9 neurons in the first hidden layer and 7 neurons in the second hidden layer.
+Conforming to \cite{pantale_Efficient_2022}, this one is referred ANN-3-9-7-1-sig.
+The training of the neural network was performed using a dataset containing \num{3430} data points defined by :
 \begin{itemize}
-\item $70$ values for $\varepsilon^p\in[0.0,3.0]$, so that $[\varepsilon^p]_{min}=0$ and $[\varepsilon^p]_{max}=3$.
-\item $7$ plastic strain rates $\mdot{\varepsilon}^p\in[1, 10, 50, 500, 5\,000, 50\,000, 500\,000]$, so that $[\ln(\mdot{\varepsilon}^p)]_{min}=0$ and $[\ln(\mdot{\varepsilon}^p)]_{max}=13.12236$.
-\FD{Add units to values?}
-\item  $7$ temperatures $T\in[293, 400, 500, 700, 900, 1\,200, 1\,500]$, so that $[T]_{min}=293$ and $[T]_{max}=1\ 500$. \FD{Add units to values?}
+\item \num{70} equidistant values for $\varepsilon^p\in[0,3]$, so that $[\varepsilon^p]_{min}=0$ and $[\varepsilon^p]_{max}=3$.
+\item \num{7} plastic strain rates $\mdot{\varepsilon}^p\in[\qty{1}{\per\s}, \qty{10}{\per\s}, \qty{50}{\per\s}, \qty{500}{\per\s}, \qty{5000}{\per\s}, \qty{50000}{\per\s}, \qty{500000}{\per\s}]$, so that $[\ln(\mdot{\varepsilon}^p)]_{min}=0$ and $[\ln(\mdot{\varepsilon}^p)]_{max}=13.12236$.
+\item \num{7} temperatures $T\in[\qty{293}{\K}, \qty{400}{\K}, \qty{500}{\K}, \qty{700}{\K}, \qty{900}{\K}, \qty{1200}{\K}, \qty{1500}{\K}]$, so that $[T]_{min}=\qty{293}{\K}$ and $[T]_{max}=\qty{1500}{\K}$.
 \end{itemize}
 
-Stresses in the training dataset ranges from $[\sigma^y]_{min}=171.44$ to $[\sigma^y]_{max}=2606.12$.
-The results of the training process are given below for quantities $\w_1$, $\w_2$, $\overrightarrow{w}$, $\overrightarrow{b_1}$, $\overrightarrow{b_2}$ and $b$.
+Stresses in the training dataset ranges from $[\sigma^y]_{min}=\qty{171.4}{\MPa}$ to $[\sigma^y]_{max}=\qty{2606.1}{\MPa}$.
+The results of the training process are given here after for the ANN quantities $\w_1$, $\w_2$, $\overrightarrow{w}$, $\overrightarrow{b_1}$, $\overrightarrow{b_2}$ and $b$.
+The weight matrix for the first hidden layer $\w_1$ is a $9\times3$ matrix:
 
@@
 
+The weight matrix for the second hidden layer $\w_2$ is a $7\times9$ matrix:
+
 \begin{equation*}
@@
 
+The weight vector for the output layer $\overrightarrow{w}$ is a $7$ components vector:
+
 \begin{equation*}
@@
 
+The biases of the first hidden layer $\overrightarrow{b_1}$ is a $9$ components vector:
 \begin{equation*}
@@
 
+The biases of the second hidden layer $\overrightarrow{b_2}$ is a $7$ components vector:
 \begin{equation*}
@@
 
+The bias of the output layer $b$ is a scalar:
 \begin{equation*}
@@
 \end{equation*}
+
+The corresponding coefficients for the other networks identified during this work (ANN-3-11-7-1-sig, ANN-3-13-7-1-sig, ANN-3-15-7-1-sig and ANN-3-17-7-1-sig) can be found in \cite{pantale_Coefficients_2022}.
 

### 2022-10-12 Article.tex
Small corrections of all Article

@@
 \DeclareMathOperator{\sigmoid}{sig}
-%\newcommand{\lay}[1]{^{(#1)}}
+\newcommand{\snsp}[2]{{#1}_{\!#2}}    % Single negative space
+\newcommand{\dnsp}[2]{{#1}_{\!\!#2}}  % Double negative space
 \newcommand{\dotp}{\boldsymbol{\cdot}}
@@
 The predictive performance of the model (i.e., the evaluation of the trends of fundamental variables with the absence of tuning of both numerical parameters and model features when cutting conditions are significantly modified) is high for the forces, mainly cutting and passive, and the chip thickness ratio on all 36 cutting conditions.
-The accuracy of the main cutting force is excellent: the mean difference with the experiments is \qty{4}{\%}, within the experimental dispersion.
+The accuracy of the main cutting force is excellent: the average difference with the experiments is \qty{4}{\%}, within the experimental dispersion.
 No significant degradation of the results is brought by the apparition of the third, out-of-plane, force, which shows the ability of the model to handle orthogonal and oblique cutting configurations.
@@
 Combinations of formulations, such as Arbitrary Lagrangian-Eulerian (ALE) and Coupled Eulerian-Lagrangian (CEL), are increasingly being used to avoid (or reduce) mesh distortions \cite{ducobu_Application_2016}.
-The Coupled Eulerian-Lagrangian (CEL) formulation has recently been successfully applied to the modelling of cutting (2D orthogonal configuration): it provides accurate results with realistic chip shape and no mesh distortion.
+The CEL formulation has recently been successfully applied to the modelling of cutting (2D orthogonal configuration): it provides accurate results with realistic chip shape and no mesh distortion.
 The first 3D applications are found in recent works \cite{xu_Simulation_2021, ducobu_Finite_2017, ambrosio_New_2022, vovk_Finite_2020, hardt_Three_2021}.
@@
 One of the points in favour of its adoption is the rather limited number of parameters to be identified, 5: $A$, $B$, $C$, $m$ and $n$.
-$\mdot{\varepsilon}_0^p$ is the reference plastic strain rate, while $T_{\text{room}}$ and $T_{\text{melt}}$ are respectively the ambient (room) and melting temperature.
+Here, $\mdot{\varepsilon}_0^p$ is the reference plastic strain rate, while $T_{\text{room}}$ and $T_{\text{melt}}$ are respectively the ambient (room) and melting temperature.
 More recent models developed on this basis, such as that of Calamaz et al.
@@
 Acquisition is performed at \qty{3}{\kHz} using a Kistler 5697A2 data acquisition system and DynoWare software.
-The recorded forces are then filtered with a second-order low-pass Bessel filter at \qty{750}{\Hz} before calculating the mean value of the steady state signal.
+The recorded forces are then filtered with a second-order low-pass Bessel filter at \qty{750}{\Hz} before calculating the average value of the steady state signal.
 
@@
 
-In a preliminary phase, after having selected the global architecture of the neural network, it is necessary to proceed to its training from experimental data resulting from tests on a Gleeble-type thermomechanical simulator.
-These experimental data, presented in the form of a data table containing the plastic strain $\varepsilon^p$, the plastic strain rate $\mdot{\varepsilon}^p$, the temperature $T$ and the flow stress $\sigma^y$, are processed by a learning algorithm, developed at LGP, in Python, using the Tensorflow library.
-Generally, one to two hours of training on a Dell XPS13 7390 laptop running Ubuntu 20.04 64~bits with 16~GiB of Ram and an Intel 4-core i7-10510U processor allow obtaining a model with a sufficient convergence for the application.
+In a preliminary phase, after having selected the global architecture of the neural network, it is necessary to proceed to its training from some inputs.
+The inputs for this application were generated from the Johnson-Cook flow law expression reported in Equation (\ref{eq:J-C}) and the identified parameters reported in Table \ref{tab:prop}.
+This approach was chosen to demonstrate the ability of the neural network flow law to replace a classically formulated flow law such as Johnson-Cook's for the simulation of metal cutting.
+In future developments, experimental tests on a Gleeble thermomechanical simulator will be used to generate this network training data.
+The training data, presented in the form of a data table containing the plastic strain $\varepsilon^p$, the plastic strain rate $\mdot{\varepsilon}^p$, the temperature $T$ and the flow stress $\sigma^y$, is processed by a learning algorithm, developed at LGP, in Python, using the Tensorflow library.
+One hour of training on a Dell XPS13 7390 laptop running Ubuntu 20.04 64~bits with 16~GiB of Ram and an Intel 4-core i7-10510U processor allow obtaining the converged parameters of the ANN model.
 
@@
 
-The main advantage of this approach (the use of an ANN), after the learning phase, is that, for example, the output $\sigma^y$ of the network is now linked to the inputs $\varepsilon^p$, $\mdot{\varepsilon}^p$, and $T$ by the equations (\ref{eq:ANN-preprocess}) to (\ref{eq:ANN-vonMises}) for a two hidden layers neural network with a sigmoid activation function as presented previously.
+The main advantage of this approach (the use of an ANN), after the learning phase, is that, for example, the output $\sigma^y$ of the network is now linked to the inputs $\varepsilon^p$, $\mdot{\varepsilon}^p$, and $T$ by the equations (\ref{eq:ANN-preprocess}) to (\ref{eq:ANN-vonMises}) for a two hidden layers neural network with a sigmoid activation function as proposed previously.
 
-Thus, in the VUHARD subroutine, the computation of the flow constraint $\sigma^y$ from the 3 input variables $\varepsilon^p$, $\mdot{\varepsilon}^p$, and $T$ is performed using the following procedure.
+Thus, in the VUHARD subroutine, the computation of the flow stress $\sigma^y$ from the 3 input variables $\varepsilon^p$, $\mdot{\varepsilon}^p$, and $T$ is performed using the following procedure.
 The first step is to scale the input data to the interval $[0,1]$ using the following equation:
@@
 \end{equation}
-where, $\overrightarrow{w}$ and $b$ are the weights and bias associated with the output layer.
+where, $\overrightarrow{w}$ and $b$ are the weights and the bias associated with the output layer.
 
-On the other hand, the three derivatives of the yield stress $\sigma^y$ with respect to the three input variables $\varepsilon^p$, $\mdot{\varepsilon}^p$, and $T$ are given by the following equations:
+On the other hand, the three derivatives of the yield stress $\sigma^y$ with respect to the three input variables $\varepsilon^p$, $\mdot{\varepsilon}^p$, and $T$ are given by the equation (\ref{eq:derivatives-ANN}):
 \begin{equation}
@@
 
-where $s'_i$ is the $i^{th}$ component of the vector $\overrightarrow{s}'$ defined by the following equation:
+where $s'_i$ is the $i^{th}$ component of the vector $\overrightarrow{s}'$ defined by the equation (\ref{eq:der-2-sig}):
 \begin{equation}
@@
 Mass scaling (MS) is introduced into the model to reduce the CPU computation time while checking that it does not influence the results (forces and energies) via a mass scaling sensitivity study.
-MS factors, ${MS}_f$, ranging from \num{1E6} (theoretical CPU time scale of $\sqrt{{MS}_f} = \num{1000}$) to 1 (no scale) were used for a cut condition ($\lambda_s$ = \qty{0}{\degree}, $v_c$ = \qty{30}{\m\per\min} and $h$ = \qty{60}{\um}).
+MS factors, $\dnsp{MS}{f}$, ranging from \num{1E6} (theoretical CPU time scale of $\sqrt{\dnsp{MS}{f}} = \num{1000}$) to 1 (no scale) were used for a cut condition ($\lambda_s$ = \qty{0}{\degree}, $v_c$ = \qty{30}{\m\per\min} and $h$ = \qty{60}{\um}).
 The same signal processing procedure is applied to the numerical forces as to the experimental forces (cf.
-\ref{ExpSet}): they are filtered with a second order low-pass Bessel filter at \qty{750}{\Hz} before calculating the steady state mean value.
+\ref{ExpSet}): they are filtered with a second order low-pass Bessel filter at \qty{750}{\Hz} before calculating the steady state average value.
 Table \ref{tab:MS} gives the results of the model with MS normalized ($\hat{F_i}$) by those of the model without MS:
@@
 with $i = c$ for the cutting force and $i = f$ for the feed force.
-As expected, the real speed does not increase linearly with the ${MS}_f$, but it remains significant.
-A ${MS}_f$ of \num{1E6} leads to an unstable computation and a ${MS}_f$ of \num{1E5} leads to erratic force evolutions.
+As expected, the real speed does not increase linearly with the $\dnsp{MS}{f}$, but it remains significant.
+A $\dnsp{MS}{f}$ of \num{1E6} leads to an unstable computation and a $\dnsp{MS}{f}$ of \num{1E5} leads to erratic force evolutions.
 These results are confirmed by high values of the ratio of the kinetic ($KE$) to the internal ($IE$) energies (it should not exceed a few \unit{\%} \cite{wang_Investigation_2011, ducobu_Introduction_2015}).
-A value of ${MS}_f$ of 1E3 is chosen as it offers a good balance between reducing the computation time and the impact on the forces, while keeping the $\frac{KE}{IE}$ below \qty{1}{\%}.
+A value of $\dnsp{MS}{f}$ of 1E3 is chosen as it offers a good balance between reducing the computation time and the impact on the forces, while keeping the $\frac{KE}{IE}$ below \qty{1}{\%}.
 To provide an order of magnitude of CPU computation time, between \qty{10}{\hour} and \qty{50}{\hour} (depending on the value of $h$) are required on 4 cores of an Intel i7-5700HQ CPU at \qtyrange{2.7}{3.5}{\GHz}.
@@
 \begin{center}
-\caption{\label{tab:MS} MS sensitivity study (selected MS factor, $MS_f$, in bold, $\hat{F_c}$: normalized cutting force, $\hat{F_f}$: normalized feed force, $KE$: kinetic energy, $IE$: internal energy)}
+\caption{\label{tab:MS} MS sensitivity study (selected MS factor, $\dnsp{MS}{f}$, in bold, $\hat{\snsp{F}{c}}$: normalized cutting force, $\hat{\snsp{F}{f}}$: normalized feed force, $KE$: kinetic energy, $IE$: internal energy)}
 \begin{tabular}{llllll}
 \hline\noalign{\smallskip}
-$MS_f$ & CPU scaling & Speed-up & $\hat{F_c}$ & $\hat{F_f}$ & $\frac{KE}{IE}$ (\unit{\%})\\
+$\dnsp{MS}{f}$ & CPU scaling & Speed-up & $\hat{\snsp{F}{c}}$ & $\hat{\snsp{F}{f}}$ & $\frac{KE}{IE}$ (\unit{\%})\\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 They show no influence on the numerical results for the forces compared to the built-in Johnson-Cook model, only the computation time is influenced by the number of neurons in the first hidden layer and increases with it.
+This increase in computation time is not only due to the increasing complexity of the neural network with the number of neurons, but also to the need to go through a VUHARD user subroutine.
 A first hidden layer of 9 neurons is therefore selected as it leads to the smallest increase in CPU computation time, without influence on the final result.
@@
 \caption{\label{tab:NbNeurons} Sensitivity of the forces to the number of neurons of the first layer, $\zeta$
-(selection in bold, $\check{F_c}$: normalized cutting force, $\check{F_f}$: normalized feed force)}
+(selection in bold, $\check{\snsp{F}{c}}$: normalized cutting force, $\check{\snsp{F}{f}}$: normalized feed force)}
 \begin{tabular}{llll}
 \hline\noalign{\smallskip}
-$\zeta$  & Time increase (\unit{\%}) & $\check{F_c}$ & $\check{F_f}$\\
+$\zeta$  & Time increase (\unit{\%}) & $\check{\snsp{F}{c}}$ & $\check{\snsp{F}{f}}$\\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 Then, a linear extrapolation (dashed line between the last two markers in Figure \ref{fig:ExpNum_Forces_v10_40µ_6}) is used to provide numerical values for the same time range as the experimental values.
-The mean and standard deviation ($2\,\sigma$) are calculated from the 3 experimental values.
-The resulting dispersion is shown in Figure \ref{fig:ExpNum_Forces_v10_40µ_6} around the mean values of each force.
+The average and standard deviation ($2\,\sigma$) are calculated from the 3 experimental values.
+The resulting dispersion is shown in Figure \ref{fig:ExpNum_Forces_v10_40µ_6} around the average values of each force.
 Steady state takes longer to be reached for the experiments than for the numerical model, in particular for the cutting force.
-The dispersion around the evolution of the mean force is greater for the feed force than for the cutting force, while the mean value of the feed force is \qty{46}{\%} of the mean value of the cutting force.
+The dispersion around the evolution of the average force is greater for the feed force than for the cutting force, while the average value of the feed force is \qty{46}{\%} of the average value of the cutting force.
 The numerical cutting force is very close to the experimental average cutting force; it is only \qty{4}{\%} higher.
@@
 The numerical passive force difference is also underestimated and is not within the narrowest experimental dispersion.
-The difference between the mean values of the experimental and numerical feed and passive forces is \qty{25}{\%}.
+The difference between the average values of the experimental and numerical feed and passive forces is \qty{25}{\%}.
 A less well modelled feed force than the cutting force is typical of FE models of the cutting process and the difference with the experimental value is similar to other studies for a narrower range of cutting conditions \cite{sima_Modified_2010, ducobu_Material_2016, karpat_Temperature_2011, zhang_Chip_2011,afrasiabi_NumericalExperimental_2021}.
@@
 \includegraphics[width = 140 mm]{Figures/ExpNum_Forces_v10_40µ_6}
-\caption{Temporal evolutions of experimental (E) and numerical (N) forces at $\lambda_s =$ \qty{6}{\degree}, $v_c =$ \qty{10}{\m\per\min} and $h =$ \qty{40}{\um} with dispersion around mean experimental values (linear extrapolation of numerical values in dashed)}
+\caption{Temporal evolutions of experimental (E) and numerical (N) forces at $\lambda_s =$ \qty{6}{\degree}, $v_c =$ \qty{10}{\m\per\min} and $h =$ \qty{40}{\um} with dispersion around average experimental values (linear extrapolation of numerical values in dashed)}
 \label{fig:ExpNum_Forces_v10_40µ_6}
@@
 When the inclination of the cutting edge is \qty{0}{\degree}, both sides of the chip are identical and a symmetry plane can be drawn in the middle of the workpiece (Figure \ref{fig:ChipsNumBack} (a)).
-On the other hand, for a slope of the cutting edge of \qty{6}{degree}, the chip is no longer aligned with the workpiece.
+On the other hand, for a slope of the cutting edge of \qty{6}{\degree}, the chip is no longer aligned with the workpiece.
 The chip bends to one side due to the orientation of the tool and symmetry is lost in both the geometry and the thermal and mechanical fields, as shown in figure \ref{fig:ChipsNumBack} (b).
-This produces helical chips for the inclination angle of \qty{6}{degree} as in the experiments.
+This produces helical chips for the inclination angle of \qty{6}{\degree} as in the experiments.
 Figure \ref{fig:ChipNumTop} shows the variation of the chip thickness across its width: it is thicker in the middle (i.e.
@@
 
-Mean values of the experimental forces and their dispersion are shown in Figures \ref{fig:Fx_0} to \ref{fig:Fz_6} together with the mean numerical values.
+Average values of the experimental forces and their dispersion are shown in Figures \ref{fig:Fx_0} to \ref{fig:Fz_6} together with the average numerical values.
 Passive force values are of course only plotted for $\lambda_s =$ \qty{6}{\degree} as they are equal to zero when $\lambda_s =$ \qty{0}{\degree}.
@@
 Increasing the inclination angle from \qty{0}{\degree} to \qty{6}{\degree} slightly reduces the cutting force; this is well captured by the model.
-For cutting speeds of \qtyrange{20}{40}{\m\per\min} and an inclination angle of \qty{0}{\degree}, $F_c$ is almost constant with cutting speed for uncut chip thicknesses of \qty{40}{\um} and \qty{60}{\um}, while it decreases slightly for \qty{80}{\um}; this small stabilization is less marked for the model.
+For cutting speeds of \qtyrange{20}{40}{\m\per\min} and an inclination angle of \qty{0}{\degree}, $\snsp{F}{c}$ is almost constant with cutting speed for uncut chip thicknesses of \qty{40}{\um} and \qty{60}{\um}, while it decreases slightly for \qty{80}{\um}; this small stabilization is less marked for the model.
 
-An increase in the deviation around the mean value with the cutting speed is noted for values above \qty{10}{\m\per\min}.
+An increase in the deviation around the average value with the cutting speed is noted for values above \qty{10}{\m\per\min}.
 All numerical values are within \qty{95}{\%} confidence of the experiments (35 of the 36 conditions are within \qty{68}{\%} confidence).
@@
 Figures \ref{fig:Fy_0} and \ref{fig:Fy_6} show the results for the feed force, where the two clearest trends for the experiments are its decrease with the inclination angle and its increase with the thickness of the uncut chip (even though it is lower than expected).
-For \qty{80}{\um}, $F_f$ decreases overall with $v_c$ in the experiments.
+For \qty{80}{\um}, $\snsp{F}{f}$ decreases overall with $v_c$ in the experiments.
 For \qty{40}{\um} and \qty{60}{\um}, the force decreases at lower $v_c$, then increases for \qty{0}{\degree}, while a decrease is observed at all $v_c$ for \qty{6}{\degree} (the experimental dispersion is high for both inclination angles, but the average trend with cutting speed is clear at \qty{6}{\degree}, not at \qty{0}{\degree}).
@@
 The numerical values are generally not within the \qty{95}{\%} confidence interval (they do not clearly change with the cutting conditions).
-Coupled with the differences in trends, this shows that $F_f$ is less well modelled (the average difference is \qty{39}{\%}) than $F_c$ as usual in FE modelling of the cutting process and even more so in 3D \cite{hardt_Three_2021}.
+Coupled with the differences in trends, this shows that $\snsp{F}{f}$ is less well modelled (the average difference is \qty{39}{\%}) than $\snsp{F}{c}$ as usual in FE modelling of the cutting process and even more so in 3D \cite{hardt_Three_2021}.
 The influence of the uncut chip thickness on the feed force should therefore be improved.
@@
 Like the cutting force, it increases with the thickness of the uncut chip and decreases with the cutting speed.
-The comparison with experiments is broadly the same as for $F_c$, except for a greater difference in the magnitude of $F_p$ (the average difference is \qty{26}{\%}, but it is small in absolute terms - less than \qty{5}{N}).
+The comparison with experiments is broadly the same as for $\snsp{F}{c}$, except for a greater difference in the magnitude of $\snsp{F}{p}$ (the average difference is \qty{26}{\%}, but it is small in absolute terms - less than \qty{5}{N}).
 Most of the numerical values do not fall within the experimental \qty{95}{\%} confidence interval.
@@
 As this selection was made with a 2D model, the results show the ability of the model to correctly handle the third (passive) force.
-Based on the mean differences, the performance of the model is very close for the cutting and feed forces for both inclinations of the cutting edge, although a small degradation (\qty{1}{\%} and \qty{2}{\%}, respectively) is noted for \qty{6}{\degree}.
+Based on the average differences, the performance of the model is very close for the cutting and feed forces for both inclinations of the cutting edge, although a small degradation (\qty{1}{\%} and \qty{2}{\%}, respectively) is noted for \qty{6}{\degree}.
 This degradation is more important (\qty{7}{\%}) for the chip thickness ratio and must be linked to the difference in passive force.
@@
 The difference is larger for the feed force than for the passive force, a trend opposite to that of Hardt and Bergs.
-The mean and range (min -- max) of the differences are larger for the forward force.
+The average and range (min -- max) of the differences are larger for the forward force.
 The smaller range of the passive force confirms a shift for all cutting conditions, similar to the results of Hardt and Bergs \cite{hardt_Three_2021}.
@@
 \begin{center}
-\caption{\label{tab:Synth} Synthetic quantitative overview of the results: differences between the experimental and the numerical results (mean difference for each cutting edge inclination, and maximal, minimal and mean differences for all the conditions) for the cutting force, $\Delta F_c$, the feed force, $\Delta F_f$, the passive force, $\Delta F_p$, and the chip thickness ratio, $\Delta \lambda_h$}
+\caption{\label{tab:Synth} Synthetic quantitative overview of the results: differences between the experimental and the numerical results (average difference for each cutting edge inclination, and maximal, minimal and average differences for all the conditions) for the cutting force, $\Delta \snsp{F}{c}$, the feed force, $\Delta \snsp{F}{f}$, the passive force, $\Delta \snsp{F}{p}$, and the chip thickness ratio, $\Delta \lambda_h$}
 \begin{tabular}{lllll}
 \hline\noalign{\smallskip}
-Difference & $\Delta F_c$ (\unit{\%}) & $\Delta F_f$ (\unit{\%}) & $\Delta F_p$ (\unit{\%}) & $\Delta \lambda_h$ (\unit{\%})\\
+Difference & $\Delta \snsp{F}{c}$ (\unit{\%}) & $\Delta \snsp{F}{f}$ (\unit{\%}) & $\Delta \snsp{F}{p}$ (\unit{\%}) & $\Delta \lambda_h$ (\unit{\%})\\
 \hline\noalign{\smallskip}
-Mean $\lambda_s =$ \qty{0}{\degree} & 3 & 38 & -- & 14\\
-Mean $\lambda_s =$ \qty{6}{\degree} & 4 & 40 & 26 & 21\\
+Average $\lambda_s =$ \qty{0}{\degree} & 3 & 38 & -- & 14\\
+Average $\lambda_s =$ \qty{6}{\degree} & 4 & 40 & 26 & 21\\
 Max global & 10 & 60 & 29 & 38\\
 Min global & 1 & 10 & 19 & 2\\
-Mean global & 4 & 39 & 26 & 17\\
+Average global & 4 & 39 & 26 & 17\\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 The numerical model is then able to better reproduce the real behaviour of the material and to take into account thermomechanical transformations which are sources of non-linearities, difficult to take into account with an analytical flow law model.
-Current work, in the LGP, on the behaviour of a modified carbon alloy AISI P20 shows the advantages of this approach compared to models in the literature such as Johnson-Cook, Zerilli-Armstrong \cite{Muralli-2017-Performance} or Hansel-Spittel \cite{chadha2018approach}.
+Current work, using a Gleeble thermomechanical simulator, on the behaviour of a modified carbon alloy AISI P20 shows the advantages of this approach compared to models in the literature such as Johnson-Cook, Zerilli-Armstrong \cite{Muralli-2017-Performance} or Hansel-Spittel \cite{chadha2018approach}, insofar as one is then able to better reproduce more complex material behaviour.
   \item The cutting force is the best modelled quantity with an average difference of \qty{4}{\%} with the experiments.

### 2022-10-18 Article.tex
Small update of all article

@@
 Modelling of the cutting process needs to move from 2D to 3D configurations to get closer to industrial applications.
-This study introduces a predictive 3D finite element model of free orthogonal and oblique cutting with an ANN-based material flow law and experimental validation in strictly the same conditions (cutting and geometrical).
+This study introduces a predictive 3D finite element model of free orthogonal and oblique cutting with an Artificial Neural Network (ANN)-based material flow law and experimental validation in strictly the same conditions (cutting and geometrical).
 The flow law based on a neural network allows simulating the cutting process based on data coming from the material characterization tests without requiring any postulate concerning the expression of the flow law.
@@
 No significant degradation of the results is brought by the apparition of the third, out-of-plane, force, which shows the ability of the model to handle orthogonal and oblique cutting configurations.
-
-\FD{Add a comment on ANN?}
-\OP{A new sentence has been introduced in the abstract}
 
@@
 This paper fills the gap in the oblique cutting literature by investigating both orthogonal and free oblique 3D cutting configurations, both experimentally and numerically.
-An artificial neural network (ANN), introduced in Pantalé et al.
+An Artificial Neural Network (ANN), introduced in Pantalé et al.
 \cite{pantale_Efficient_2022}, is implemented in a FE cutting model for the first time in place of the JC analytical law.
@@
 This type of model is intended to support future choices and developments without the need for experimental data.
-No assumptions are made about the geometry of the workpiece in the model (i.e.
-its width is the same as in experiments), while keeping the calculation time relevant for industrial applications.
+No assumptions are made about the geometry of the workpiece in the model (i.e., its width is the same as in experiments), while keeping the calculation time relevant for industrial applications.
 The developments are applied to the formation of continuous chips of the titanium alloy Ti6Al4V.
@@
 The top of the sample has 3 ribs of \qty{1}{\mm} width (the width of the tool is \qty{6}{\mm}) and \qty{10}{\mm} length.
-The test consists of removing the top layer (its height is the thickness of the uncut chip, $h$) of a rib at the prescribed cutting speed, $v_c$.
+The test consists of removing the top layer (its height is the uncut chip thickness, $h$) of a rib at the prescribed cutting speed, $v_c$.
 The cutting speed is provided by the feed rate, $v_f$, of the machine (maximum value of \qty{40}{\metre\per\min}).
-The inclination of the cutting edge of the tool, $\lambda_s$, results from the relative angular orientation of the tool and the sample.
+The tool cutting edge inclination, $\lambda_s$, results from the relative angular orientation of the tool and the sample.
 Table \ref{tab:CutCond} shows the cutting conditions: 6 cutting speeds, 3 uncut chip thicknesses and 2 inclination angles, each repeated 3 times.
@@
 
-The CEL formulation is adopted to model the dry orthogonal and oblique cutting tests with Abaqus/Explicit 2020.
-The 3D model is composed of a fixed Lagrangian tool and an Eulerian part (Figure \ref{fig:BC}).
+The CEL formulation is adopted to model the dry orthogonal and free oblique cutting tests with Abaqus/Explicit 2020.
+The 3D model is composed of a fixed Lagrangian tool and a Eulerian part (Figure \ref{fig:BC}).
 Chip formation occurs by plastic flow through the Eulerian domain without mesh distortion.
@@
 
-As shown in Figure \ref{fig:FEConfig}, the full width of the workpiece (\qty{1}{\mm}), i.e.
-one rib in the experiments, is modelled.
+As shown in Figure \ref{fig:FEConfig}, the full width of the workpiece (\qty{1}{\mm}), i.e., one rib in the experiments, is modelled.
 To allow for chip formation and lateral flow, the Eulerian domain is wider (it includes the volume in which the material can move).
@@
 
-According to a previous sensitivity study of the mesh in orthogonal section with the CEL formulation \cite{ducobu_Finite_2017}, the edge size of the elements is \qty{5}{\um} in the plane parallel to the cutting velocity.
-In the direction perpendicular to this plane, it is \qty{5}{\um} in the areas close to the lateral limits of the Eulerian domain and \qty{50}{\um} in the middle of the part.
+According to a previous sensitivity study of the mesh in orthogonal cutting with the CEL formulation \cite{ducobu_Finite_2017}, the edge size of the elements is \qty{5}{\um} in the plane parallel to the cutting speed.
+In the direction perpendicular to this plane, it is \qty{5}{\um} in the areas close to the lateral boundaries of the Eulerian domain and \qty{50}{\um} in the middle of the part.
 To reduce the computation time, the size of the model depends on the value of the uncut chip thickness.
-This results in an Eulerian domain (EC3D8RT 8-node 3D linear Eulerian elements, coupled mechanical-thermal behaviour and reduced integration) composed of \num{216550} to \num{273350} nodes and a Lagrangian domain (C3D8T 8-node 3D linear Lagrangian elements, coupled mechanical-thermal behaviour) of \num{4650} nodes.
+This results in a Eulerian domain (EC3D8RT 8-node 3D linear Eulerian elements, coupled mechanical-thermal behaviour and reduced integration) composed of \num{216550} to \num{273350} nodes and a Lagrangian domain (C3D8T 8-node 3D linear Lagrangian elements, coupled mechanical-thermal behaviour) of \num{4650} nodes.
 
 The Ti6Al4V part is assumed to be thermo-elasto-viscoplastic (isotropic) and the inelastic thermal fraction is 0.9.
-The JC parameter set of Seo et al.
+The JC parameters set of Seo et al.
 \cite{seo_Constitutive_2005} is adopted because the value of $A$ corresponds to the value of the typical yield strength of Ti6Al4V and this set was found to provide the best results among the 20 sets available in the literature \cite{ducobu_Importance_2017}.
@@
 According to the experimental results of Rech et al.
-\cite{rech_Characterisation_2013}, it is assumed that Coulomb friction occurs at the tool-piece interface and that the coefficients of friction, $\mu$, and heat sharing, $\beta$, depend on the cutting speed.
+\cite{rech_Characterisation_2013}, it is assumed that Coulomb friction occurs at the tool-piece interface and that the coefficients of friction, $\mu$, and heat partition, $\beta$, depend on the cutting speed.
 The limiting shear stress, $\tau_{\text{max}}$, is included and is given by:
-
+%
 \begin{equation}
@@
 \end{equation}
-
+%
 All the friction energy is converted into heat. Table \ref{tab:fricHeat} shows the friction coefficients adopted in this study.
@@
 \subsection{Material constitutive model of Ti6Al4V}
-\OP{This section has been enhanced and completed}
 
@@
 
-\FD{Inclure dans corps du texte puisque article normal et rq reviewer?}
-
-\OP{I think it should still be enough as we put a complete set in the appendix, no need to put everything concerning all networds (see final remark in Appendix)}
-
 \subsection{Sensitivity study of the results to mass scaling}
@@
 Mass scaling (MS) is introduced into the model to reduce the CPU computation time while checking that it does not influence the results (forces and energies) via a mass scaling sensitivity study.
-MS factors, $\dnsp{MS}{f}$, ranging from \num{1E6} (theoretical CPU time scale of $\sqrt{\dnsp{MS}{f}} = \num{1000}$) to 1 (no scale) were used for a cut condition ($\lambda_s$ = \qty{0}{\degree}, $v_c$ = \qty{30}{\m\per\min} and $h$ = \qty{60}{\um}).
+MS factors, $\dnsp{MS}{f}$, ranging from \num{1E6} (theoretical CPU time scale of $\sqrt{\dnsp{MS}{f}} = \num{1000}$) to 1 (no scale) were used for a cutting condition ($\lambda_s$ = \qty{0}{\degree}, $v_c$ = \qty{30}{\m\per\min} and $h$ = \qty{60}{\um}).
 The same signal processing procedure is applied to the numerical forces as to the experimental forces (cf.
-\ref{ExpSet}): they are filtered with a second order low-pass Bessel filter at \qty{750}{\Hz} before calculating the steady state average value.
+\ref{ExpSet}): they are filtered with a second-order low-pass Bessel filter at \qty{750}{\Hz} before calculating the steady state average value.
 Table \ref{tab:MS} gives the results of the model with MS normalized ($\hat{F_i}$) by those of the model without MS:
@@
 with $i = c$ for the cutting force and $i = f$ for the feed force.
-As expected, the real speed does not increase linearly with the $\dnsp{MS}{f}$, but it remains significant.
+As expected, the real speed-up does not increase linearly with the $\dnsp{MS}{f}$, but it remains significant.
 A $\dnsp{MS}{f}$ of \num{1E6} leads to an unstable computation and a $\dnsp{MS}{f}$ of \num{1E5} leads to erratic force evolutions.
@@
 The results of the study are provided in Table \ref{tab:NbNeurons}.
-The $\check{F_i}$ corresponds to the results of the model with ANN normalized by those of the model with the built-in JC model:
+$\check{F_i}$ corresponds to the results of the model with ANN normalized by those of the model with the built-in JC model:
 
@@
 
-An example of the time evolution of the numerical and experimental forces is plotted for the 3 directions in Figure \ref{fig:ExpNum_Forces_v10_40µ_6} at $\lambda_s =$ \qty{6}{\degree}, $v_c =$ \qty{10}{\m\per\min} and $h =$ \qty{40}{\m\per\min}.
+An example of the temporal evolution of the numerical and experimental forces is plotted for the 3 directions in Figure \ref{fig:ExpNum_Forces_v10_40µ_6} at $\lambda_s =$ \qty{6}{\degree}, $v_c =$ \qty{10}{\m\per\min} and $h =$ \qty{40}{\m\per\min}.
 The FE models are calculated up to a few microseconds after the stationary state is reached.
@@
 The numerical feed force is underestimated by the model, but is within the \qty{95}{\%} experimental confidence interval.
-The numerical passive force difference is also underestimated and is not within the narrowest experimental dispersion.
+The numerical passive force difference is also underestimated and is not within the narrower experimental dispersion.
 The difference between the average values of the experimental and numerical feed and passive forces is \qty{25}{\%}.
@@
 When the inclination of the cutting edge is \qty{0}{\degree}, both sides of the chip are identical and a symmetry plane can be drawn in the middle of the workpiece (Figure \ref{fig:ChipsNumBack} (a)).
-On the other hand, for a slope of the cutting edge of \qty{6}{\degree}, the chip is no longer aligned with the workpiece.
+On the other hand, for an inclination of the cutting edge of \qty{6}{\degree}, the chip is no longer aligned with the workpiece.
 The chip bends to one side due to the orientation of the tool and symmetry is lost in both the geometry and the thermal and mechanical fields, as shown in figure \ref{fig:ChipsNumBack} (b).
 This produces helical chips for the inclination angle of \qty{6}{\degree} as in the experiments.
-Figure \ref{fig:ChipNumTop} shows the variation of the chip thickness across its width: it is thicker in the middle (i.e.
-the body of the chip) than on its sides.
+Figure \ref{fig:ChipNumTop} shows the variation of the chip thickness across its width: it is thicker in the middle (i.e., the body of the chip) than on its sides.
 This underlines the importance of 3D modelling, even for the orthogonal cutting configuration as highlighted earlier \cite{ducobu_Finite_2017}.
@@
 
-Figures \ref{fig:Fy_0} and \ref{fig:Fy_6} show the results for the feed force, where the two clearest trends for the experiments are its decrease with the inclination angle and its increase with the thickness of the uncut chip (even though it is lower than expected).
+Figures \ref{fig:Fy_0} and \ref{fig:Fy_6} show the results for the feed force, where the two clearest trends for the experiments are its decrease with the inclination angle and its increase with the uncut chip thickness (even though it is lower than expected).
 For \qty{80}{\um}, $\snsp{F}{f}$ decreases overall with $v_c$ in the experiments.
@@
 It should be noted that the numerical model does not correctly handle the trends of the feed forces: as Figure \ref{fig:Fy_6} clearly shows, the numerical forces have an overall increasing trend with the cutting speed, while their average value mainly decreases when the uncut chip thickness increases.
-The differences between the average numerical and experimental values increase with the thickness of the uncut chip: the forces are closer at \qty{40}{\um} than at \qty{80}{\um}.
+The differences between the average numerical and experimental values increase with the uncut chip thickness: the forces are closer at \qty{40}{\um} than at \qty{80}{\um}.
 The numerical values are generally not within the \qty{95}{\%} confidence interval (they do not clearly change with the cutting conditions).
@@
 The passive force is non-zero for the inclination angle of \qty{6}{\degree} (Figure \ref{fig:Fz_6}).
-Like the cutting force, it increases with the thickness of the uncut chip and decreases with the cutting speed.
-The comparison with experiments is broadly the same as for $\snsp{F}{c}$, except for a greater difference in the magnitude of $\snsp{F}{p}$ (the average difference is \qty{26}{\%}, but it is small in absolute terms - less than \qty{5}{N}).
+Like the cutting force, it increases with the uncut chip thickness and decreases with the cutting speed.
+The comparison with experiments is broadly the same as for $\snsp{F}{c}$, except for a greater difference in the magnitude of $\snsp{F}{p}$ (the average difference is \qty{26}{\%}, but it is small in absolute terms -- less than \qty{5}{N}).
 Most of the numerical values do not fall within the experimental \qty{95}{\%} confidence interval.
@@
 %
-with $h$ the thickness of the uncut chip and $h'$ the thickness of the chip, is almost independent of the thickness of the uncut chip (Figures \ref{fig:h0} and \ref{fig:h6}).
-It is slightly reduced from $\lambda_s =$ \qty{0}{\degree} to $\lambda_s =$ \qty{6}{\degree}, which means that the chip thickness decreases with the angle of inclination.
+with $h$ the uncut chip thickness and $h'$ the chip thickness, is almost independent of the uncut chip thickness (Figures \ref{fig:h0} and \ref{fig:h6}).
+It is slightly reduced from $\lambda_s =$ \qty{0}{\degree} to $\lambda_s =$ \qty{6}{\degree}, which means that the chip thickness decreases with the inclination angle.
 This influence is underestimated by the model: the reduction of $\lambda_h$ is smaller than in the experiments.
@@
 
-The differences calculated according to the equation \ref{eq:diff} are presented in Table \ref{tab:Synth} to provide a quantitative overview of the results.
+The differences calculated according to the equation (\ref{eq:diff}) are presented in Table \ref{tab:Synth} to provide a quantitative overview of the results.
 The cutting force is the best modelled quantity as observed in the literature.
@@
 As this selection was made with a 2D model, the results show the ability of the model to correctly handle the third (passive) force.
-Based on the average differences, the performance of the model is very close for the cutting and feed forces for both inclinations of the cutting edge, although a small degradation (\qty{1}{\%} and \qty{2}{\%}, respectively) is noted for \qty{6}{\degree}.
+Based on the average differences, the performance of the model is very close for the cutting and feed forces for both cutting edge inclinations, although a small degradation (\qty{1}{\%} and \qty{2}{\%}, respectively) is noted for \qty{6}{\degree}.
 This degradation is more important (\qty{7}{\%}) for the chip thickness ratio and must be linked to the difference in passive force.
@@
 It should be noted that the chip thickness is very well modelled under certain cutting conditions with a minimum difference of \qty{2}{\%}.
-The difference is larger for the feed force than for the passive force, a trend opposite to that of Hardt and Bergs.
-The average and range (min -- max) of the differences are larger for the forward force.
+The difference is larger for the feed force than for the passive force, a trend opposite to that of Hardt and Bergs \cite{hardt_Three_2021}.
+The average and range (min -- max) of the differences are larger for the feed force.
 The smaller range of the passive force confirms a shift for all cutting conditions, similar to the results of Hardt and Bergs \cite{hardt_Three_2021}.
@@
 Average $\lambda_s =$ \qty{6}{\degree} & 4 & 40 & 26 & 21\\
-Max global & 10 & 60 & 29 & 38\\
-Min global & 1 & 10 & 19 & 2\\
+Max. global & 10 & 60 & 29 & 38\\
+Min. global & 1 & 10 & 19 & 2\\
 Average global & 4 & 39 & 26 & 17\\
@@
 \begin{itemize}
-  \item The experimental study was carried out with the same set-up in free orthogonal and free oblique cuts for the titanium alloy Ti6Al4V (the only change is the inclination of the cutting edge).
+  \item The experimental study was carried out with the same set-up in free orthogonal and free oblique cutting for the titanium alloy Ti6Al4V (the only change is the cutting edge inclination).
 This is a reference to evaluate the performance of the FE 3D model introducing an ANN-based constitutive model developed under the same conditions.
-A wide range of novel cutting conditions, 36, is considered, including 2 cutting edge inclinations.
+An unpreviously seen wide range of cutting conditions, 36, is considered, including 2 cutting edge inclinations.
   \item A major novelty of this work is the accurate evaluation of the fundamental variables and their trends in 3D, without the need to adjust the numerical parameters and the model characteristics when the cutting conditions and the inclination angle are changed significantly.
@@
 The numerical model is then able to better reproduce the real behaviour of the material and to take into account thermomechanical transformations which are sources of non-linearities, difficult to take into account with an analytical flow law model.
-Current work, using a Gleeble thermomechanical simulator, on the behaviour of a modified carbon alloy AISI P20 shows the advantages of this approach compared to models in the literature such as Johnson-Cook, Zerilli-Armstrong \cite{Muralli-2017-Performance} or Hansel-Spittel \cite{chadha2018approach}, insofar as one is then able to better reproduce more complex material behaviour.
+Current work, using a Gleeble thermomechanical simulator, on the behaviour of a modified carbon alloy AISI P20 shows the advantages of this approach compared to models in the literature such as Johnson-Cook, Zerilli-Armstrong \cite{Muralli-2017-Performance} or Hansel-Spittel \cite{chadha2018approach}, insofar as one is then able to better reproduce more complex material behaviours.
   \item The cutting force is the best modelled quantity with an average difference of \qty{4}{\%} with the experiments.
@@
 Conforming to \cite{pantale_Efficient_2022}, this one is referred ANN-3-9-7-1-sig.
-The training of the neural network was performed using a dataset containing \num{3430} data points defined by :
+The training of the neural network was performed using a dataset containing \num{3430} data points defined by:
 \begin{itemize}

### 2023-11-22 Article.tex
Version soumise à EAAI
Journal et titre mis à jour

@@
 
-\journal{CIRP Journal of Manufacturing Science and Technology}
+\journal{Engineering Applications of Artificial Intelligence}
 
@@
 
-\title{Predictive 3D modelling of free oblique cutting with an ANN-based material constitutive model and experimental validation over a wide range of conditions}
+\title{Predictive 3D modelling of free oblique cutting with an Artificial Neural Network (ANN)-based material constitutive model and experimental validation over a wide range of conditions}
 

### 2023-11-24 Article.tex
Update of text after EAAI rejection

--- 2022-10-18 Article.tex
@@
 
-\journal{CIRP Journal of Manufacturing Science and Technology}
+\journal{Journal}
 
@@
 
-\title{Predictive 3D modelling of free oblique cutting with an ANN-based material constitutive model and experimental validation over a wide range of conditions}
+\title{Predictive 3D modelling of free oblique cutting introducing an ANN-based material flow law with experimental validation over a wide range of conditions}
 
@@
 
-Oblique cutting \sep Finite element method (FEM) \sep Predictive model \sep Artificial Neural Network (ANN)
+Oblique cutting \sep Finite element method (FEM) \sep Predictive model \sep Artificial Neural Network (ANN) \sep Material flow law
 
@@
 
-Selection of the tools and the cutting conditions in machining, but also comprehension of the influence of the process parameters on the quality of a component and its optimization, are still difficult to achieve because of the high level of complexity and the related nonlinear phenomena.
+Selection of the tools and the cutting conditions in machining are still difficult to achieve because of the high level of complexity and the related nonlinear phenomena.
+Comprehension of the influence of the process parameters on the quality of a component and its optimization are also a challenge for the same reasons.
 In the frame of digital manufacturing and Industry 4.0, modelling the cutting process supports them, while remaining a challenging task.
@@
 \cite{arrazola_Recent_2013}, most finite element (FE) models are developed in 2D (orthogonal cutting configuration usually) although industrial applications require 3D modelling.
-
-Experimental validation of a model is a crucial step in modelling the cutting process.
-The experimental configuration should be as close as possible to the simulation.
-For the validation of orthogonal cutting, a rotational motion usually generates the cutting speed.
-This is often done in turning \cite{agmell_Development_2018} or milling \cite{xu_Simulation_2021} and the diameter of the rotating workpiece must be large enough to reduce the influence of curvature on the results.
-Experimental configurations under strictly orthogonal cutting conditions are less often adopted, for example on broaching machines \cite{abouridouane_Friction_2021} or milling machines \cite{ducobu_Experimental_2015, sela_Measurement_2021}.
-If they remove the assumptions related to the rotary cutting motion, they generally allow lower cutting speeds (except on a dedicated machine, as in Afrasiabi et al.
-\cite{afrasiabi_NumericalExperimental_2021}).
-Free oblique cutting with a straight cutting edge has not yet been studied: all efforts have been concentrated on orthogonal cutting (mainly for 2D validation).
-
-Lagrangian and Eulerian formulations are the most used for FE modelling of the cutting process.
-Combinations of formulations, such as Arbitrary Lagrangian-Eulerian (ALE) and Coupled Eulerian-Lagrangian (CEL), are increasingly being used to avoid (or reduce) mesh distortions \cite{ducobu_Application_2016}.
-The CEL formulation has recently been successfully applied to the modelling of cutting (2D orthogonal configuration): it provides accurate results with realistic chip shape and no mesh distortion.
-The first 3D applications are found in recent works \cite{xu_Simulation_2021, ducobu_Finite_2017, ambrosio_New_2022, vovk_Finite_2020, hardt_Three_2021}.
-They cover orthogonal (free) cutting or a simple 3D operation, while free oblique cutting has yet to be studied.
 
@@
 One of the points in favour of its adoption is the rather limited number of parameters to be identified, 5: $A$, $B$, $C$, $m$ and $n$.
-Here, $\mdot{\varepsilon}_0^p$ is the reference plastic strain rate, while $T_{\text{room}}$ and $T_{\text{melt}}$ are respectively the ambient (room) and melting temperature.
+Here, $\mdot{\varepsilon}_0^p$ is the reference plastic strain rate, while $T_{\text{room}}$ and $T_{\text{melt}}$ are respectively the ambient (room) and melting temperatures.
 More recent models developed on this basis, such as that of Calamaz et al.
@@
 They identified simultaneously the parameters of the material constitutive model and the friction model for Ti6Al4V.
+The identified parameters showed good performance when applied to a different FE model \cite{ducobu_Application_2023}.
 Most of these works highlight the non-uniqueness of the identification and they all require the definition of the analytical expression of the constitutive model.
 
+ANN (Artificial Neural Network)-based material models have been introduced to avoid postulating or knowing the analytical expression of the material behaviour.
+Gorji et al \cite{gorji_Potential_2020} recently reviewed the use of recurrent neural networks for material models, while Jamli and Farid \cite{jamli_Sustainability_2019} reviewed their application in FE simulation of material forming.
+When compared to classical analytical and emprirical models, such as JC model, they proved to be more powerful to represent the experimental behaviour \cite{tizemha_Interpolation_2023}.
+Use of these ANN-based models in FE simulation of forming processes also turned out to provide better results than the classical JC model \cite{pantale_Development_2023} and to handle complex phenomena such as dynamic recrystallisation \cite{tizemha_Artificial_2023}.
+No application of these ANN-based models in FE simulation of cutting currently exists.
+
+Lagrangian and Eulerian formulations are the most used for FE modelling of the cutting process.
+Combinations of formulations, such as Arbitrary Lagrangian-Eulerian (ALE) and Coupled Eulerian-Lagrangian (CEL), are increasingly being used to avoid (or reduce) mesh distortions \cite{ducobu_Application_2016}.
+The CEL formulation has recently been successfully applied to the modelling of cutting (in 2D orthogonal configuration): it provides accurate results with realistic chip shape and no mesh distortion.
+The first 3D applications are found in recent works \cite{xu_Simulation_2021, ducobu_Finite_2017, ambrosio_New_2022, vovk_Finite_2020, hardt_Three_2021}.
+They cover orthogonal (free) cutting or a simple 3D operation, while free oblique cutting has yet to be studied.
+
+Experimental validation of a model is a crucial step in modelling the cutting process.
+The experimental configuration should be as close as possible to the simulation.
+For the validation of orthogonal cutting, a rotational motion usually generates the cutting speed.
+This is often done in turning \cite{agmell_Development_2018} or milling \cite{xu_Simulation_2021} and the diameter of the rotating workpiece must be large enough to reduce the influence of curvature on the results.
+Experimental configurations under strictly orthogonal cutting conditions are less often adopted, for example on broaching machines \cite{abouridouane_Friction_2021} or milling machines \cite{ducobu_Experimental_2015, sela_Measurement_2021}.
+If they remove the assumptions related to the rotary cutting motion, they generally allow lower cutting speeds (except on a dedicated machine, as in Afrasiabi et al.
+\cite{afrasiabi_NumericalExperimental_2021}).
+Free oblique cutting with a straight cutting edge has not yet been studied: all efforts have been concentrated on orthogonal cutting (mainly for validation of 2D FE models).
+
 This paper fills the gap in the oblique cutting literature by investigating both orthogonal and free oblique 3D cutting configurations, both experimentally and numerically.
-An Artificial Neural Network (ANN), introduced in Pantalé et al.
+An ANN, introduced in Pantalé et al.
 \cite{pantale_Efficient_2022}, is implemented in a FE cutting model for the first time in place of the JC analytical law.
 A wide range of cutting speeds (6), uncut chip thicknesses (3) and cutting edge inclination angles (2) resulting in 36 different conditions are considered to demonstrate the predictive capability of the FE model for the fundamental variables.
-The main objectives of a predictive model are the accurate modelling of trends in results as conditions change and the good agreement of predicted values with experimental values (exact values are not sought due to experimental dispersions).
-This type of model is intended to support future choices and developments without the need for experimental data.
-No assumptions are made about the geometry of the workpiece in the model (i.e., its width is the same as in experiments), while keeping the calculation time relevant for industrial applications.
 The developments are applied to the formation of continuous chips of the titanium alloy Ti6Al4V.
@@
 
+The main objectives of a predictive model are the accurate modelling of trends in results as conditions change and the good agreement of predicted values with experimental values (exact values are not expected due to experimental dispersions of at least \qty{10}{\%} around the mean values).
+This type of model is intended to support future choices and developments without the need for experimental data.
+No assumptions are made about the geometry of the workpiece in the model (i.e., its width is the same as in experiments), while keeping the calculation time relevant for industrial applications.
 The CEL formulation is adopted to model the dry orthogonal and free oblique cutting tests with Abaqus/Explicit 2020.
@@
 \cite{seo_Constitutive_2005} is adopted because the value of $A$ corresponds to the value of the typical yield strength of Ti6Al4V and this set was found to provide the best results among the 20 sets available in the literature \cite{ducobu_Importance_2017}.
-The TiN coated tungsten carbide tool is assumed to have linear elasticity.
+The TiN coated tungsten carbide (WC) tool is assumed to have linear elasticity.
 The material properties are given in Table \ref{tab:prop}.
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-JC constitutive model & $A$ (\unit{\MPa}) & 997.9\\
+JC flow stress & $A$ (\unit{\MPa}) & 997.9\\
  & $B$ (\unit{\MPa}) & 653.1\\
@@
 
-\subsection{Material constitutive model of Ti6Al4V}
+\subsection{Material model of Ti6Al4V}
 
-The constitutive model of the Ti6Al4V material used in all the numerical simulations proposed in the section \ref{sec:ExpNumResults} is a thermo-elasto-viscoplastic law using a flow criterion based on an Artificial Neural Network (ANN) identified for the chosen material and implemented in the Abaqus/Explicit code via a Fortran subroutine VUHARD as proposed by Pantalé et al.
+The material model of Ti6Al4V used in all the numerical simulations proposed in the section \ref{sec:ExpNumResults} is a thermo-elasto-viscoplastic law using a flow criterion based on an Artificial Neural Network (ANN) identified for the chosen material and implemented in the Abaqus/Explicit code via a Fortran subroutine VUHARD as proposed by Pantalé et al.
 in \cite{pantale_Efficient_2022}.
@@
 The influence of the uncut chip thickness on the feed force should therefore be improved.
-The parameters of the material constitutive model are known to have an impact on the forces (and on the chip morphology) \cite{ducobu_Importance_2017,kugalurpalanisamy_Identification_2022}.
+The parameters of the material model are known to have an impact on the forces (and on the chip morphology) \cite{ducobu_Importance_2017,kugalurpalanisamy_Identification_2022}.
 The friction model should also be improved to strengthen the results \cite{hardt_Three_2021}.
@@
 A lower magnitude of the passive force from the simulation than from the experiments with the correct trends when the cutting conditions change was also observed by Hardt and Bergs \cite{hardt_Three_2021}.
-The differences were mainly attributed to differences in cutting edge radius, friction modelling and material constitutive model.
+The differences were mainly attributed to differences in cutting edge radius, friction modelling and material model.
 In this work, the impact of the cutting edge radius can be neglected as it is the same in the model as in the experiments.
@@
 The cutting force is the best modelled quantity as observed in the literature.
-This result was to be expected as the parameter set of the constitutive model was selected mainly due to its good approximation of the cutting force \cite{ducobu_Importance_2017}.
+This result was to be expected as the parameter set of the material model was selected mainly due to its good approximation of the cutting force \cite{ducobu_Importance_2017}.
 As this selection was made with a 2D model, the results show the ability of the model to correctly handle the third (passive) force.
@@
 
-An experimental and numerical study of the orthogonal and oblique free cutting of Ti6Al4V was carried out for a wide range of cutting conditions using an ANN-based material constitutive model.
+An experimental and numerical study of the orthogonal and oblique free cutting of Ti6Al4V was carried out for a wide range of cutting conditions using an ANN-based flow law.
 The following main conclusions are drawn:
@@
   \item The experimental study was carried out with the same set-up in free orthogonal and free oblique cutting for the titanium alloy Ti6Al4V (the only change is the cutting edge inclination).
-This is a reference to evaluate the performance of the FE 3D model introducing an ANN-based constitutive model developed under the same conditions.
+This is a reference to evaluate the performance of the FE 3D model introducing an ANN-based flow law developed under the same conditions.
 An unpreviously seen wide range of cutting conditions, 36, is considered, including 2 cutting edge inclinations.

### 2023-11-27 Article.tex
Update figures

@@
 \cite{calamaz_New_2008}, increase this number of parameters (for the particular Calamaz model to 9).
-Other authors have also used Zerilli-Armstrong model to simulate cutting processes \cite{Muralli-2017-Performance}.
+Other authors have also used Zerilli-Armstrong model to simulate cutting processes \cite{gurusamy_Performance_2017}.
 The best description (in theory) of the behaviour is obtained at the cost of a greater complexity of the identification process and a reduction of the link with the physical meaning of the model.
@@
 \includegraphics[width = 140 mm]{Figures/FEConfig}
-\caption{Configuration of the FE model for $\lambda_s$ = \qty{6}{\degree}}
+\caption{Configuration of the FE model for $\lambda_s =$~\qty{6}{\degree}}
 \label{fig:FEConfig}
@@
 In order to verify the influence of the neural network complexity on the numerical results of the simulation and on the computation time, several ANN architectures are tested afterwards (in \ref{subsec:nberneu}).
-The chosen global architecture has 2 hidden layers with a variable number of neurons for the first hidden layer ($\zeta$ = 9 to 17) and 7 neurons for the second hidden layer, 3 inputs (the plastic strain, $\varepsilon^p$, the plastic strain rate, $\mdot{\varepsilon}^p$, and the temperature, $T$) and one output (the yield strength, $\sigma^y$).
+The chosen global architecture has 2 hidden layers with a variable number of neurons for the first hidden layer ($\zeta$~=~9 to 17) and 7 neurons for the second hidden layer, 3 inputs (the plastic strain, $\varepsilon^p$, the plastic strain rate, $\mdot{\varepsilon}^p$, and the temperature, $T$) and one output (the yield strength, $\sigma^y$).
 The global architecture of this type of ANN is given in Figure \ref{fig:ANN} for 9 neurons in the first hidden layer.
@@
 Mass scaling (MS) is introduced into the model to reduce the CPU computation time while checking that it does not influence the results (forces and energies) via a mass scaling sensitivity study.
-MS factors, $\dnsp{MS}{f}$, ranging from \num{1E6} (theoretical CPU time scale of $\sqrt{\dnsp{MS}{f}} = \num{1000}$) to 1 (no scale) were used for a cutting condition ($\lambda_s$ = \qty{0}{\degree}, $v_c$ = \qty{30}{\m\per\min} and $h$ = \qty{60}{\um}).
+MS factors, $\dnsp{MS}{f}$, ranging from \num{1E6} (theoretical CPU time scale of $\sqrt{\dnsp{MS}{f}} = \num{1000}$) to 1 (no scale) were used for a cutting condition ($\lambda_s$~=~\qty{0}{\degree}, $v_c$~=~\qty{30}{\m\per\min} and $h$~=~\qty{60}{\um}).
 The same signal processing procedure is applied to the numerical forces as to the experimental forces (cf.
@@
 
-An example of the temporal evolution of the numerical and experimental forces is plotted for the 3 directions in Figure \ref{fig:ExpNum_Forces_v10_40µ_6} at $\lambda_s =$ \qty{6}{\degree}, $v_c =$ \qty{10}{\m\per\min} and $h =$ \qty{40}{\m\per\min}.
+An example of the temporal evolution of the numerical and experimental forces is plotted for the 3 directions in Figure \ref{fig:ExpNum_Forces_v10_40µ_6} at $\lambda_s =$~\qty{6}{\degree}, $v_c =$~\qty{10}{\m\per\min} and $h =$~\qty{40}{\m\per\min}.
 The FE models are calculated up to a few microseconds after the stationary state is reached.
@@
 \includegraphics[width = 140 mm]{Figures/ExpNum_Forces_v10_40µ_6}
-\caption{Temporal evolutions of experimental (E) and numerical (N) forces at $\lambda_s =$ \qty{6}{\degree}, $v_c =$ \qty{10}{\m\per\min} and $h =$ \qty{40}{\um} with dispersion around average experimental values (linear extrapolation of numerical values in dashed)}
+\caption{Temporal evolutions of experimental (E) and numerical (N) forces at $\lambda_s =$~\qty{6}{\degree}, $v_c =$~\qty{10}{\m\per\min} and $h =$~\qty{40}{\um} with dispersion around average experimental values (linear extrapolation of numerical values in dashed)}
 \label{fig:ExpNum_Forces_v10_40µ_6}
@@
 
-Numerical chips at $v_c =$ \qty{10}{\m\per\min} and $h =$ \qty{40}{\um} for $\lambda_s =$ \qty{0}{\degree} and $\lambda_s =$ \qty{6}{\degree} are provided in Figures \ref{fig:ChipsNum} and \ref{fig:ChipsNumBack}.
+Numerical chips at $v_c =$~\qty{10}{\m\per\min} and $h =$~\qty{40}{\um} for $\lambda_s =$~\qty{0}{\degree} and $\lambda_s =$~\qty{6}{\degree} are provided in Figures \ref{fig:ChipsNum} and \ref{fig:ChipsNumBack}.
 When the inclination of the cutting edge is \qty{0}{\degree}, both sides of the chip are identical and a symmetry plane can be drawn in the middle of the workpiece (Figure \ref{fig:ChipsNumBack} (a)).
@@
 \includegraphics[width = 140 mm]{Figures/ChipsNum}
-\caption{Temperature contours (in \unit{\K}) of the numerical chip after \qty{1.5}{\ms} at $v_c =$ \qty{10}{\m\per\min}, $h =$ \qty{40}{\um} and (a) $\lambda_s =$ \qty{0}{\degree}, (b) $\lambda_s =$ \qty{6}{\degree}}
+\caption{Temperature contours (in \unit{\K}) of the numerical chip after \qty{1.5}{\ms} at $v_c =$~\qty{10}{\m\per\min}, $h =$~\qty{40}{\um} and (a) $\lambda_s =$~\qty{0}{\degree}, (b) $\lambda_s =$~\qty{6}{\degree}}
 \label{fig:ChipsNum}
@@
 \includegraphics[width = 140 mm]{Figures/ChipsNumBack}
-\caption{Temperature contours (in \unit{\K}) of the back of the numerical chip (tool is removed) after \qty{1.5}{\ms} at $v_c =$ \qty{10}{\m\per\min}, $h =$ \qty{40}{\um} and (a) $\lambda_s =$ \qty{0}{\degree}, (b) $\lambda_s =$ \qty{6}{\degree}}
+\caption{Temperature contours (in \unit{\K}) of the back of the numerical chip (tool is removed) after \qty{1.5}{\ms} at $v_c =$~\qty{10}{\m\per\min}, $h =$~\qty{40}{\um} and (a) $\lambda_s =$~\qty{0}{\degree}, (b) $\lambda_s =$~\qty{6}{\degree}}
 \label{fig:ChipsNumBack}
@@
 \includegraphics[width = 140 mm]{Figures/ChipNumTop}
-\caption{Temperature contours (in \unit{\K}) of the top of the numerical chip after \qty{1.5}{\ms} at $v_c =$ \qty{10}{\m\per\min}, $h =$ \qty{40}{\um} and $\lambda_s =$ \qty{0}{\degree}}
+\caption{Temperature contours (in \unit{\K}) of the top of the numerical chip after \qty{1.5}{\ms} at $v_c =$~\qty{10}{\m\per\min}, $h =$~\qty{40}{\um} and $\lambda_s =$~\qty{0}{\degree}}
 \label{fig:ChipNumTop}
@@
 Average values of the experimental forces and their dispersion are shown in Figures \ref{fig:Fx_0} to \ref{fig:Fz_6} together with the average numerical values.
-Passive force values are of course only plotted for $\lambda_s =$ \qty{6}{\degree} as they are equal to zero when $\lambda_s =$ \qty{0}{\degree}.
+Passive force values are of course only plotted for $\lambda_s =$~\qty{6}{\degree} as they are equal to zero when $\lambda_s =$~\qty{0}{\degree}.
 
@@
 \includegraphics[width = 140 mm]{Figures/Fx_0}
-\caption{Comparison of experimental (E) and numerical (N) cutting forces at the cutting edge inclination of \qty{0}{\degree} for the 3 uncut chip thicknesses (40, 60 and \qty{40}{\um}) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and \qty{40}{\m\per\min})}
+\caption{Comparison of experimental and numerical cutting forces at the cutting edge inclination of \qty{0}{\degree} for the 3 uncut chip thicknesses and the 6 cutting speeds}
 \label{fig:Fx_0}
@@
 \includegraphics[width = 140 mm]{Figures/Fx_6}
-\caption{Comparison of experimental (E) and numerical (N) cutting forces at the cutting edge inclination of \qty{6}{\degree} for the 3 uncut chip thicknesses (40, 60 and \qty{80}{\um}) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and \qty{40}{\m\per\min})}
+\caption{Comparison of experimental and numerical cutting forces at the cutting edge inclination of \qty{6}{\degree} for the 3 uncut chip thicknesses and the 6 cutting speeds}
 \label{fig:Fx_6}
@@
 \includegraphics[width = 140 mm]{Figures/Fy_0}
-\caption{Comparison of experimental (E) and numerical (N) feed forces at the cutting edge inclination of \qty{0}{\degree} for the 3 uncut chip thicknesses (40, 60 and \qty{80}{\um}) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and \qty{40}{\m\per\min})}
+\caption{Comparison of experimental and numerical feed forces at the cutting edge inclination of \qty{0}{\degree} for the 3 uncut chip thicknesses and the 6 cutting speeds}
 \label{fig:Fy_0}
@@
 \includegraphics[width = 140 mm]{Figures/Fy_6}
-\caption{Comparison of experimental (E) and numerical (N) feed forces at the cutting edge inclination of \qty{6}{\degree} for the 3 uncut chip thicknesses (40, 60 and \qty{80}{\um}) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and \qty{40}{\m\per\min})}
+\caption{Comparison of experimental and numerical feed forces at the cutting edge inclination of \qty{6}{\degree} for the 3 uncut chip thicknesses and the 6 cutting speeds}
 \label{fig:Fy_6}
@@
 \includegraphics[width = 140 mm]{Figures/Fz_6}
-\caption{Comparison of experimental (E) and numerical (N) passive forces at the cutting edge inclination of \qty{6}{\degree} for the 3 uncut chip thicknesses (40, 60 and \qty{80}{\um}) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and \qty{40}{\m\per\min})}
+\caption{Comparison of experimental and numerical passive forces at the cutting edge inclination of \qty{6}{\degree} for the 3 uncut chip thicknesses and the 6 cutting speeds}
 \label{fig:Fz_6}
@@
 with $h$ the uncut chip thickness and $h'$ the chip thickness, is almost independent of the uncut chip thickness (Figures \ref{fig:h0} and \ref{fig:h6}).
-It is slightly reduced from $\lambda_s =$ \qty{0}{\degree} to $\lambda_s =$ \qty{6}{\degree}, which means that the chip thickness decreases with the inclination angle.
+It is slightly reduced from $\lambda_s =$~\qty{0}{\degree} to $\lambda_s =$~\qty{6}{\degree}, which means that the chip thickness decreases with the inclination angle.
 This influence is underestimated by the model: the reduction of $\lambda_h$ is smaller than in the experiments.
@@
 \includegraphics[width = 140 mm]{Figures/h0}
-\caption{Comparison of experimental (E) and numerical (N) chip thickness ratios at the cutting edge inclination of \qty{0}{\degree} for the 3 uncut chip thicknesses (40, 60 and \qty{80}{\um}) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and \qty{40}{\m\per\min})}
+\caption{Comparison of experimental and numerical chip thickness ratios at the cutting edge inclination of \qty{0}{\degree} for the 3 uncut chip thicknesses and the 6 cutting speeds}
 \label{fig:h0}
@@
 \includegraphics[width = 140 mm]{Figures/h6}
-\caption{Comparison of experimental (E) and numerical (N) chip thickness ratios at the cutting edge inclination of \qty{6}{\degree} for the 3 uncut chip thicknesses (40, 60 and \qty{80}{\um}) and the 6 cutting speeds (5, 7.5, 10, 20, 30 and \qty{40}{\m\per\min})}
+\caption{Comparison of experimental and numerical chip thickness ratios at the cutting edge inclination of \qty{6}{\degree} for the 3 uncut chip thicknesses and the 6 cutting speeds}
 \label{fig:h6}
@@
 \hline\noalign{\smallskip}
-Average $\lambda_s =$ \qty{0}{\degree} & 3 & 38 & -- & 14\\
-Average $\lambda_s =$ \qty{6}{\degree} & 4 & 40 & 26 & 21\\
+Average $\lambda_s =$~\qty{0}{\degree} & 3 & 38 & -- & 14\\
+Average $\lambda_s =$~\qty{6}{\degree} & 4 & 40 & 26 & 21\\
 Max. global & 10 & 60 & 29 & 38\\
@@
 The numerical model is then able to better reproduce the real behaviour of the material and to take into account thermomechanical transformations which are sources of non-linearities, difficult to take into account with an analytical flow law model.
-Current work, using a Gleeble thermomechanical simulator, on the behaviour of a modified carbon alloy AISI P20 shows the advantages of this approach compared to models in the literature such as Johnson-Cook, Zerilli-Armstrong \cite{Muralli-2017-Performance} or Hansel-Spittel \cite{chadha2018approach}, insofar as one is then able to better reproduce more complex material behaviours.
+Current work, using a Gleeble thermomechanical simulator, on the behaviour of a modified carbon alloy AISI P20 shows the advantages of this approach compared to models in the literature such as Johnson-Cook, Zerilli-Armstrong \cite{gurusamy_Performance_2017} or Hansel-Spittel \cite{chadha_Approach_2018}, insofar as one is then able to better reproduce more complex material behaviours.
   \item The cutting force is the best modelled quantity with an average difference of \qty{4}{\%} with the experiments.

### 2023-12-10 Article.tex
Removal of "Preprint submitted to XX"
Revision-1

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% To remove "Preprint submitted to Journal" at the bottom of the 1st page
+\makeatletter
+\def\ps@pprintTitle{%
+ \let\@oddhead\@empty
+ \let\@evenhead\@empty
+ \def\@oddfoot{}%
+ \let\@evenfoot\@oddfoot}
+\makeatother
+
+\makeatletter
+\def\ps@pprintTitle{
+  \let\@oddhead\@empty
+  \let\@evenhead\@empty
+  \def\@oddfoot{\textit{\small{\hfill\today}}}
+  \def\@evenfoot{\thepage\hfill}}
+\makeatother
+
 \journal{Journal}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\author[1]{F. Ducobu\corref{cor1}}
+\author[1]{François Ducobu\corref{cor1}}
 \ead{Francois.Ducobu@umons.ac.be}
@@
 
-\author[2]{O. Pantal\'{e}}
-\author[3]{B. Lauwers}
+\author[2]{Olivier Pantal\'{e}}
+\author[3]{Bert Lauwers}
 
@@
 Table \ref{tab:CutCond} shows the cutting conditions: 6 cutting speeds, 3 uncut chip thicknesses and 2 inclination angles, each repeated 3 times.
+\FD{Add comment to link with SECO's recommendations for the standard tool + reference}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Statements \& Declarations}
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\noindent\textbf{Funding}
+
+\noindent The authors declare that this research received no external funding.\\
+
+\noindent\textbf{Competing Interests}
+
+\noindent The authors have no relevant financial or non-financial interests to disclose.\\
+
+%\textbf{Availability of data and material}
+%
+%\textbf{Code availability}
+%
+%\textbf{Ethics approval and consent to participate}
+%
+%This article does not contain any studies with human participants or animals performed by any 
+%authors.
+%
+%\textbf{Consent for publication}
+
+\noindent\textbf{Author Contributions}
+
+\noindent François Ducobu contributed to Data curation, Formal analysis, Investigation, Methodology, Software, Supervision, Validation, Visualization, Writing -- original draft and review \& editing (focussing on non ANN-related aspects).
+Olivier Pantalé contributed to Data curation, Formal analysis, Investigation, Methodology, Software, Validation, Visualization, Writing -- original draft and review \& editing (focussing on ANN-related aspects).
+Bert Lauwers contributed to Supervision and Writing -- review \& editing.
+All authors read and approved the final manuscript.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%% References

### 2023-12-11 Article.tex
Revision in red

@@
 Table \ref{tab:CutCond} shows the cutting conditions: 6 cutting speeds, 3 uncut chip thicknesses and 2 inclination angles, each repeated 3 times.
-\FD{Add comment to link with SECO's recommendations for the standard tool + reference}
+\textcolor{red}{An inclination angle of \qty{6}{\degree} is the typical value when turning Ti6Al4V, while cutting speeds and uncut chip thicknesses values in accordance with recommended ranges by SECO for the standard tool \cite{secotoolsab_Turning_2011} are adopted.}
 

### 2023-12-12 Article.tex
Update paper with some adds in red

@@
 
-The material model of Ti6Al4V used in all the numerical simulations proposed in the section \ref{sec:ExpNumResults} is a thermo-elasto-viscoplastic law using a flow criterion based on an Artificial Neural Network (ANN) identified for the chosen material and implemented in the Abaqus/Explicit code via a Fortran subroutine VUHARD as proposed by Pantalé et al.
-in \cite{pantale_Efficient_2022}.
-The principle of this approach consists in replacing the analytical formulation of the flow law, based on a Johnson-Cook or Zerilli-Armstrong type model, and allowing the calculation of the flow stress $\sigma^y$ as a function of the plastic strain $\varepsilon^p$, the plastic strain rate, $\mdot{\varepsilon}^p$, and the temperature $T$, by a multi-layer ANN serving as universal approximator.
-Thus, the parameters of the neural network can be directly identified from the experimental data without having to postulate a behavioural model, which simplifies the procedure and allows greater flexibility in the definition of the model.
-The proposed approach also allows, as shown in Pantalé et al.
-\cite{pantale_Efficient_2022}, to compute the three derivatives of the flow stress $\sigma^y$ with respect to the three input variables of the model, a necessary step to implement this model as a flow law in the form of a VUHARD subroutine in the FEM code Abaqus/Explicit, using the exact same network architecture and identified trained parameters as the one used to compute the flow stress $\sigma^y$.
+\textcolor{red}{In the numerical simulations presented in Section \ref{sec:ExpNumResults}, a thermo-elasto-viscoplastic material model for Ti6Al4V is employed, which utilizes a flow criterion based on an Artificial Neural Network (ANN) identified for the material.
+This ANN is implemented in the Abaqus/Explicit code through a Fortran VUHARD subroutine, as proposed by Pantalé et al.
+\cite{pantale_Efficient_2022, pantale_Development_2023}, to compute the flow stress $\sigma^y$ as a function of the plastic strain $\varepsilon^p$, the plastic strain rate, $\mdot{\varepsilon}^p$, and the temperature $T$.
+The approach replaces the analytical formulation of the flow law, typically based on Johnson-Cook or Zerilli-Armstrong type models, with a multi-layer ANN serving as a universal approximator.
+This enables the direct identification of the neural network parameters from experimental data without postulating a behavioral model, simplifying the procedure and providing greater flexibility in model definition.}
 
-In order to verify the influence of the neural network complexity on the numerical results of the simulation and on the computation time, several ANN architectures are tested afterwards (in \ref{subsec:nberneu}).
+\textcolor{red}{In contrast to the classic approach, which involves conducting experiments on a material, postulating an analytical form for the flow law, and identifying the parameters that best fit the experimental data, the use of ANN allows for direct identification of the law from experimental data without the need to postulate the analytical form of the flow law.
+This method also enables the computation of the three derivatives of the flow stress $\sigma^y$ with respect to the three input variables of the model, which is necessary for implementing the model as a flow law in the form of a VUHARD subroutine in the FEM code Abaqus/Explicit.
+The same network architecture and identified trained parameters are used to compute the flow stress $\sigma^y$ and the derivatives in a one-step procedure \cite{pantale_Efficient_2022, pantale_Development_2023}.}
+
+In order to verify the influence of the neural network complexity on the numerical results of the simulation and on the computation time, several ANN architectures \textcolor{red}{(i.e.
+hyperparameters of the ANN)} are tested afterwards (in \ref{subsec:nberneu}).
 The chosen global architecture has 2 hidden layers with a variable number of neurons for the first hidden layer ($\zeta$~=~9 to 17) and 7 neurons for the second hidden layer, 3 inputs (the plastic strain, $\varepsilon^p$, the plastic strain rate, $\mdot{\varepsilon}^p$, and the temperature, $T$) and one output (the yield strength, $\sigma^y$).
@@
 \cite{pantale_Efficient_2022}, this ANN is referred to as ANN 3-9-7-1-sig, as it has 3 inputs, 9 neurons in the first hidden layer, 7 neurons in the second hidden layer, 1 output and a sigmoid activation function.
+\textcolor{red}{The selection of an architecture with two hidden layers was made based on the conclusions drawn in Pantalé et al.
+\cite{pantale_Efficient_2022}.
+Additionally, the decision to use the sigmoid activation function was guided by the findings in Pantalé \cite{pantale_Comparing_2023}, who identified the most efficient and accurate activation functions for finite element simulations in thermomechanical forming.}
 
@@
 In future developments, experimental tests on a Gleeble thermomechanical simulator will be used to generate this network training data.
-The training data, presented in the form of a data table containing the plastic strain $\varepsilon^p$, the plastic strain rate $\mdot{\varepsilon}^p$, the temperature $T$ and the flow stress $\sigma^y$, is processed by a learning algorithm, developed at LGP, in Python, using the Tensorflow library.
+The training data, presented in the form of a data table containing the plastic strain $\varepsilon^p$, the plastic strain rate $\mdot{\varepsilon}^p$, the temperature $T$ and the flow stress $\sigma^y$, is processed by a learning algorithm, developed at LGP, in Python, using the Tensorflow library \cite{Tensorflow-2015}.
 One hour of training on a Dell XPS13 7390 laptop running Ubuntu 20.04 64~bits with 16~GiB of Ram and an Intel 4-core i7-10510U processor allow obtaining the converged parameters of the ANN model.

### 2023-12-17 Article.tex
Revision according to reviewer 2

@@
 %
-All the friction energy is converted into heat. Table \ref{tab:fricHeat} shows the friction coefficients adopted in this study.
+All the friction energy is converted into heat.
+Table \ref{tab:fricHeat} shows the friction coefficients adopted in this study.
+\textcolor{red}{Gap heat conductance based on the distance between the two surfaces is not available in Abaqus/Explicit 2020.
+It is therefore not included in the modelling.}
 
@@
 \begin{center}
-\caption{\label{tab:fricHeat} Friction and heat transfer coefficients \cite{rech_Characterisation_2013, _GRANTA_2020}}
+\caption{\label{tab:fricHeat} Friction and heat transfer coefficients \textcolor{red}{\cite{rech_Characterisation_2013, _GRANTA_2020, stampfer_Material_2021}}}
 \begin{tabular}{lll}
@@
 Numerical chips at $v_c =$~\qty{10}{\m\per\min} and $h =$~\qty{40}{\um} for $\lambda_s =$~\qty{0}{\degree} and $\lambda_s =$~\qty{6}{\degree} are provided in Figures \ref{fig:ChipsNum} and \ref{fig:ChipsNumBack}.
-When the inclination of the cutting edge is \qty{0}{\degree}, both sides of the chip are identical and a symmetry plane can be drawn in the middle of the workpiece (Figure \ref{fig:ChipsNumBack} (a)).
+\textcolor{red}{Due to the absence of heat gap generation in the model, temperatures in the tool increase mainly by the heat generated by friction.
+They are therefore underestimated: maximal temperature in the tool is under \qty{400}{\kelvin} (and all temperatures in the tools are in the blue colours with the scale of Figure \ref{fig:ChipsNum}).} When the inclination of the cutting edge is \qty{0}{\degree}, both sides of the chip are identical and a symmetry plane can be drawn in the middle of the workpiece (Figure \ref{fig:ChipsNumBack} (a)).
 On the other hand, for an inclination of the cutting edge of \qty{6}{\degree}, the chip is no longer aligned with the workpiece.

### 2023-12-18 Article.tex
Answer to question #4 reviewer #2

@@
 This approach was chosen to demonstrate the ability of the neural network flow law to replace a classically formulated flow law such as Johnson-Cook's for the simulation of metal cutting.
-In future developments, experimental tests on a Gleeble thermomechanical simulator will be used to generate this network training data.
+In future developments, experimental tests on a Gleeble thermomechanical simulator \textcolor{red}{associated with Taylor impact tests or Hopkinson bar tests} will be used to generate this network training data.
 The training data, presented in the form of a data table containing the plastic strain $\varepsilon^p$, the plastic strain rate $\mdot{\varepsilon}^p$, the temperature $T$ and the flow stress $\sigma^y$, is processed by a learning algorithm, developed at LGP, in Python, using the Tensorflow library \cite{Tensorflow-2015}.
